### 2022-03-16 paper/MDPI_template/Definitions/journalnames.tex
Removed paper/ folder from .gitignore

%%Updated on 15 January 2022
%,% Website Name,%,%,% Website Name,%%,% Full Name,%%,% Short Name,%%,% DOI abbr,%%,% ISSN,% \continuouspages
%\DeclareOption{}{\gdef\@journal{}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{acoustics}{\gdef\@journal{acoustics}\gdef\@journalfull{Acoustics}\gdef\@journalshort{Acoustics}\gdef\@doiabbr{acoustics}\gdef\@ISSN{2624-599X}\gdef\@continuouspages{yes}}
\DeclareOption{actuators}{\gdef\@journal{actuators}\gdef\@journalfull{Actuators}\gdef\@journalshort{Actuators}\gdef\@doiabbr{act}\gdef\@ISSN{2076-0825}}
\DeclareOption{addictions}{\gdef\@journal{addictions}\gdef\@journalfull{Addictions}\gdef\@journalshort{Addictions}\gdef\@doiabbr{}\gdef\@ISSN{0006-0006}}
\DeclareOption{admsci}{\gdef\@journal{admsci}\gdef\@journalfull{Administrative Sciences}\gdef\@journalshort{Adm. Sci.}\gdef\@doiabbr{admsci}\gdef\@ISSN{2076-3387}}
\DeclareOption{adolescents}{\gdef\@journal{adolescents}\gdef\@journalfull{Adolescents}\gdef\@journalshort{Adolescents}\gdef\@doiabbr{adolescents}\gdef\@ISSN{2673-7051}\gdef\@continuouspages{yes}}
\DeclareOption{aerospace}{\gdef\@journal{aerospace}\gdef\@journalfull{Aerospace}\gdef\@journalshort{Aerospace}\gdef\@doiabbr{aerospace}\gdef\@ISSN{2226-4310}}
\DeclareOption{agriculture}{\gdef\@journal{agriculture}\gdef\@journalfull{Agriculture}\gdef\@journalshort{Agriculture}\gdef\@doiabbr{agriculture}\gdef\@ISSN{2077-0472}}
\DeclareOption{agriengineering}{\gdef\@journal{agriengineering}\gdef\@journalfull{AgriEngineering}\gdef\@journalshort{AgriEngineering}\gdef\@doiabbr{agriengineering}\gdef\@ISSN{2624-7402}\gdef\@continuouspages{yes}}
\DeclareOption{agrochemicals}{\gdef\@journal{agrochemicals}\gdef\@journalfull{Agrochemicals}\gdef\@journalshort{Agrochemicals}\gdef\@doiabbr{agrochemicals}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{agronomy}{\gdef\@journal{agronomy}\gdef\@journalfull{Agronomy}\gdef\@journalshort{Agronomy}\gdef\@doiabbr{agronomy}\gdef\@ISSN{2073-4395}}
\DeclareOption{ai}{\gdef\@journal{ai}\gdef\@journalfull{AI}\gdef\@journalshort{AI}\gdef\@doiabbr{ai}\gdef\@ISSN{2673-2688}\gdef\@continuouspages{yes}}
\DeclareOption{algorithms}{\gdef\@journal{algorithms}\gdef\@journalfull{Algorithms}\gdef\@journalshort{Algorithms}\gdef\@doiabbr{a}\gdef\@ISSN{1999-4893}}
\DeclareOption{allergies}{\gdef\@journal{allergies}\gdef\@journalfull{Allergies}\gdef\@journalshort{Allergies}\gdef\@doiabbr{allergies}\gdef\@ISSN{2313-5786}}
\DeclareOption{alloys}{\gdef\@journal{alloys}\gdef\@journalfull{Alloys}\gdef\@journalshort{Alloys}\gdef\@doiabbr{alloys}\gdef\@ISSN{2674-063X}\gdef\@continuouspages{yes}}
\DeclareOption{analytica}{\gdef\@journal{analytica}\gdef\@journalfull{Analytica}\gdef\@journalshort{Analytica}\gdef\@doiabbr{analytica}\gdef\@ISSN{2673-4532}\gdef\@continuouspages{yes}}
\DeclareOption{analytics}{\gdef\@journal{analytics}\gdef\@journalfull{Analytics}\gdef\@journalshort{Analytics}\gdef\@doiabbr{analytics}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{anatomia}{\gdef\@journal{anatomia}\gdef\@journalfull{Anatomia}\gdef\@journalshort{Anatomia}\gdef\@doiabbr{anatomia}\gdef\@ISSN{2813-0545}\gdef\@continuouspages{yes}}
\DeclareOption{animals}{\gdef\@journal{animals}\gdef\@journalfull{Animals}\gdef\@journalshort{Animals}\gdef\@doiabbr{ani}\gdef\@ISSN{2076-2615}}
\DeclareOption{antibiotics}{\gdef\@journal{antibiotics}\gdef\@journalfull{Antibiotics}\gdef\@journalshort{Antibiotics}\gdef\@doiabbr{antibiotics}\gdef\@ISSN{2079-6382}}
\DeclareOption{antibodies}{\gdef\@journal{antibodies}\gdef\@journalfull{Antibodies}\gdef\@journalshort{Antibodies}\gdef\@doiabbr{antib}\gdef\@ISSN{2073-4468}}
\DeclareOption{antioxidants}{\gdef\@journal{antioxidants}\gdef\@journalfull{Antioxidants}\gdef\@journalshort{Antioxidants}\gdef\@doiabbr{antiox}\gdef\@ISSN{2076-3921}}
\DeclareOption{applbiosci}{\gdef\@journal{applbiosci}\gdef\@journalfull{Applied Biosciences}\gdef\@journalshort{Appl. Biosci.}\gdef\@doiabbr{applbiosci}\gdef\@ISSN{2813-0464}\gdef\@continuouspages{yes}}
\DeclareOption{appliedchem}{\gdef\@journal{appliedchem}\gdef\@journalfull{AppliedChem}\gdef\@journalshort{AppliedChem}\gdef\@doiabbr{appliedchem}\gdef\@ISSN{2673-9623}\gdef\@continuouspages{yes}}
\DeclareOption{appliedmath}{\gdef\@journal{appliedmath}\gdef\@journalfull{AppliedMath}\gdef\@journalshort{AppliedMath}\gdef\@doiabbr{appliedmath}\gdef\@ISSN{2673-9909}\gdef\@continuouspages{yes}}
\DeclareOption{applmech}{\gdef\@journal{applmech}\gdef\@journalfull{Applied Mechanics}\gdef\@journalshort{Appl. Mech.}\gdef\@doiabbr{applmech}\gdef\@ISSN{2673-3161}\gdef\@continuouspages{yes}}
\DeclareOption{applmicrobiol}{\gdef\@journal{applmicrobiol}\gdef\@journalfull{Applied Microbiology}\gdef\@journalshort{Appl. Microbiol.}\gdef\@doiabbr{applmicrobiol}\gdef\@ISSN{2673-8007}\gdef\@continuouspages{yes}}
\DeclareOption{applnano}{\gdef\@journal{applnano}\gdef\@journalfull{Applied Nano}\gdef\@journalshort{Appl. Nano}\gdef\@doiabbr{applnano}\gdef\@ISSN{2673-3501}\gdef\@continuouspages{yes}}
\DeclareOption{applsci}{\gdef\@journal{applsci}\gdef\@journalfull{Applied Sciences}\gdef\@journalshort{Appl. Sci.}\gdef\@doiabbr{app}\gdef\@ISSN{2076-3417}}
\DeclareOption{aquacj}{\gdef\@journal{aquacj}\gdef\@journalfull{Aquaculture Journal}\gdef\@journalshort{Aquac. J.}\gdef\@doiabbr{aj}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{architecture}{\gdef\@journal{architecture}\gdef\@journalfull{Architecture}\gdef\@journalshort{Architecture}\gdef\@doiabbr{architecture}\gdef\@ISSN{2673-8945}\gdef\@continuouspages{yes}}
\DeclareOption{arts}{\gdef\@journal{arts}\gdef\@journalfull{Arts}\gdef\@journalshort{Arts}\gdef\@doiabbr{arts}\gdef\@ISSN{2076-0752}}
\DeclareOption{asc}{\gdef\@journal{asc}\gdef\@journalfull{Automatic Systems and Control}\gdef\@journalshort{Autom. Syst. Control}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{asi}{\gdef\@journal{asi}\gdef\@journalfull{Applied System Innovation}\gdef\@journalshort{Appl. Syst. Innov.}\gdef\@doiabbr{asi}\gdef\@ISSN{2571-5577}}
\DeclareOption{astronomy}{\gdef\@journal{astronomy}\gdef\@journalfull{Astronomy}\gdef\@journalshort{Astronomy}\gdef\@doiabbr{astronomy}\gdef\@ISSN{2674-0346}\gdef\@continuouspages{yes}}
\DeclareOption{atmosphere}{\gdef\@journal{atmosphere}\gdef\@journalfull{Atmosphere}\gdef\@journalshort{Atmosphere}\gdef\@doiabbr{atmos}\gdef\@ISSN{2073-4433}}
\DeclareOption{atoms}{\gdef\@journal{atoms}\gdef\@journalfull{Atoms}\gdef\@journalshort{Atoms}\gdef\@doiabbr{atoms}\gdef\@ISSN{2218-2004}}
\DeclareOption{audiolres}{\gdef\@journal{audiolres}\gdef\@journalfull{Audiology Research}\gdef\@journalshort{Audiol. Res.}\gdef\@doiabbr{audiolres}\gdef\@ISSN{2039-4349}\gdef\@continuouspages{yes}}
\DeclareOption{automation}{\gdef\@journal{automation}\gdef\@journalfull{Automation}\gdef\@journalshort{Automation}\gdef\@doiabbr{automation}\gdef\@ISSN{2673-4052}\gdef\@continuouspages{yes}}
\DeclareOption{axioms}{\gdef\@journal{axioms}\gdef\@journalfull{Axioms}\gdef\@journalshort{Axioms}\gdef\@doiabbr{axioms}\gdef\@ISSN{2075-1680}}
\DeclareOption{bacteria}{\gdef\@journal{bacteria}\gdef\@journalfull{Bacteria}\gdef\@journalshort{Bacteria}\gdef\@doiabbr{bacteria}\gdef\@ISSN{2674-1334}\gdef\@continuouspages{yes}}
\DeclareOption{batteries}{\gdef\@journal{batteries}\gdef\@journalfull{Batteries}\gdef\@journalshort{Batteries}\gdef\@doiabbr{batteries}\gdef\@ISSN{2313-0105}}
\DeclareOption{bdcc}{\gdef\@journal{bdcc}\gdef\@journalfull{Big Data and Cognitive Computing}\gdef\@journalshort{Big Data Cogn. Comput.}\gdef\@doiabbr{bdcc}\gdef\@ISSN{2504-2289}}
\DeclareOption{behavsci}{\gdef\@journal{behavsci}\gdef\@journalfull{Behavioral Sciences}\gdef\@journalshort{Behav. Sci.}\gdef\@doiabbr{bs}\gdef\@ISSN{2076-328X}}
\DeclareOption{beverages}{\gdef\@journal{beverages}\gdef\@journalfull{Beverages}\gdef\@journalshort{Beverages}\gdef\@doiabbr{beverages}\gdef\@ISSN{2306-5710}}
\DeclareOption{biochem}{\gdef\@journal{biochem}\gdef\@journalfull{BioChem}\gdef\@journalshort{BioChem}\gdef\@doiabbr{biochem}\gdef\@ISSN{2673-6411}\gdef\@continuouspages{yes}}
\DeclareOption{bioengineering}{\gdef\@journal{bioengineering}\gdef\@journalfull{Bioengineering}\gdef\@journalshort{Bioengineering}\gdef\@doiabbr{bioengineering}\gdef\@ISSN{2306-5354}}
\DeclareOption{biologics}{\gdef\@journal{biologics}\gdef\@journalfull{Biologics}\gdef\@journalshort{Biologics}\gdef\@doiabbr{biologics}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{biology}{\gdef\@journal{biology}\gdef\@journalfull{Biology}\gdef\@journalshort{Biology}\gdef\@doiabbr{biology}\gdef\@ISSN{2079-7737}}
\DeclareOption{biomass}{\gdef\@journal{biomass}\gdef\@journalfull{Biomass}\gdef\@journalshort{Biomass}\gdef\@doiabbr{biomass}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{biomechanics}{\gdef\@journal{biomechanics}\gdef\@journalfull{Biomechanics}\gdef\@journalshort{Biomechanics}\gdef\@doiabbr{biomechanics}\gdef\@ISSN{2673-7078}\gdef\@continuouspages{yes}}
\DeclareOption{biomed}{\gdef\@journal{biomed}\gdef\@journalfull{BioMed}\gdef\@journalshort{BioMed}\gdef\@doiabbr{biomed}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{biomedicines}{\gdef\@journal{biomedicines}\gdef\@journalfull{Biomedicines}\gdef\@journalshort{Biomedicines}\gdef\@doiabbr{biomedicines}\gdef\@ISSN{2227-9059}}
\DeclareOption{biomedinformatics}{\gdef\@journal{biomedinformatics}\gdef\@journalfull{Biomedinformatics}\gdef\@journalshort{Biomedinformatics}\gdef\@doiabbr{biomedinformatics}\gdef\@ISSN{2673-7426}\gdef\@continuouspages{yes}}
\DeclareOption{biomimetics}{\gdef\@journal{biomimetics}\gdef\@journalfull{Biomimetics}\gdef\@journalshort{Biomimetics}\gdef\@doiabbr{biomimetics}\gdef\@ISSN{2313-7673}}
\DeclareOption{biomolecules}{\gdef\@journal{biomolecules}\gdef\@journalfull{Biomolecules}\gdef\@journalshort{Biomolecules}\gdef\@doiabbr{biom}\gdef\@ISSN{2218-273X}}
\DeclareOption{biophysica}{\gdef\@journal{biophysica}\gdef\@journalfull{Biophysica}\gdef\@journalshort{Biophysica}\gdef\@doiabbr{biophysica}\gdef\@ISSN{2673-4125}\gdef\@continuouspages{yes}}
\DeclareOption{biosensors}{\gdef\@journal{biosensors}\gdef\@journalfull{Biosensors}\gdef\@journalshort{Biosensors}\gdef\@doiabbr{bios}\gdef\@ISSN{2079-6374}}
\DeclareOption{biotech}{\gdef\@journal{biotech}\gdef\@journalfull{BioTech}\gdef\@journalshort{BioTech}\gdef\@doiabbr{biotech}\gdef\@ISSN{2673-6284}}
\DeclareOption{birds}{\gdef\@journal{birds}\gdef\@journalfull{Birds}\gdef\@journalshort{Birds}\gdef\@doiabbr{birds}\gdef\@ISSN{2673-6004}\gdef\@continuouspages{yes}}
\DeclareOption{bloods}{\gdef\@journal{bloods}\gdef\@journalfull{Bloods}\gdef\@journalshort{Bloods}\gdef\@doiabbr{bloods}\gdef\@ISSN{2673-415X}}
\DeclareOption{blsf}{\gdef\@journal{blsf}\gdef\@journalfull{Biology and Life Sciences Forum}\gdef\@journalshort{Biol. Life Sci. Forum}\gdef\@doiabbr{blsf	}\gdef\@ISSN{2673-9976}}
\DeclareOption{brainsci}{\gdef\@journal{brainsci}\gdef\@journalfull{Brain Sciences}\gdef\@journalshort{Brain Sci.}\gdef\@doiabbr{brainsci}\gdef\@ISSN{2076-3425}}
\DeclareOption{breath}{\gdef\@journal{breath}\gdef\@journalfull{Breath}\gdef\@journalshort{Breath}\gdef\@doiabbr{breath}\gdef\@ISSN{}}
\DeclareOption{buildings}{\gdef\@journal{buildings}\gdef\@journalfull{Buildings}\gdef\@journalshort{Buildings}\gdef\@doiabbr{buildings}\gdef\@ISSN{2075-5309}}
\DeclareOption{businesses}{\gdef\@journal{businesses}\gdef\@journalfull{Businesses}\gdef\@journalshort{Businesses}\gdef\@doiabbr{businesses}\gdef\@ISSN{2673-7116}\gdef\@continuouspages{yes}}
\DeclareOption{cancers}{\gdef\@journal{cancers}\gdef\@journalfull{Cancers}\gdef\@journalshort{Cancers}\gdef\@doiabbr{cancers}\gdef\@ISSN{2072-6694}}
\DeclareOption{carbon}{\gdef\@journal{carbon}\gdef\@journalfull{C}\gdef\@journalshort{C}\gdef\@doiabbr{c}\gdef\@ISSN{2311-5629}}
\DeclareOption{cardiogenetics}{\gdef\@journal{cardiogenetics}\gdef\@journalfull{Cardiogenetics}\gdef\@journalshort{Cardiogenetics}\gdef\@doiabbr{cardiogenetics}\gdef\@ISSN{2035-8148}\gdef\@continuouspages{yes}}
\DeclareOption{catalysts}{\gdef\@journal{catalysts}\gdef\@journalfull{Catalysts}\gdef\@journalshort{Catalysts}\gdef\@doiabbr{catal}\gdef\@ISSN{2073-4344}}
\DeclareOption{cells}{\gdef\@journal{cells}\gdef\@journalfull{Cells}\gdef\@journalshort{Cells}\gdef\@doiabbr{cells}\gdef\@ISSN{2073-4409}}
\DeclareOption{ceramics}{\gdef\@journal{ceramics}\gdef\@journalfull{Ceramics}\gdef\@journalshort{Ceramics}\gdef\@doiabbr{ceramics}\gdef\@ISSN{2571-6131}\gdef\@continuouspages{yes}}
\DeclareOption{challenges}{\gdef\@journal{challenges}\gdef\@journalfull{Challenges}\gdef\@journalshort{Challenges}\gdef\@doiabbr{challe}\gdef\@ISSN{2078-1547}}
\DeclareOption{chemengineering}{\gdef\@journal{chemengineering}\gdef\@journalfull{ChemEngineering}\gdef\@journalshort{ChemEngineering}\gdef\@doiabbr{chemengineering}\gdef\@ISSN{2305-7084}}
\DeclareOption{chemistry}{\gdef\@journal{chemistry}\gdef\@journalfull{Chemistry}\gdef\@journalshort{Chemistry}\gdef\@doiabbr{chemistry}\gdef\@ISSN{2624-8549}\gdef\@continuouspages{yes}}
\DeclareOption{chemosensors}{\gdef\@journal{chemosensors}\gdef\@journalfull{Chemosensors}\gdef\@journalshort{Chemosensors}\gdef\@doiabbr{chemosensors}\gdef\@ISSN{2227-9040}}
\DeclareOption{chemproc}{\gdef\@journal{chemproc}\gdef\@journalfull{Chemistry Proceedings}\gdef\@journalshort{Chem. Proc.}\gdef\@doiabbr{chemproc}\gdef\@ISSN{2673-4583}}
\DeclareOption{children}{\gdef\@journal{children}\gdef\@journalfull{Children}\gdef\@journalshort{Children}\gdef\@doiabbr{children}\gdef\@ISSN{2227-9067}}
\DeclareOption{chips}{\gdef\@journal{chips}\gdef\@journalfull{Chips}\gdef\@journalshort{Chips}\gdef\@doiabbr{chips}\gdef\@ISSN{2674-0710}\gdef\@continuouspages{yes}}
\DeclareOption{cimb}{\gdef\@journal{cimb}\gdef\@journalfull{Current Issues in Molecular Biology}\gdef\@journalshort{Curr. Issues Mol. Biol.}\gdef\@doiabbr{cimb}\gdef\@ISSN{1467-3045}\gdef\@continuouspages{yes}}
\DeclareOption{civileng}{\gdef\@journal{civileng}\gdef\@journalfull{CivilEng}\gdef\@journalshort{CivilEng}\gdef\@doiabbr{civileng}\gdef\@ISSN{2673-4109}\gdef\@continuouspages{yes}}
\DeclareOption{cleantechnol}{\gdef\@journal{cleantechnol}\gdef\@journalfull{Clean Technologies}\gdef\@journalshort{Clean Technol.}\gdef\@doiabbr{cleantechnol}\gdef\@ISSN{2571-8797}\gdef\@continuouspages{yes}}
\DeclareOption{climate}{\gdef\@journal{climate}\gdef\@journalfull{Climate}\gdef\@journalshort{Climate}\gdef\@doiabbr{cli}\gdef\@ISSN{2225-1154}}
\DeclareOption{clinpract}{\gdef\@journal{clinpract}\gdef\@journalfull{Clinics and Practice}\gdef\@journalshort{Clin. Pract.}\gdef\@doiabbr{clinpract}\gdef\@ISSN{2039-7283}\gdef\@continuouspages{yes}}
\DeclareOption{clockssleep}{\gdef\@journal{clockssleep}\gdef\@journalfull{Clocks \& Sleep}\gdef\@journalshort{Clocks\&Sleep}\gdef\@doiabbr{clockssleep}\gdef\@ISSN{2624-5175}\gdef\@continuouspages{yes}}
\DeclareOption{cmd}{\gdef\@journal{cmd}\gdef\@journalfull{Corrosion and Materials Degradation}\gdef\@journalshort{Corros. Mater. Degrad.}\gdef\@doiabbr{cmd}\gdef\@ISSN{2624-5558}\gdef\@continuouspages{yes}}
\DeclareOption{coasts}{\gdef\@journal{coasts}\gdef\@journalfull{Coasts}\gdef\@journalshort{Coasts}\gdef\@doiabbr{coasts}\gdef\@ISSN{2673-964X}\gdef\@continuouspages{yes}}
\DeclareOption{coatings}{\gdef\@journal{coatings}\gdef\@journalfull{Coatings}\gdef\@journalshort{Coatings}\gdef\@doiabbr{coatings}\gdef\@ISSN{2079-6412}}
\DeclareOption{colloids}{\gdef\@journal{colloids}\gdef\@journalfull{Colloids Interfaces}\gdef\@journalshort{Colloids Interfaces}\gdef\@doiabbr{colloids}\gdef\@ISSN{2504-5377}}
\DeclareOption{colorants}{\gdef\@journal{colorants}\gdef\@journalfull{Colorants}\gdef\@journalshort{Colorants}\gdef\@doiabbr{colorants}\gdef\@ISSN{2079-6447}\gdef\@continuouspages{yes}}
\DeclareOption{commodities}{\gdef\@journal{commodities}\gdef\@journalfull{Commodities}\gdef\@journalshort{Commodities}\gdef\@doiabbr{commodities}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{compounds}{\gdef\@journal{compounds}\gdef\@journalfull{Compounds}\gdef\@journalshort{Compounds}\gdef\@doiabbr{compounds}\gdef\@ISSN{2673-6918}\gdef\@continuouspages{yes}}
\DeclareOption{computation}{\gdef\@journal{computation}\gdef\@journalfull{Computation}\gdef\@journalshort{Computation}\gdef\@doiabbr{computation}\gdef\@ISSN{2079-3197}}
\DeclareOption{computers}{\gdef\@journal{computers}\gdef\@journalfull{Computers}\gdef\@journalshort{Computers}\gdef\@doiabbr{computers}\gdef\@ISSN{2073-431X}}
\DeclareOption{condensedmatter}{\gdef\@journal{condensedmatter}\gdef\@journalfull{Condensed Matter}\gdef\@journalshort{Condens. Matter}\gdef\@doiabbr{condmat}\gdef\@ISSN{2410-3896}}
\DeclareOption{conservation}{\gdef\@journal{conservation}\gdef\@journalfull{Conservation}\gdef\@journalshort{Conservation}\gdef\@doiabbr{conservation}\gdef\@ISSN{2673-7159}\gdef\@continuouspages{yes}}
\DeclareOption{constrmater}{\gdef\@journal{constrmater}\gdef\@journalfull{Construction Materials}\gdef\@journalshort{Constr. Mater.}\gdef\@doiabbr{constrmater}\gdef\@ISSN{2673-7108}\gdef\@continuouspages{yes}}
\DeclareOption{cosmetics}{\gdef\@journal{cosmetics}\gdef\@journalfull{Cosmetics}\gdef\@journalshort{Cosmetics}\gdef\@doiabbr{cosmetics}\gdef\@ISSN{2079-9284}}
\DeclareOption{covid}{\gdef\@journal{covid}\gdef\@journalfull{COVID}\gdef\@journalshort{COVID}\gdef\@doiabbr{covid}\gdef\@ISSN{2673-8112}\gdef\@continuouspages{yes}}
\DeclareOption{crops}{\gdef\@journal{crops}\gdef\@journalfull{Crops}\gdef\@journalshort{Crops}\gdef\@doiabbr{crops}\gdef\@ISSN{2673-7655}\gdef\@continuouspages{yes}}
\DeclareOption{cryptography}{\gdef\@journal{cryptography}\gdef\@journalfull{Cryptography}\gdef\@journalshort{Cryptography}\gdef\@doiabbr{cryptography}\gdef\@ISSN{2410-387X}}
\DeclareOption{crystals}{\gdef\@journal{crystals}\gdef\@journalfull{Crystals}\gdef\@journalshort{Crystals}\gdef\@doiabbr{cryst}\gdef\@ISSN{2073-4352}}
\DeclareOption{csmf}{\gdef\@journal{csmf}\gdef\@journalfull{Computer Sciences \& Mathematics Forum}\gdef\@journalshort{Comput. Sci. Math. Forum}\gdef\@doiabbr{csmf}\gdef\@ISSN{2813-0324}\gdef\@continuouspages{yes}}
\DeclareOption{ctn}{\gdef\@journal{ctn}\gdef\@journalfull{Clinical and Translational Neuroscience}\gdef\@journalshort{CTN}\gdef\@doiabbr{Clin. Transl. Neurosci.}\gdef\@ISSN{2514-183X}}
\DeclareOption{curroncol}{\gdef\@journal{curroncol}\gdef\@journalfull{Current Oncology}\gdef\@journalshort{Curr. Oncol.}\gdef\@doiabbr{curroncol}\gdef\@ISSN{1718-7729}\gdef\@continuouspages{yes}}
\DeclareOption{cyber}{\gdef\@journal{cyber}\gdef\@journalfull{Cyber}\gdef\@journalshort{Cyber}\gdef\@doiabbr{cyber}\gdef\@ISSN{2624-800X}}
\DeclareOption{dairy}{\gdef\@journal{dairy}\gdef\@journalfull{Dairy}\gdef\@journalshort{Dairy}\gdef\@doiabbr{dairy}\gdef\@ISSN{2624-862X}\gdef\@continuouspages{yes}}
\DeclareOption{data}{\gdef\@journal{data}\gdef\@journalfull{Data}\gdef\@journalshort{Data}\gdef\@doiabbr{data}\gdef\@ISSN{2306-5729}}
\DeclareOption{dentistry}{\gdef\@journal{dentistry}\gdef\@journalfull{Dentistry Journal}\gdef\@journalshort{Dent. J.}\gdef\@doiabbr{dj}\gdef\@ISSN{2304-6767}}
\DeclareOption{dermato}{\gdef\@journal{dermato}\gdef\@journalfull{Dermato}\gdef\@journalshort{Dermato}\gdef\@doiabbr{dermato}\gdef\@ISSN{2673-6179}\gdef\@continuouspages{yes}}
\DeclareOption{dermatopathology}{\gdef\@journal{dermatopathology}\gdef\@journalfull{Dermatopathology}\gdef\@journalshort{Dermatopathology}\gdef\@doiabbr{dermatopathology}\gdef\@ISSN{2296-3529}\gdef\@continuouspages{yes}}
\DeclareOption{designs}{\gdef\@journal{designs}\gdef\@journalfull{Designs}\gdef\@journalshort{Designs}\gdef\@doiabbr{designs}\gdef\@ISSN{2411-9660}}
\DeclareOption{diabetology}{\gdef\@journal{diabetology}\gdef\@journalfull{Diabetology}\gdef\@journalshort{Diabetology}\gdef\@doiabbr{diabetology}\gdef\@ISSN{2673-4540}\gdef\@continuouspages{yes}}
\DeclareOption{diagnostics}{\gdef\@journal{diagnostics}\gdef\@journalfull{Diagnostics}\gdef\@journalshort{Diagnostics}\gdef\@doiabbr{diagnostics}\gdef\@ISSN{2075-4418}}
\DeclareOption{dietetics}{\gdef\@journal{dietetics}\gdef\@journalfull{Dietetics}\gdef\@journalshort{Dietetics}\gdef\@doiabbr{dietetics}\gdef\@ISSN{2674-0311}\gdef\@continuouspages{yes}}
\DeclareOption{digital}{\gdef\@journal{digital}\gdef\@journalfull{Digital}\gdef\@journalshort{Digital}\gdef\@doiabbr{digital}\gdef\@ISSN{2673-6470}\gdef\@continuouspages{yes}}
\DeclareOption{disabilities}{\gdef\@journal{disabilities}\gdef\@journalfull{Disabilities}\gdef\@journalshort{Disabilities}\gdef\@doiabbr{disabilities}\gdef\@ISSN{2673-7272}\gdef\@continuouspages{yes}}
\DeclareOption{diseases}{\gdef\@journal{diseases}\gdef\@journalfull{Diseases}\gdef\@journalshort{Diseases}\gdef\@doiabbr{diseases}\gdef\@ISSN{2079-9721}}
\DeclareOption{diversity}{\gdef\@journal{diversity}\gdef\@journalfull{Diversity}\gdef\@journalshort{Diversity}\gdef\@doiabbr{d}\gdef\@ISSN{1424-2818}}
\DeclareOption{dna}{\gdef\@journal{dna}\gdef\@journalfull{DNA}\gdef\@journalshort{DNA}\gdef\@doiabbr{dna}\gdef\@ISSN{2673-8856}\gdef\@continuouspages{yes}}
\DeclareOption{drones}{\gdef\@journal{drones}\gdef\@journalfull{Drones}\gdef\@journalshort{Drones}\gdef\@doiabbr{drones}\gdef\@ISSN{2504-446X}}
\DeclareOption{dynamics}{\gdef\@journal{dynamics}\gdef\@journalfull{Dynamics}\gdef\@journalshort{Dynamics}\gdef\@doiabbr{dynamics}\gdef\@ISSN{2673-8716}\gdef\@continuouspages{yes}}
\DeclareOption{earth}{\gdef\@journal{earth}\gdef\@journalfull{Earth}\gdef\@journalshort{Earth}\gdef\@doiabbr{earth}\gdef\@ISSN{2673-4834}\gdef\@continuouspages{yes}}
\DeclareOption{ebj}{\gdef\@journal{ebj}\gdef\@journalfull{European Burn Journal}\gdef\@journalshort{Eur. Burn J.}\gdef\@doiabbr{ebj}\gdef\@ISSN{2673-1991}\gdef\@continuouspages{yes}}
\DeclareOption{ecologies}{\gdef\@journal{ecologies}\gdef\@journalfull{Ecologies}\gdef\@journalshort{Ecologies}\gdef\@doiabbr{ecologies}\gdef\@ISSN{2673-4133}\gdef\@continuouspages{yes}}
\DeclareOption{econometrics}{\gdef\@journal{econometrics}\gdef\@journalfull{Econometrics}\gdef\@journalshort{Econometrics}\gdef\@doiabbr{econometrics}\gdef\@ISSN{2225-1146}}
\DeclareOption{economies}{\gdef\@journal{economies}\gdef\@journalfull{Economies}\gdef\@journalshort{Economies}\gdef\@doiabbr{economies}\gdef\@ISSN{2227-7099}}
\DeclareOption{education}{\gdef\@journal{education}\gdef\@journalfull{Education Sciences}\gdef\@journalshort{Educ. Sci.}\gdef\@doiabbr{educsci}\gdef\@ISSN{2227-7102}}
\DeclareOption{ejihpe}{\gdef\@journal{ejihpe}\gdef\@journalfull{European Journal of Investigation in Health Psychology and Education}\gdef\@journalshort{Eur. J. Investig. Health Psychol. Educ.}\gdef\@doiabbr{ejihpe}\gdef\@ISSN{2254-9625}\gdef\@continuouspages{yes}}
\DeclareOption{electricity}{\gdef\@journal{electricity}\gdef\@journalfull{Electricity}\gdef\@journalshort{Electricity}\gdef\@doiabbr{electricity}\gdef\@ISSN{2673-4826}\gdef\@continuouspages{yes}}
\DeclareOption{electrochem}{\gdef\@journal{electrochem}\gdef\@journalfull{Electrochem}\gdef\@journalshort{Electrochem}\gdef\@doiabbr{electrochem}\gdef\@ISSN{2673-3293}\gdef\@continuouspages{yes}}
\DeclareOption{electronicmat}{\gdef\@journal{electronicmat}\gdef\@journalfull{Electronic Materials}\gdef\@journalshort{Electron. Mater.}\gdef\@doiabbr{electronicmat}\gdef\@ISSN{2673-3978}\gdef\@continuouspages{yes}}
\DeclareOption{electronics}{\gdef\@journal{electronics}\gdef\@journalfull{Electronics}\gdef\@journalshort{Electronics}\gdef\@doiabbr{electronics}\gdef\@ISSN{2079-9292}}
\DeclareOption{encyclopedia}{\gdef\@journal{encyclopedia}\gdef\@journalfull{Encyclopedia}\gdef\@journalshort{Encyclopedia}\gdef\@doiabbr{encyclopedia}\gdef\@ISSN{2673-8392}\gdef\@continuouspages{yes}}
\DeclareOption{endocrines}{\gdef\@journal{endocrines}\gdef\@journalfull{Endocrines}\gdef\@journalshort{Endocrines}\gdef\@doiabbr{endocrines}\gdef\@ISSN{2673-396X}\gdef\@continuouspages{yes}}
\DeclareOption{energies}{\gdef\@journal{energies}\gdef\@journalfull{Energies}\gdef\@journalshort{Energies}\gdef\@doiabbr{en}\gdef\@ISSN{1996-1073}}
\DeclareOption{eng}{\gdef\@journal{eng}\gdef\@journalfull{Eng-Advances in Engineering}\gdef\@journalshort{Eng}\gdef\@doiabbr{eng}\gdef\@ISSN{2673-4117}\gdef\@continuouspages{yes}}
\DeclareOption{engproc}{\gdef\@journal{engproc}\gdef\@journalfull{Engineering Proceedings}\gdef\@journalshort{Eng. Proc.}\gdef\@doiabbr{engproc}\gdef\@ISSN{2673-4591}}
%\DeclareOption{ent}{\gdef\@journal{ent}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{entomology}{\gdef\@journal{entomology}\gdef\@journalfull{Entomology}\gdef\@journalshort{Entomology}\gdef\@doiabbr{entomology}\gdef\@ISSN{2813-0502}\gdef\@continuouspages{yes}}	
\DeclareOption{entropy}{\gdef\@journal{entropy}\gdef\@journalfull{Entropy}\gdef\@journalshort{Entropy}\gdef\@doiabbr{e}\gdef\@ISSN{1099-4300}}
\DeclareOption{environments}{\gdef\@journal{environments}\gdef\@journalfull{Environments}\gdef\@journalshort{Environments}\gdef\@doiabbr{environments}\gdef\@ISSN{2076-3298}}
\DeclareOption{environsciproc}{\gdef\@journal{environsciproc}\gdef\@journalfull{Environmental Sciences Proceedings}\gdef\@journalshort{Environ. Sci. Proc.}\gdef\@doiabbr{environsciproc}\gdef\@ISSN{2673-4931}}
\DeclareOption{epidemiologia}{\gdef\@journal{epidemiologia}\gdef\@journalfull{Epidemiologia}\gdef\@journalshort{Epidemiologia}\gdef\@doiabbr{epidemiologia}\gdef\@ISSN{2673-3986}\gdef\@continuouspages{yes}}
\DeclareOption{epigenomes}{\gdef\@journal{epigenomes}\gdef\@journalfull{Epigenomes}\gdef\@journalshort{Epigenomes}\gdef\@doiabbr{epigenomes}\gdef\@ISSN{2075-4655}}
\DeclareOption{est}{\gdef\@journal{est}\gdef\@journalfull{Electrochemical Science and Technology}\gdef\@journalshort{Electrochem. Sci. Technol.}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{fermentation}{\gdef\@journal{fermentation}\gdef\@journalfull{Fermentation}\gdef\@journalshort{Fermentation}\gdef\@doiabbr{fermentation}\gdef\@ISSN{2311-5637}}
\DeclareOption{fibers}{\gdef\@journal{fibers}\gdef\@journalfull{Fibers}\gdef\@journalshort{Fibers}\gdef\@doiabbr{fib}\gdef\@ISSN{2079-6439}}
\DeclareOption{fintech}{\gdef\@journal{fintech}\gdef\@journalfull{FinTech}\gdef\@journalshort{FinTech}\gdef\@doiabbr{fintech}\gdef\@ISSN{2674-1032}\gdef\@continuouspages{yes}}
\DeclareOption{fire}{\gdef\@journal{fire}\gdef\@journalfull{Fire}\gdef\@journalshort{Fire}\gdef\@doiabbr{fire}\gdef\@ISSN{2571-6255}}
\DeclareOption{fishes}{\gdef\@journal{fishes}\gdef\@journalfull{Fishes}\gdef\@journalshort{Fishes}\gdef\@doiabbr{fishes}\gdef\@ISSN{2410-3888}}
\DeclareOption{fluids}{\gdef\@journal{fluids}\gdef\@journalfull{Fluids}\gdef\@journalshort{Fluids}\gdef\@doiabbr{fluids}\gdef\@ISSN{2311-5521}}
\DeclareOption{foods}{\gdef\@journal{foods}\gdef\@journalfull{Foods}\gdef\@journalshort{Foods}\gdef\@doiabbr{foods}\gdef\@ISSN{2304-8158}}
\DeclareOption{forecasting}{\gdef\@journal{forecasting}\gdef\@journalfull{Forecasting}\gdef\@journalshort{Forecasting}\gdef\@doiabbr{forecast}\gdef\@ISSN{2571-9394}\gdef\@continuouspages{yes}}
\DeclareOption{forensicsci}{\gdef\@journal{forensicsci}\gdef\@journalfull{Forensic Sciences}\gdef\@journalshort{Forensic Sci.}\gdef\@doiabbr{forensicsci}\gdef\@ISSN{2673-6756}\gdef\@continuouspages{yes}}
\DeclareOption{forests}{\gdef\@journal{forests}\gdef\@journalfull{Forests}\gdef\@journalshort{Forests}\gdef\@doiabbr{f}\gdef\@ISSN{1999-4907}}
\DeclareOption{foundations}{\gdef\@journal{foundations}\gdef\@journalfull{Foundations}\gdef\@journalshort{Foundations}\gdef\@doiabbr{foundations}\gdef\@ISSN{2673-9321}\gdef\@continuouspages{yes}}
\DeclareOption{fractalfract}{\gdef\@journal{fractalfract}\gdef\@journalfull{Fractal and Fractional}\gdef\@journalshort{Fractal Fract.}\gdef\@doiabbr{fractalfract}\gdef\@ISSN{2504-3110}}
\DeclareOption{fuels}{\gdef\@journal{fuels}\gdef\@journalfull{Fuels}\gdef\@journalshort{Fuels}\gdef\@doiabbr{fuels}\gdef\@ISSN{2673-3994}\gdef\@continuouspages{yes}}
\DeclareOption{futureinternet}{\gdef\@journal{futureinternet}\gdef\@journalfull{Future Internet}\gdef\@journalshort{Future Internet}\gdef\@doiabbr{fi}\gdef\@ISSN{1999-5903}}
%\DeclareOption{futureparasites}{\gdef\@journal{futureparasites}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{futurepharmacol}{\gdef\@journal{futurepharmacol}\gdef\@journalfull{Future Pharmacology}\gdef\@journalshort{Future Pharm.}\gdef\@doiabbr{futurepharmacol}\gdef\@ISSN{2673-9879}\gdef\@continuouspages{yes}}
\DeclareOption{futurephys}{\gdef\@journal{futurephys}\gdef\@journalfull{Future Physics}\gdef\@journalshort{Future Phys.}\gdef\@doiabbr{futurephys}\gdef\@ISSN{2624-6503}}
\DeclareOption{futuretransp}{\gdef\@journal{futuretransp}\gdef\@journalfull{Future Transportation}\gdef\@journalshort{Future Transp.}\gdef\@doiabbr{futuretransp}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{galaxies}{\gdef\@journal{galaxies}\gdef\@journalfull{Galaxies}\gdef\@journalshort{Galaxies}\gdef\@doiabbr{galaxies}\gdef\@ISSN{2075-4434}}
\DeclareOption{games}{\gdef\@journal{games}\gdef\@journalfull{Games}\gdef\@journalshort{Games}\gdef\@doiabbr{g}\gdef\@ISSN{2073-4336}}
\DeclareOption{gases}{\gdef\@journal{gases}\gdef\@journalfull{Gases}\gdef\@journalshort{Gases}\gdef\@doiabbr{gases}\gdef\@ISSN{2673-5628}\gdef\@continuouspages{yes}}
\DeclareOption{gastroent}{\gdef\@journal{gastroent}\gdef\@journalfull{Gastroenterology Insights}\gdef\@journalshort{Gastroenterol. Insights}\gdef\@doiabbr{gastroent}\gdef\@ISSN{2036-7422}\gdef\@continuouspages{yes}}
\DeclareOption{gastrointestdisord}{\gdef\@journal{gastrointestdisord}\gdef\@journalfull{Gastrointestinal Disorders}\gdef\@journalshort{Gastrointest. Disord.}\gdef\@doiabbr{gidisord}\gdef\@ISSN{2624-5647}\gdef\@continuouspages{yes}}
\DeclareOption{gels}{\gdef\@journal{gels}\gdef\@journalfull{Gels}\gdef\@journalshort{Gels}\gdef\@doiabbr{gels}\gdef\@ISSN{2310-2861}}
\DeclareOption{genealogy}{\gdef\@journal{genealogy}\gdef\@journalfull{Genealogy}\gdef\@journalshort{Genealogy}\gdef\@doiabbr{genealogy}\gdef\@ISSN{2313-5778}}
\DeclareOption{genes}{\gdef\@journal{genes}\gdef\@journalfull{Genes}\gdef\@journalshort{Genes}\gdef\@doiabbr{genes}\gdef\@ISSN{2073-4425}}
\DeclareOption{geographies}{\gdef\@journal{geographies}\gdef\@journalfull{Geographies}\gdef\@journalshort{Geographies}\gdef\@doiabbr{geographies}\gdef\@ISSN{2673-7086}\gdef\@continuouspages{yes}}
\DeclareOption{geohazards}{\gdef\@journal{geohazards}\gdef\@journalfull{GeoHazards}\gdef\@journalshort{GeoHazards}\gdef\@doiabbr{geohazards}\gdef\@ISSN{2624-795X}\gdef\@continuouspages{yes}}
\DeclareOption{geomatics}{\gdef\@journal{geomatics}\gdef\@journalfull{Geomatics}\gdef\@journalshort{Geomatics}\gdef\@doiabbr{geomatics}\gdef\@ISSN{2673-7418}\gdef\@continuouspages{yes}}
\DeclareOption{geosciences}{\gdef\@journal{geosciences}\gdef\@journalfull{Geosciences}\gdef\@journalshort{Geosciences}\gdef\@doiabbr{geosciences}\gdef\@ISSN{2076-3263}}
\DeclareOption{geotechnics}{\gdef\@journal{geotechnics}\gdef\@journalfull{Geotechnics}\gdef\@journalshort{Geotechnics}\gdef\@doiabbr{geotechnics}\gdef\@ISSN{2673-7094}\gdef\@continuouspages{yes}}
\DeclareOption{geriatrics}{\gdef\@journal{geriatrics}\gdef\@journalfull{Geriatrics}\gdef\@journalshort{Geriatrics}\gdef\@doiabbr{geriatrics}\gdef\@ISSN{2308-3417}}
\DeclareOption{grasses}{\gdef\@journal{grasses}\gdef\@journalfull{Grasses}\gdef\@journalshort{Grasses}\gdef\@doiabbr{grasses}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{hazardousmatters}{\gdef\@journal{hazardousmatters}\gdef\@journalfull{Hazardous Matters}\gdef\@journalshort{Hazard. Matters}\gdef\@doiabbr{}\gdef\@ISSN{0014-0014}}
\DeclareOption{healthcare}{\gdef\@journal{healthcare}\gdef\@journalfull{Healthcare}\gdef\@journalshort{Healthcare}\gdef\@doiabbr{healthcare}\gdef\@ISSN{2227-9032}}
\DeclareOption{hearts}{\gdef\@journal{hearts}\gdef\@journalfull{Hearts}\gdef\@journalshort{Hearts}\gdef\@doiabbr{hearts}\gdef\@ISSN{2673-3846}\gdef\@continuouspages{yes}}
\DeclareOption{hemato}{\gdef\@journal{hemato}\gdef\@journalfull{Hemato}\gdef\@journalshort{Hemato}\gdef\@doiabbr{hemato}\gdef\@ISSN{2673-6357}\gdef\@continuouspages{yes}}
\DeclareOption{heritage}{\gdef\@journal{heritage}\gdef\@journalfull{Heritage}\gdef\@journalshort{Heritage}\gdef\@doiabbr{heritage}\gdef\@ISSN{2571-9408}\gdef\@continuouspages{yes}}
\DeclareOption{highthroughput}{\gdef\@journal{highthroughput}\gdef\@journalfull{High-Throughput}\gdef\@journalshort{High-Throughput}\gdef\@doiabbr{ht}\gdef\@ISSN{2571-5135}}
\DeclareOption{histories}{\gdef\@journal{histories}\gdef\@journalfull{Histories}\gdef\@journalshort{Histories}\gdef\@doiabbr{histories}\gdef\@ISSN{2409-9252}\gdef\@continuouspages{yes}}
\DeclareOption{horticulturae}{\gdef\@journal{horticulturae}\gdef\@journalfull{Horticulturae}\gdef\@journalshort{Horticulturae}\gdef\@doiabbr{horticulturae}\gdef\@ISSN{2311-7524}}
\DeclareOption{humanities}{\gdef\@journal{humanities}\gdef\@journalfull{Humanities}\gdef\@journalshort{Humanities}\gdef\@doiabbr{h}\gdef\@ISSN{2076-0787}}
\DeclareOption{humans}{\gdef\@journal{humans}\gdef\@journalfull{Humans}\gdef\@journalshort{Humans}\gdef\@doiabbr{humans}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{hydrobiology}{\gdef\@journal{hydrobiology}\gdef\@journalfull{Hydrobiology}\gdef\@journalshort{Hydrobiology	}\gdef\@doiabbr{hydrobiology}\gdef\@ISSN{2673-9917}\gdef\@continuouspages{yes}}
\DeclareOption{hydrogen}{\gdef\@journal{hydrogen}\gdef\@journalfull{Hydrogen}\gdef\@journalshort{Hydrogen}\gdef\@doiabbr{hydrogen}\gdef\@ISSN{2673-4141}\gdef\@continuouspages{yes}}
\DeclareOption{hydrology}{\gdef\@journal{hydrology}\gdef\@journalfull{Hydrology}\gdef\@journalshort{Hydrology}\gdef\@doiabbr{hydrology}\gdef\@ISSN{2306-5338}}
\DeclareOption{hygiene}{\gdef\@journal{hygiene}\gdef\@journalfull{Hygiene}\gdef\@journalshort{Hygiene}\gdef\@doiabbr{hygiene}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{idr}{\gdef\@journal{idr}\gdef\@journalfull{Infectious Disease Reports}\gdef\@journalshort{Infect. Dis. Rep.}\gdef\@doiabbr{idr}\gdef\@ISSN{2036-7449}\gdef\@continuouspages{yes}}
\DeclareOption{ijerph}{\gdef\@journal{ijerph}\gdef\@journalfull{International Journal of Environmental Research and Public Health}\gdef\@journalshort{Int. J. Environ. Res. Public Health}\gdef\@doiabbr{ijerph}\gdef\@ISSN{1660-4601}}
\DeclareOption{ijfs}{\gdef\@journal{ijfs}\gdef\@journalfull{International Journal of Financial Studies}\gdef\@journalshort{Int. J. Financial Stud.}\gdef\@doiabbr{ijfs}\gdef\@ISSN{2227-7072}}
\DeclareOption{ijgi}{\gdef\@journal{ijgi}\gdef\@journalfull{ISPRS International Journal of Geo-Information}\gdef\@journalshort{ISPRS Int. J. Geo-Inf.}\gdef\@doiabbr{ijgi}\gdef\@ISSN{2220-9964}}
\DeclareOption{ijms}{\gdef\@journal{ijms}\gdef\@journalfull{International Journal of Molecular Sciences}\gdef\@journalshort{Int. J. Mol. Sci.}\gdef\@doiabbr{ijms}\gdef\@ISSN{1422-0067}}
\DeclareOption{ijns}{\gdef\@journal{ijns}\gdef\@journalfull{International Journal of Neonatal Screening}\gdef\@journalshort{Int. J. Neonatal Screen.}\gdef\@doiabbr{ijns}\gdef\@ISSN{2409-515X}}
\DeclareOption{ijtm}{\gdef\@journal{ijtm}\gdef\@journalfull{International Journal of Translational Medicine}\gdef\@journalshort{Int. J. Transl. Med.}\gdef\@doiabbr{ijtm}\gdef\@ISSN{2673-8937}\gdef\@continuouspages{yes}}
\DeclareOption{ijtpp}{\gdef\@journal{ijtpp}\gdef\@journalfull{International Journal of Turbomachinery Propulsion and Power}\gdef\@journalshort{Int. J. Turbomach. Propuls. Power}\gdef\@doiabbr{ijtpp}\gdef\@ISSN{2504-186X}}
\DeclareOption{immuno}{\gdef\@journal{immuno}\gdef\@journalfull{Immuno}\gdef\@journalshort{Immuno}\gdef\@doiabbr{immuno}\gdef\@ISSN{2673-5601}\gdef\@continuouspages{yes}}
\DeclareOption{informatics}{\gdef\@journal{informatics}\gdef\@journalfull{Informatics}\gdef\@journalshort{Informatics}\gdef\@doiabbr{informatics}\gdef\@ISSN{2227-9709}}
\DeclareOption{information}{\gdef\@journal{information}\gdef\@journalfull{Information}\gdef\@journalshort{Information}\gdef\@doiabbr{info}\gdef\@ISSN{2078-2489}}
\DeclareOption{infrastructures}{\gdef\@journal{infrastructures}\gdef\@journalfull{Infrastructures}\gdef\@journalshort{Infrastructures}\gdef\@doiabbr{infrastructures}\gdef\@ISSN{2412-3811}}
\DeclareOption{inorganics}{\gdef\@journal{inorganics}\gdef\@journalfull{Inorganics}\gdef\@journalshort{Inorganics}\gdef\@doiabbr{inorganics}\gdef\@ISSN{2304-6740}}
\DeclareOption{insects}{\gdef\@journal{insects}\gdef\@journalfull{Insects}\gdef\@journalshort{Insects}\gdef\@doiabbr{insects}\gdef\@ISSN{2075-4450}}
\DeclareOption{instruments}{\gdef\@journal{instruments}\gdef\@journalfull{Instruments}\gdef\@journalshort{Instruments}\gdef\@doiabbr{instruments}\gdef\@ISSN{2410-390X}}
\DeclareOption{inventions}{\gdef\@journal{inventions}\gdef\@journalfull{Inventions}\gdef\@journalshort{Inventions}\gdef\@doiabbr{inventions}\gdef\@ISSN{2411-5134}}
\DeclareOption{iot}{\gdef\@journal{iot}\gdef\@journalfull{IoT}\gdef\@journalshort{IoT}\gdef\@doiabbr{iot}\gdef\@ISSN{2624-831X}\gdef\@continuouspages{yes}}
\DeclareOption{j}{\gdef\@journal{j}\gdef\@journalfull{J}\gdef\@journalshort{J}\gdef\@doiabbr{j}\gdef\@ISSN{2571-8800}\gdef\@continuouspages{yes}}
\DeclareOption{jal}{\gdef\@journal{jal}\gdef\@journalfull{Journal of Ageing and Longevity}\gdef\@journalshort{J. Ageing Longev.}\gdef\@doiabbr{jal}\gdef\@ISSN{2673-9259}\gdef\@continuouspages{yes}}
\DeclareOption{jcdd}{\gdef\@journal{jcdd}\gdef\@journalfull{Journal of Cardiovascular Development and Disease}\gdef\@journalshort{J. Cardiovasc. Dev. Dis.}\gdef\@doiabbr{jcdd}\gdef\@ISSN{2308-3425}}
\DeclareOption{jcm}{\gdef\@journal{jcm}\gdef\@journalfull{Journal of Clinical Medicine}\gdef\@journalshort{J. Clin. Med.}\gdef\@doiabbr{jcm}\gdef\@ISSN{2077-0383}}
\DeclareOption{jcp}{\gdef\@journal{jcp}\gdef\@journalfull{Journal of Cybersecurity and Privacy}\gdef\@journalshort{J. Cybersecur. Priv.}\gdef\@doiabbr{jcp}\gdef\@ISSN{2624-800X}\gdef\@continuouspages{yes}}
\DeclareOption{jcs}{\gdef\@journal{jcs}\gdef\@journalfull{Journal of Composites Science}\gdef\@journalshort{J. Compos. Sci.}\gdef\@doiabbr{jcs}\gdef\@ISSN{2504-477X}}
\DeclareOption{jcto}{\gdef\@journal{jcto}\gdef\@journalfull{Journal of Clinical \& Translational Ophthalmology}\gdef\@journalshort{J. Clin. Transl. Ophthalmol.}\gdef\@doiabbr{jcto}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{jdb}{\gdef\@journal{jdb}\gdef\@journalfull{Journal of Developmental Biology}\gdef\@journalshort{J. Dev. Biol.}\gdef\@doiabbr{jdb}\gdef\@ISSN{2221-3759}}
\DeclareOption{jeta}{\gdef\@journal{jeta}\gdef\@journalfull{Journal of Experimental and Theoretical Analyses}\gdef\@journalshort{J. Exp. Theor. Anal.}\gdef\@doiabbr{jeta}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{jfb}{\gdef\@journal{jfb}\gdef\@journalfull{Journal of Functional Biomaterials}\gdef\@journalshort{J. Funct. Biomater.}\gdef\@doiabbr{jfb}\gdef\@ISSN{2079-4983}}
\DeclareOption{jfmk}{\gdef\@journal{jfmk}\gdef\@journalfull{Journal of Functional Morphology and Kinesiology}\gdef\@journalshort{J. Funct. Morphol. Kinesiol.}\gdef\@doiabbr{jfmk}\gdef\@ISSN{2411-5142}}
\DeclareOption{jimaging}{\gdef\@journal{jimaging}\gdef\@journalfull{Journal of Imaging}\gdef\@journalshort{J. Imaging}\gdef\@doiabbr{jimaging}\gdef\@ISSN{2313-433X}}
\DeclareOption{jintelligence}{\gdef\@journal{jintelligence}\gdef\@journalfull{Journal of Intelligence}\gdef\@journalshort{J. Intell.}\gdef\@doiabbr{jintelligence}\gdef\@ISSN{2079-3200}}
\DeclareOption{jlpea}{\gdef\@journal{jlpea}\gdef\@journalfull{Journal of Low Power Electronics and Applications}\gdef\@journalshort{J. Low Power Electron. Appl.}\gdef\@doiabbr{jlpea}\gdef\@ISSN{2079-9268}}
\DeclareOption{jmmp}{\gdef\@journal{jmmp}\gdef\@journalfull{Journal of Manufacturing and Materials Processing}\gdef\@journalshort{J. Manuf. Mater. Process.}\gdef\@doiabbr{jmmp}\gdef\@ISSN{2504-4494}}
\DeclareOption{jmp}{\gdef\@journal{jmp}\gdef\@journalfull{Journal of Molecular Pathology}\gdef\@journalshort{J. Mol. Pathol.}\gdef\@doiabbr{jmp}\gdef\@ISSN{2673-5261}\gdef\@continuouspages{yes}}
\DeclareOption{jmse}{\gdef\@journal{jmse}\gdef\@journalfull{Journal of Marine Science and Engineering}\gdef\@journalshort{J. Mar. Sci. Eng.}\gdef\@doiabbr{jmse}\gdef\@ISSN{2077-1312}}
\DeclareOption{jne}{\gdef\@journal{jne}\gdef\@journalfull{Journal of Nuclear Engineering}\gdef\@journalshort{J. Nucl. Eng.}\gdef\@doiabbr{jne}\gdef\@ISSN{2673-4362}\gdef\@continuouspages{yes}}
\DeclareOption{jnt}{\gdef\@journal{jnt}\gdef\@journalfull{Journal of Nanotheranostics}\gdef\@journalshort{J. Nanotheranostics}\gdef\@doiabbr{jnt}\gdef\@ISSN{2624-845X}\gdef\@continuouspages{yes}}
\DeclareOption{jof}{\gdef\@journal{jof}\gdef\@journalfull{Journal of Fungi}\gdef\@journalshort{J. Fungi}\gdef\@doiabbr{jof}\gdef\@ISSN{2309-608X}}
\DeclareOption{joitmc}{\gdef\@journal{joitmc}\gdef\@journalfull{Journal of Open Innovation: Technology Market and Complexity}\gdef\@journalshort{J. Open Innov. Technol. Mark. Complex.}\gdef\@doiabbr{joitmc}\gdef\@ISSN{2199-8531}}
\DeclareOption{jor}{\gdef\@journal{jor}\gdef\@journalfull{Journal of Respiration}\gdef\@journalshort{J. Respir.}\gdef\@doiabbr{jor}\gdef\@ISSN{2673-527X}\gdef\@continuouspages{yes}}
\DeclareOption{journalmedia}{\gdef\@journal{journalmedia}\gdef\@journalfull{Journalism and Media}\gdef\@journalshort{Journal. Media}\gdef\@doiabbr{journalmedia}\gdef\@ISSN{2673-5172}\gdef\@continuouspages{yes}}
\DeclareOption{jox}{\gdef\@journal{jox}\gdef\@journalfull{Journal of Xenobiotics}\gdef\@journalshort{J. Xenobiot.}\gdef\@doiabbr{jox}\gdef\@ISSN{2039-4713}\gdef\@continuouspages{yes}}
\DeclareOption{jpm}{\gdef\@journal{jpm}\gdef\@journalfull{Journal of Personalized Medicine}\gdef\@journalshort{J. Pers. Med.}\gdef\@doiabbr{jpm}\gdef\@ISSN{2075-4426}}
\DeclareOption{jrfm}{\gdef\@journal{jrfm}\gdef\@journalfull{Journal of Risk and Financial Management}\gdef\@journalshort{J. Risk Financial Manag.}\gdef\@doiabbr{jrfm}\gdef\@ISSN{1911-8074}}
\DeclareOption{jsan}{\gdef\@journal{jsan}\gdef\@journalfull{Journal of Sensor and Actuator Networks}\gdef\@journalshort{J. Sens. Actuator Netw.}\gdef\@doiabbr{jsan}\gdef\@ISSN{2224-2708}}
\DeclareOption{jtaer}{\gdef\@journal{jtaer}\gdef\@journalfull{Journal of Theoretical and Applied Electronic Commerce Research}\gdef\@journalshort{J. Theor. Appl. Electron. Commer. Res.}\gdef\@doiabbr{jtaer}\gdef\@ISSN{0718-1876}\gdef\@continuouspages{yes}}
\DeclareOption{jzbg}{\gdef\@journal{jzbg}\gdef\@journalfull{Journal of Zoological and Botanical Gardens}\gdef\@journalshort{J. Zool. Bot. Gard.}\gdef\@doiabbr{jzbg}\gdef\@ISSN{2673-5636}\gdef\@continuouspages{yes}}
%\DeclareOption{kidney}{\gdef\@journal{kidney}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{kidneydial}{\gdef\@journal{kidneydial}\gdef\@journalfull{Kidney and Dialysis}\gdef\@journalshort{Kidney Dial.}\gdef\@doiabbr{kidneydial}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{knowledge}{\gdef\@journal{knowledge}\gdef\@journalfull{Knowledge}\gdef\@journalshort{Knowledge}\gdef\@doiabbr{knowledge}\gdef\@ISSN{2673-9585}\gdef\@continuouspages{yes}}
\DeclareOption{land}{\gdef\@journal{land}\gdef\@journalfull{Land}\gdef\@journalshort{Land}\gdef\@doiabbr{land}\gdef\@ISSN{2073-445X}}
\DeclareOption{languages}{\gdef\@journal{languages}\gdef\@journalfull{Languages}\gdef\@journalshort{Languages}\gdef\@doiabbr{languages}\gdef\@ISSN{2226-471X}}
\DeclareOption{laws}{\gdef\@journal{laws}\gdef\@journalfull{Laws}\gdef\@journalshort{Laws}\gdef\@doiabbr{laws}\gdef\@ISSN{2075-471X}}
\DeclareOption{life}{\gdef\@journal{life}\gdef\@journalfull{Life}\gdef\@journalshort{Life}\gdef\@doiabbr{life}\gdef\@ISSN{2075-1729}}
\DeclareOption{liquids}{\gdef\@journal{liquids}\gdef\@journalfull{Liquids}\gdef\@journalshort{Liquids}\gdef\@doiabbr{liquids}\gdef\@ISSN{2673-8015}\gdef\@continuouspages{yes}}
\DeclareOption{literature}{\gdef\@journal{literature}\gdef\@journalfull{Literature}\gdef\@journalshort{Literature}\gdef\@doiabbr{literature}\gdef\@ISSN{2410-9789}\gdef\@continuouspages{yes}}
\DeclareOption{livers}{\gdef\@journal{livers}\gdef\@journalfull{Livers}\gdef\@journalshort{Livers}\gdef\@doiabbr{livers}\gdef\@ISSN{2673-4389}\gdef\@continuouspages{yes}}
\DeclareOption{logics}{\gdef\@journal{logics}\gdef\@journalfull{Logics}\gdef\@journalshort{Logics}\gdef\@doiabbr{logics}\gdef\@ISSN{2813-0405}\gdef\@continuouspages{yes}}
\DeclareOption{logistics}{\gdef\@journal{logistics}\gdef\@journalfull{Logistics}\gdef\@journalshort{Logistics}\gdef\@doiabbr{logistics}\gdef\@ISSN{2305-6290}}
\DeclareOption{lubricants}{\gdef\@journal{lubricants}\gdef\@journalfull{Lubricants}\gdef\@journalshort{Lubricants}\gdef\@doiabbr{lubricants}\gdef\@ISSN{2075-4442}}
\DeclareOption{lymphatics}{\gdef\@journal{lymphatics}\gdef\@journalfull{Lymphatics}\gdef\@journalshort{Lymphatics}\gdef\@doiabbr{lymphatics}\gdef\@ISSN{}\gdef\@continuouspages{yes}}	
\DeclareOption{machines}{\gdef\@journal{machines}\gdef\@journalfull{Machines}\gdef\@journalshort{Machines}\gdef\@doiabbr{machines}\gdef\@ISSN{2075-1702}}
\DeclareOption{macromol}{\gdef\@journal{macromol}\gdef\@journalfull{Macromol}\gdef\@journalshort{Macromol}\gdef\@doiabbr{macromol}\gdef\@ISSN{2673-6209}\gdef\@continuouspages{yes}}
\DeclareOption{magnetism}{\gdef\@journal{magnetism}\gdef\@journalfull{Magnetism}\gdef\@journalshort{Magnetism}\gdef\@doiabbr{magnetism}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{magnetochemistry}{\gdef\@journal{magnetochemistry}\gdef\@journalfull{Magnetochemistry}\gdef\@journalshort{Magnetochemistry}\gdef\@doiabbr{magnetochemistry}\gdef\@ISSN{2312-7481}}
\DeclareOption{make}{\gdef\@journal{make}\gdef\@journalfull{Machine Learning and Knowledge Extraction}\gdef\@journalshort{Mach. Learn. Knowl. Extr.}\gdef\@doiabbr{make}\gdef\@ISSN{2504-4990}\gdef\@continuouspages{yes}}
\DeclareOption{marinedrugs}{\gdef\@journal{marinedrugs}\gdef\@journalfull{Marine Drugs}\gdef\@journalshort{Mar. Drugs}\gdef\@doiabbr{md}\gdef\@ISSN{1660-3397}}
\DeclareOption{materials}{\gdef\@journal{materials}\gdef\@journalfull{Materials}\gdef\@journalshort{Materials}\gdef\@doiabbr{ma}\gdef\@ISSN{1996-1944}}
\DeclareOption{materproc}{\gdef\@journal{materproc}\gdef\@journalfull{Materials Proceedings}\gdef\@journalshort{Mater. Proc.}\gdef\@doiabbr{materproc}\gdef\@ISSN{2673-4605}}
\DeclareOption{mathematics}{\gdef\@journal{mathematics}\gdef\@journalfull{Mathematics}\gdef\@journalshort{Mathematics}\gdef\@doiabbr{math}\gdef\@ISSN{2227-7390}}
\DeclareOption{mca}{\gdef\@journal{mca}\gdef\@journalfull{Mathematical and Computational Applications}\gdef\@journalshort{Math. Comput. Appl.}\gdef\@doiabbr{mca}\gdef\@ISSN{2297-8747}}
\DeclareOption{measurements}{\gdef\@journal{measurements}\gdef\@journalfull{Measurements}\gdef\@journalshort{Measurements}\gdef\@doiabbr{measurements}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{medicina}{\gdef\@journal{medicina}\gdef\@journalfull{Medicina}\gdef\@journalshort{Medicina}\gdef\@doiabbr{medicina}\gdef\@ISSN{1648-9144}}
\DeclareOption{medicines}{\gdef\@journal{medicines}\gdef\@journalfull{Medicines}\gdef\@journalshort{Medicines}\gdef\@doiabbr{medicines}\gdef\@ISSN{2305-6320}}
\DeclareOption{medsci}{\gdef\@journal{medsci}\gdef\@journalfull{Medical Sciences}\gdef\@journalshort{Med. Sci.}\gdef\@doiabbr{medsci}\gdef\@ISSN{2076-3271}}
\DeclareOption{membranes}{\gdef\@journal{membranes}\gdef\@journalfull{Membranes}\gdef\@journalshort{Membranes}\gdef\@doiabbr{membranes}\gdef\@ISSN{2077-0375}}
\DeclareOption{merits}{\gdef\@journal{merits}\gdef\@journalfull{Merits}\gdef\@journalshort{Merits}\gdef\@doiabbr{merits}\gdef\@ISSN{2673-8104}\gdef\@continuouspages{yes}}
\DeclareOption{metabolites}{\gdef\@journal{metabolites}\gdef\@journalfull{Metabolites}\gdef\@journalshort{Metabolites}\gdef\@doiabbr{metabo}\gdef\@ISSN{2218-1989}}
\DeclareOption{metals}{\gdef\@journal{metals}\gdef\@journalfull{Metals}\gdef\@journalshort{Metals}\gdef\@doiabbr{met}\gdef\@ISSN{2075-4701}}
\DeclareOption{meteorology}{\gdef\@journal{meteorology}\gdef\@journalfull{Meteorology}\gdef\@journalshort{Meteorology}\gdef\@doiabbr{meteorology}\gdef\@ISSN{2674-0494}\gdef\@continuouspages{yes}}
\DeclareOption{methane}{\gdef\@journal{methane}\gdef\@journalfull{Methane}\gdef\@journalshort{Methane}\gdef\@doiabbr{methane}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{metrology}{\gdef\@journal{metrology}\gdef\@journalfull{Metrology}\gdef\@journalshort{Metrology}\gdef\@doiabbr{metrology}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{micro}{\gdef\@journal{micro}\gdef\@journalfull{Micro}\gdef\@journalshort{Micro}\gdef\@doiabbr{micro}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{microarrays}{\gdef\@journal{microarrays}\gdef\@journalfull{Microarrays}\gdef\@journalshort{Microarrays}\gdef\@doiabbr{microarrays}\gdef\@ISSN{2076-3905}}
\DeclareOption{microbiolres}{\gdef\@journal{microbiolres}\gdef\@journalfull{Microbiology Research}\gdef\@journalshort{Microbiol. Res.}\gdef\@doiabbr{microbiolres}\gdef\@ISSN{2036-7481}\gdef\@continuouspages{yes}}
\DeclareOption{micromachines}{\gdef\@journal{micromachines}\gdef\@journalfull{Micromachines}\gdef\@journalshort{Micromachines}\gdef\@doiabbr{mi}\gdef\@ISSN{2072-666X}}
\DeclareOption{microorganisms}{\gdef\@journal{microorganisms}\gdef\@journalfull{Microorganisms}\gdef\@journalshort{Microorganisms}\gdef\@doiabbr{microorganisms}\gdef\@ISSN{2076-2607}}
\DeclareOption{microplastics}{\gdef\@journal{microplastics}\gdef\@journalfull{Microplastics}\gdef\@journalshort{Microplastics}\gdef\@doiabbr{microplastics}\gdef\@ISSN{2673-8929}\gdef\@continuouspages{yes}}
\DeclareOption{minerals}{\gdef\@journal{minerals}\gdef\@journalfull{Minerals}\gdef\@journalshort{Minerals}\gdef\@doiabbr{min}\gdef\@ISSN{2075-163X}}
\DeclareOption{mining}{\gdef\@journal{mining}\gdef\@journalfull{Mining}\gdef\@journalshort{Mining}\gdef\@doiabbr{mining}\gdef\@ISSN{2673-6489}\gdef\@continuouspages{yes}}
\DeclareOption{modelling}{\gdef\@journal{modelling}\gdef\@journalfull{Modelling}\gdef\@journalshort{Modelling}\gdef\@doiabbr{modelling}\gdef\@ISSN{2673-3951}\gdef\@continuouspages{yes}}
\DeclareOption{molbank}{\gdef\@journal{molbank}\gdef\@journalfull{Molbank}\gdef\@journalshort{Molbank}\gdef\@doiabbr{M}\gdef\@ISSN{1422-8599}}
\DeclareOption{molecules}{\gdef\@journal{molecules}\gdef\@journalfull{Molecules}\gdef\@journalshort{Molecules}\gdef\@doiabbr{molecules}\gdef\@ISSN{1420-3049}}
\DeclareOption{mps}{\gdef\@journal{mps}\gdef\@journalfull{Methods and Protocols}\gdef\@journalshort{Methods Protoc.}\gdef\@doiabbr{mps}\gdef\@ISSN{2409-9279}}
\DeclareOption{msf}{\gdef\@journal{msf}\gdef\@journalfull{Medical Sciences Forum}\gdef\@journalshort{Med. Sci. Forum}\gdef\@doiabbr{msf}\gdef\@ISSN{2673-9992}}
\DeclareOption{mti}{\gdef\@journal{mti}\gdef\@journalfull{Multimodal Technologies and Interaction}\gdef\@journalshort{Multimodal Technol. Interact.}\gdef\@doiabbr{mti}\gdef\@ISSN{2414-4088}}
\DeclareOption{muscles}{\gdef\@journal{muscles}\gdef\@journalfull{Muscles}\gdef\@journalshort{Muscles}\gdef\@doiabbr{muscles}\gdef\@ISSN{2813-0413}\gdef\@continuouspages{yes}}
\DeclareOption{nanoenergyadv}{\gdef\@journal{nanoenergyadv}\gdef\@journalfull{Nanoenergy Advances}\gdef\@journalshort{Nanoenergy Adv.}\gdef\@doiabbr{nanoenergyadv}\gdef\@ISSN{2673-706X}\gdef\@continuouspages{yes}}
\DeclareOption{nanomanufacturing}{\gdef\@journal{nanomanufacturing}\gdef\@journalfull{Nanomanufacturing}\gdef\@journalshort{Nanomanufacturing}\gdef\@doiabbr{nanomanufacturing}\gdef\@ISSN{2673-687X}\gdef\@continuouspages{yes}}
\DeclareOption{nanomaterials}{\gdef\@journal{nanomaterials}\gdef\@journalfull{Nanomaterials}\gdef\@journalshort{Nanomaterials}\gdef\@doiabbr{nano}\gdef\@ISSN{2079-4991}}
\DeclareOption{ncrna}{\gdef\@journal{ncrna}\gdef\@journalfull{Non-coding RNA}\gdef\@journalshort{Non-coding RNA}\gdef\@doiabbr{ncrna}\gdef\@ISSN{2311-553X}}
\DeclareOption{network}{\gdef\@journal{network}\gdef\@journalfull{Network}\gdef\@journalshort{Network}\gdef\@doiabbr{network}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{neuroglia}{\gdef\@journal{neuroglia}\gdef\@journalfull{Neuroglia}\gdef\@journalshort{Neuroglia}\gdef\@doiabbr{neuroglia}\gdef\@ISSN{2571-6980}\gdef\@continuouspages{yes}}
\DeclareOption{neurolint}{\gdef\@journal{neurolint}\gdef\@journalfull{Neurology International}\gdef\@journalshort{Neurol. Int.}\gdef\@doiabbr{neurolint}\gdef\@ISSN{2035-8377}\gdef\@continuouspages{yes}}
\DeclareOption{neurosci}{\gdef\@journal{neurosci}\gdef\@journalfull{NeuroSci}\gdef\@journalshort{NeuroSci}\gdef\@doiabbr{neurosci}\gdef\@ISSN{2673-4087}\gdef\@continuouspages{yes}}
\DeclareOption{nitrogen}{\gdef\@journal{nitrogen}\gdef\@journalfull{Nitrogen}\gdef\@journalshort{Nitrogen}\gdef\@doiabbr{nitrogen}\gdef\@ISSN{2504-3129}\gdef\@continuouspages{yes}}
\DeclareOption{notspecified}{\gdef\@journal{notspecified}\gdef\@journalfull{Journal Not Specified}\gdef\@journalshort{Journal Not Specified}\gdef\@doiabbr{}\gdef\@ISSN{}}
%%\DeclareOption{nri}{\gdef\@journal{nri}\gdef\@journalfull{Natural Resources Informatics}\gdef\@journalshort{Nat. Resour. Inform.}\gdef\@doiabbr{nri}\gdef\@ISSN{2673-981X}\gdef\@continuouspages{yes}}
\DeclareOption{nursrep}{\gdef\@journal{nursrep}\gdef\@journalfull{Nursing Reports}\gdef\@journalshort{Nurs. Rep.}\gdef\@doiabbr{nursrep}\gdef\@ISSN{2039-4403}\gdef\@continuouspages{yes}}
\DeclareOption{nutraceuticals}{\gdef\@journal{nutraceuticals}\gdef\@journalfull{Nutraceuticals}\gdef\@journalshort{Nutraceuticals}\gdef\@doiabbr{nutraceuticals}\gdef\@ISSN{1661-3821}\gdef\@continuouspages{yes}}
\DeclareOption{nutrients}{\gdef\@journal{nutrients}\gdef\@journalfull{Nutrients}\gdef\@journalshort{Nutrients}\gdef\@doiabbr{nu}\gdef\@ISSN{2072-6643}}
\DeclareOption{obesities}{\gdef\@journal{obesities}\gdef\@journalfull{Obesities}\gdef\@journalshort{Obesities}\gdef\@doiabbr{obesities}\gdef\@ISSN{2673-4168}\gdef\@continuouspages{yes}}
\DeclareOption{oceans}{\gdef\@journal{oceans}\gdef\@journalfull{Oceans}\gdef\@journalshort{Oceans}\gdef\@doiabbr{oceans}\gdef\@ISSN{2673-1924}\gdef\@continuouspages{yes}}
\DeclareOption{ohbm}{\gdef\@journal{ohbm}\gdef\@journalfull{Journal of Otorhinolaryngology Hearing and Balance Medicine}\gdef\@journalshort{J. Otorhinolaryngol. Hear. Balance Med.}\gdef\@doiabbr{ohbm}\gdef\@ISSN{2504-463X}}
\DeclareOption{onco}{\gdef\@journal{onco}\gdef\@journalfull{Onco}\gdef\@journalshort{Onco}\gdef\@doiabbr{onco}\gdef\@ISSN{2673-7523}\gdef\@continuouspages{yes}}
%\DeclareOption{oncopathology}{\gdef\@journal{oncopathology}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{optics}{\gdef\@journal{optics}\gdef\@journalfull{Optics}\gdef\@journalshort{Optics}\gdef\@doiabbr{opt}\gdef\@ISSN{2673-3269}\gdef\@continuouspages{yes}}
\DeclareOption{oral}{\gdef\@journal{oral}\gdef\@journalfull{Oral}\gdef\@journalshort{Oral}\gdef\@doiabbr{oral}\gdef\@ISSN{2673-6373}\gdef\@continuouspages{yes}}
\DeclareOption{organics}{\gdef\@journal{organics}\gdef\@journalfull{Organics}\gdef\@journalshort{Organics}\gdef\@doiabbr{org}\gdef\@ISSN{2673-401X}\gdef\@continuouspages{yes}}
\DeclareOption{organoids}{\gdef\@journal{organoids}\gdef\@journalfull{Organoids}\gdef\@journalshort{Organoids}\gdef\@doiabbr{organoids}\gdef\@ISSN{2674-1172}\gdef\@continuouspages{yes}}
\DeclareOption{osteology}{\gdef\@journal{osteology}\gdef\@journalfull{Osteology}\gdef\@journalshort{Osteology}\gdef\@doiabbr{osteology}\gdef\@ISSN{2673-4036}\gdef\@continuouspages{yes}}
\DeclareOption{oxygen}{\gdef\@journal{oxygen}\gdef\@journalfull{Oxygen}\gdef\@journalshort{Oxygen}\gdef\@doiabbr{oxygen}\gdef\@ISSN{2673-9801}\gdef\@continuouspages{yes}}
\DeclareOption{parasites}{\gdef\@journal{parasites}\gdef\@journalfull{Parasites}\gdef\@journalshort{Parasites}\gdef\@doiabbr{parasites}\gdef\@ISSN{2673-5946}}
\DeclareOption{parasitologia}{\gdef\@journal{parasitologia}\gdef\@journalfull{Parasitologia}\gdef\@journalshort{Parasitologia}\gdef\@doiabbr{parasitologia}\gdef\@ISSN{2673-6772}\gdef\@continuouspages{yes}}
\DeclareOption{particles}{\gdef\@journal{particles}\gdef\@journalfull{Particles}\gdef\@journalshort{Particles}\gdef\@doiabbr{particles}\gdef\@ISSN{2571-712X}\gdef\@continuouspages{yes}}
\DeclareOption{pathogens}{\gdef\@journal{pathogens}\gdef\@journalfull{Pathogens}\gdef\@journalshort{Pathogens}\gdef\@doiabbr{pathogens}\gdef\@ISSN{2076-0817}}
\DeclareOption{pathophysiology}{\gdef\@journal{pathophysiology}\gdef\@journalfull{Pathophysiology}\gdef\@journalshort{Pathophysiology}\gdef\@doiabbr{pathophysiology}\gdef\@ISSN{0928-4680}\gdef\@continuouspages{yes}}
\DeclareOption{pediatrrep}{\gdef\@journal{pediatrrep}\gdef\@journalfull{Pediatric Reports}\gdef\@journalshort{Pediatr. Rep.}\gdef\@doiabbr{pediatric}\gdef\@ISSN{2036-7503}\gdef\@continuouspages{yes}}
\DeclareOption{pharmaceuticals}{\gdef\@journal{pharmaceuticals}\gdef\@journalfull{Pharmaceuticals}\gdef\@journalshort{Pharmaceuticals}\gdef\@doiabbr{ph}\gdef\@ISSN{1424-8247}}
\DeclareOption{pharmaceutics}{\gdef\@journal{pharmaceutics}\gdef\@journalfull{Pharmaceutics}\gdef\@journalshort{Pharmaceutics}\gdef\@doiabbr{pharmaceutics}\gdef\@ISSN{1999-4923}}
\DeclareOption{pharmacoepidemiology}{\gdef\@journal{pharmacoepidemiology}\gdef\@journalfull{Pharmacoepidemiology}\gdef\@journalshort{Pharmacoepidemiology}\gdef\@doiabbr{pharma}\gdef\@ISSN{2813-0618}\gdef\@continuouspages{yes}}
\DeclareOption{pharmacy}{\gdef\@journal{pharmacy}\gdef\@journalfull{Pharmacy}\gdef\@journalshort{Pharmacy}\gdef\@doiabbr{pharmacy}\gdef\@ISSN{2226-4787}}
\DeclareOption{philosophies}{\gdef\@journal{philosophies}\gdef\@journalfull{Philosophies}\gdef\@journalshort{Philosophies}\gdef\@doiabbr{philosophies}\gdef\@ISSN{2409-9287}}
\DeclareOption{photochem}{\gdef\@journal{photochem}\gdef\@journalfull{Photochem}\gdef\@journalshort{Photochem}\gdef\@doiabbr{photochem}\gdef\@ISSN{2673-7256}\gdef\@continuouspages{yes}}
\DeclareOption{photonics}{\gdef\@journal{photonics}\gdef\@journalfull{Photonics}\gdef\@journalshort{Photonics}\gdef\@doiabbr{photonics}\gdef\@ISSN{2304-6732}}
\DeclareOption{phycology}{\gdef\@journal{phycology}\gdef\@journalfull{Phycology}\gdef\@journalshort{Phycology}\gdef\@doiabbr{phycology}\gdef\@ISSN{2673-9410}\gdef\@continuouspages{yes}}
\DeclareOption{physchem}{\gdef\@journal{physchem}\gdef\@journalfull{Physchem}\gdef\@journalshort{Physchem}\gdef\@doiabbr{physchem}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{physics}{\gdef\@journal{physics}\gdef\@journalfull{Physics}\gdef\@journalshort{Physics}\gdef\@doiabbr{physics}\gdef\@ISSN{2624-8174}\gdef\@continuouspages{yes}}
\DeclareOption{physiologia}{\gdef\@journal{physiologia}\gdef\@journalfull{Physiologia}\gdef\@journalshort{Physiologia}\gdef\@doiabbr{physiologia}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{plants}{\gdef\@journal{plants}\gdef\@journalfull{Plants}\gdef\@journalshort{Plants}\gdef\@doiabbr{plants}\gdef\@ISSN{2223-7747}}
\DeclareOption{plasma}{\gdef\@journal{plasma}\gdef\@journalfull{Plasma}\gdef\@journalshort{Plasma}\gdef\@doiabbr{plasma}\gdef\@ISSN{2571-6182}\gdef\@continuouspages{yes}}
\DeclareOption{pollutants}{\gdef\@journal{pollutants}\gdef\@journalfull{Pollutants}\gdef\@journalshort{Pollutants}\gdef\@doiabbr{pollutants}\gdef\@ISSN{2673-4672}\gdef\@continuouspages{yes}}
\DeclareOption{polymers}{\gdef\@journal{polymers}\gdef\@journalfull{Polymers}\gdef\@journalshort{Polymers}\gdef\@doiabbr{polym}\gdef\@ISSN{2073-4360}}
\DeclareOption{polysaccharides}{\gdef\@journal{polysaccharides}\gdef\@journalfull{Polysaccharides}\gdef\@journalshort{Polysaccharides}\gdef\@doiabbr{polysaccharides}\gdef\@ISSN{2673-4176}\gdef\@continuouspages{yes}}
\DeclareOption{poultry}{\gdef\@journal{poultry}\gdef\@journalfull{Poultry}\gdef\@journalshort{Poultry}\gdef\@doiabbr{poultry}\gdef\@ISSN{2674-1164}\gdef\@continuouspages{yes}}
\DeclareOption{powders}{\gdef\@journal{powders}\gdef\@journalfull{Powders}\gdef\@journalshort{Powders}\gdef\@doiabbr{powders}\gdef\@ISSN{2674-0516}\gdef\@continuouspages{yes}}
\DeclareOption{preprints}{\gdef\@journal{preprints}\gdef\@journalfull{Preprints}\gdef\@journalshort{Preprints}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{proceedings}{\gdef\@journal{proceedings}\gdef\@journalfull{Proceedings}\gdef\@journalshort{Proceedings}\gdef\@doiabbr{proceedings}\gdef\@ISSN{2504-3900}}
\DeclareOption{processes}{\gdef\@journal{processes}\gdef\@journalfull{Processes}\gdef\@journalshort{Processes}\gdef\@doiabbr{pr}\gdef\@ISSN{2227-9717}}
\DeclareOption{prosthesis}{\gdef\@journal{prosthesis}\gdef\@journalfull{Prosthesis}\gdef\@journalshort{Prosthesis}\gdef\@doiabbr{prosthesis}\gdef\@ISSN{2673-1592}\gdef\@continuouspages{yes}}
\DeclareOption{proteomes}{\gdef\@journal{proteomes}\gdef\@journalfull{Proteomes}\gdef\@journalshort{Proteomes}\gdef\@doiabbr{proteomes}\gdef\@ISSN{2227-7382}}
\DeclareOption{psf}{\gdef\@journal{psf}\gdef\@journalfull{Physical Sciences Forum}\gdef\@journalshort{Phys. Sci. Forum}\gdef\@doiabbr{psf}\gdef\@ISSN{2673-9984}}
\DeclareOption{psych}{\gdef\@journal{psych}\gdef\@journalfull{Psych}\gdef\@journalshort{Psych}\gdef\@doiabbr{psych}\gdef\@ISSN{2624-8611}\gdef\@continuouspages{yes}}
\DeclareOption{psychiatryint}{\gdef\@journal{psychiatryint}\gdef\@journalfull{Psychiatry International}\gdef\@journalshort{Psychiatry Int.}\gdef\@doiabbr{psychiatryint}\gdef\@ISSN{2673-5318}\gdef\@continuouspages{yes}}
\DeclareOption{psychoactives}{\gdef\@journal{psychoactives}\gdef\@journalfull{Psychoactives}\gdef\@journalshort{Psychoactives}\gdef\@doiabbr{psychoactives}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{publications}{\gdef\@journal{publications}\gdef\@journalfull{Publications}\gdef\@journalshort{Publications}\gdef\@doiabbr{publications}\gdef\@ISSN{2304-6775}}
\DeclareOption{quantumrep}{\gdef\@journal{quantumrep}\gdef\@journalfull{Quantum Reports}\gdef\@journalshort{Quantum Rep.}\gdef\@doiabbr{quantum}\gdef\@ISSN{2624-960X}\gdef\@continuouspages{yes}}
\DeclareOption{quaternary}{\gdef\@journal{quaternary}\gdef\@journalfull{Quaternary}\gdef\@journalshort{Quaternary}\gdef\@doiabbr{quat}\gdef\@ISSN{2571-550X}}
\DeclareOption{qubs}{\gdef\@journal{qubs}\gdef\@journalfull{Quantum Beam Science}\gdef\@journalshort{Quantum Beam Sci.}\gdef\@doiabbr{qubs}\gdef\@ISSN{2412-382X}}
\DeclareOption{radiation}{\gdef\@journal{radiation}\gdef\@journalfull{Radiation}\gdef\@journalshort{Radiation}\gdef\@doiabbr{radiation}\gdef\@ISSN{2673-592X}\gdef\@continuouspages{yes}}
\DeclareOption{reactions}{\gdef\@journal{reactions}\gdef\@journalfull{Reactions}\gdef\@journalshort{Reactions}\gdef\@doiabbr{reactions}\gdef\@ISSN{2624-781X}\gdef\@continuouspages{yes}}
\DeclareOption{receptors}{\gdef\@journal{receptors}\gdef\@journalfull{Receptors}\gdef\@journalshort{Receptors}\gdef\@doiabbr{receptors}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{recycling}{\gdef\@journal{recycling}\gdef\@journalfull{Recycling}\gdef\@journalshort{Recycling}\gdef\@doiabbr{recycling}\gdef\@ISSN{2313-4321}}
\DeclareOption{regeneration}{\gdef\@journal{regeneration}\gdef\@journalfull{Regeneration}\gdef\@journalshort{Regeneration}\gdef\@doiabbr{regeneration}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{religions}{\gdef\@journal{religions}\gdef\@journalfull{Religions}\gdef\@journalshort{Religions}\gdef\@doiabbr{rel}\gdef\@ISSN{2077-1444}}
\DeclareOption{remotesensing}{\gdef\@journal{remotesensing}\gdef\@journalfull{Remote Sensing}\gdef\@journalshort{Remote Sens.}\gdef\@doiabbr{rs}\gdef\@ISSN{2072-4292}}
\DeclareOption{reports}{\gdef\@journal{reports}\gdef\@journalfull{Reports}\gdef\@journalshort{Reports}\gdef\@doiabbr{reports}\gdef\@ISSN{2571-841X}}
\DeclareOption{reprodmed}{\gdef\@journal{reprodmed}\gdef\@journalfull{Reproductive Medicine}\gdef\@journalshort{Reprod. Med.}\gdef\@doiabbr{reprodmed}\gdef\@ISSN{2673-3897}\gdef\@continuouspages{yes}}
\DeclareOption{resources}{\gdef\@journal{resources}\gdef\@journalfull{Resources}\gdef\@journalshort{Resources}\gdef\@doiabbr{resources}\gdef\@ISSN{2079-9276}}
\DeclareOption{rheumato}{\gdef\@journal{rheumato}\gdef\@journalfull{Rheumato}\gdef\@journalshort{Rheumato}\gdef\@doiabbr{rheumato}\gdef\@ISSN{2674-0621}\gdef\@continuouspages{yes}}
\DeclareOption{risks}{\gdef\@journal{risks}\gdef\@journalfull{Risks}\gdef\@journalshort{Risks}\gdef\@doiabbr{risks}\gdef\@ISSN{2227-9091}}
\DeclareOption{robotics}{\gdef\@journal{robotics}\gdef\@journalfull{Robotics}\gdef\@journalshort{Robotics}\gdef\@doiabbr{robotics}\gdef\@ISSN{2218-6581}}
\DeclareOption{ruminants}{\gdef\@journal{ruminants}\gdef\@journalfull{Ruminants}\gdef\@journalshort{Ruminants}\gdef\@doiabbr{ruminants}\gdef\@ISSN{2673-933X}\gdef\@continuouspages{yes}}
\DeclareOption{safety}{\gdef\@journal{safety}\gdef\@journalfull{Safety}\gdef\@journalshort{Safety}\gdef\@doiabbr{safety}\gdef\@ISSN{2313-576X}}
\DeclareOption{sci}{\gdef\@journal{sci}\gdef\@journalfull{Sci}\gdef\@journalshort{Sci}\gdef\@doiabbr{sci}\gdef\@ISSN{2413-4155}}
\DeclareOption{scipharm}{\gdef\@journal{scipharm}\gdef\@journalfull{Scientia Pharmaceutica}\gdef\@journalshort{Sci. Pharm.}\gdef\@doiabbr{scipharm}\gdef\@ISSN{2218-0532}}
\DeclareOption{seeds}{\gdef\@journal{seeds}\gdef\@journalfull{Seeds}\gdef\@journalshort{Seeds}\gdef\@doiabbr{seeds}\gdef\@ISSN{2674-1024}\gdef\@continuouspages{yes}}
\DeclareOption{sensors}{\gdef\@journal{sensors}\gdef\@journalfull{Sensors}\gdef\@journalshort{Sensors}\gdef\@doiabbr{s}\gdef\@ISSN{1424-8220}}
\DeclareOption{separations}{\gdef\@journal{separations}\gdef\@journalfull{Separations}\gdef\@journalshort{Separations}\gdef\@doiabbr{separations}\gdef\@ISSN{2297-8739}}
\DeclareOption{sexes}{\gdef\@journal{sexes}\gdef\@journalfull{Sexes}\gdef\@journalshort{Sexes}\gdef\@doiabbr{sexes}\gdef\@ISSN{2411-5118}\gdef\@continuouspages{yes}}
\DeclareOption{signals}{\gdef\@journal{signals}\gdef\@journalfull{Signals}\gdef\@journalshort{Signals}\gdef\@doiabbr{signals}\gdef\@ISSN{2624-6120}\gdef\@continuouspages{yes}}
\DeclareOption{sinusitis}{\gdef\@journal{sinusitis}\gdef\@journalfull{Sinusitis}\gdef\@journalshort{Sinusitis}\gdef\@doiabbr{sinusitis}\gdef\@ISSN{2309-107X}\gdef\@continuouspages{yes}}
\DeclareOption{skins}{\gdef\@journal{skins}\gdef\@journalfull{Skins}\gdef\@journalshort{Skins}\gdef\@doiabbr{skins}\gdef\@ISSN{}}
\DeclareOption{smartcities}{\gdef\@journal{smartcities}\gdef\@journalfull{Smart Cities}\gdef\@journalshort{Smart Cities}\gdef\@doiabbr{smartcities}\gdef\@ISSN{2624-6511}\gdef\@continuouspages{yes}}
\DeclareOption{sna}{\gdef\@journal{sna}\gdef\@journalfull{Sinusitis and Asthma}\gdef\@journalshort{Sinusitis Asthma}\gdef\@doiabbr{sna}\gdef\@ISSN{2624-7003}}
\DeclareOption{societies}{\gdef\@journal{societies}\gdef\@journalfull{Societies}\gdef\@journalshort{Societies}\gdef\@doiabbr{soc}\gdef\@ISSN{2075-4698}}
\DeclareOption{socsci}{\gdef\@journal{socsci}\gdef\@journalfull{Social Sciences}\gdef\@journalshort{Soc. Sci.}\gdef\@doiabbr{socsci}\gdef\@ISSN{2076-0760}}
\DeclareOption{software}{\gdef\@journal{software}\gdef\@journalfull{Software}\gdef\@journalshort{Software}\gdef\@doiabbr{software}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{soilsystems}{\gdef\@journal{soilsystems}\gdef\@journalfull{Soil Systems}\gdef\@journalshort{Soil Syst.}\gdef\@doiabbr{soilsystems}\gdef\@ISSN{2571-8789}}
\DeclareOption{solar}{\gdef\@journal{solar}\gdef\@journalfull{Solar}\gdef\@journalshort{Solar}\gdef\@doiabbr{solar}\gdef\@ISSN{2673-9941}\gdef\@continuouspages{yes}}
\DeclareOption{solids}{\gdef\@journal{solids}\gdef\@journalfull{Solids}\gdef\@journalshort{Solids}\gdef\@doiabbr{solids}\gdef\@ISSN{2673-6497}\gdef\@continuouspages{yes}}
\DeclareOption{sports}{\gdef\@journal{sports}\gdef\@journalfull{Sports}\gdef\@journalshort{Sports}\gdef\@doiabbr{sports}\gdef\@ISSN{2075-4663}}
\DeclareOption{standards}{\gdef\@journal{standards}\gdef\@journalfull{Standards}\gdef\@journalshort{Standards}\gdef\@doiabbr{standards}\gdef\@ISSN{2305-6703}\gdef\@continuouspages{yes}}
\DeclareOption{stats}{\gdef\@journal{stats}\gdef\@journalfull{Stats}\gdef\@journalshort{Stats}\gdef\@doiabbr{stats}\gdef\@ISSN{2571-905X}\gdef\@continuouspages{yes}}
\DeclareOption{stresses}{\gdef\@journal{stresses}\gdef\@journalfull{Stresses}\gdef\@journalshort{Stresses}\gdef\@doiabbr{stresses}\gdef\@ISSN{2673-7140}\gdef\@continuouspages{yes}}
\DeclareOption{surfaces}{\gdef\@journal{surfaces}\gdef\@journalfull{Surfaces}\gdef\@journalshort{Surfaces}\gdef\@doiabbr{surfaces}\gdef\@ISSN{2571-9637}\gdef\@continuouspages{yes}}
\DeclareOption{surgeries}{\gdef\@journal{surgeries}\gdef\@journalfull{Surgeries}\gdef\@journalshort{Surgeries}\gdef\@doiabbr{surgeries}\gdef\@ISSN{2017-2017}\gdef\@continuouspages{yes}}
\DeclareOption{suschem}{\gdef\@journal{suschem}\gdef\@journalfull{Sustainable Chemistry}\gdef\@journalshort{Sustain. Chem.}\gdef\@doiabbr{suschem}\gdef\@ISSN{2673-4079}\gdef\@continuouspages{yes}}
\DeclareOption{sustainability}{\gdef\@journal{sustainability}\gdef\@journalfull{Sustainability}\gdef\@journalshort{Sustainability}\gdef\@doiabbr{su}\gdef\@ISSN{2071-1050}}
\DeclareOption{symmetry}{\gdef\@journal{symmetry}\gdef\@journalfull{Symmetry}\gdef\@journalshort{Symmetry}\gdef\@doiabbr{sym}\gdef\@ISSN{2073-8994}}
\DeclareOption{synbio}{\gdef\@journal{synbio}\gdef\@journalfull{Synbio}\gdef\@journalshort{Synbio}\gdef\@doiabbr{synbio}\gdef\@ISSN{2674-0583}\gdef\@continuouspages{yes}}
\DeclareOption{systems}{\gdef\@journal{systems}\gdef\@journalfull{Systems}\gdef\@journalshort{Systems}\gdef\@doiabbr{systems}\gdef\@ISSN{2079-8954}}
\DeclareOption{taxonomy}{\gdef\@journal{taxonomy}\gdef\@journalfull{Taxonomy}\gdef\@journalshort{Taxonomy}\gdef\@doiabbr{taxonomy}\gdef\@ISSN{2673-6500}\gdef\@continuouspages{yes}}
\DeclareOption{technologies}{\gdef\@journal{technologies}\gdef\@journalfull{Technologies}\gdef\@journalshort{Technologies}\gdef\@doiabbr{technologies}\gdef\@ISSN{2227-7080}}
\DeclareOption{telecom}{\gdef\@journal{telecom}\gdef\@journalfull{Telecom}\gdef\@journalshort{Telecom}\gdef\@doiabbr{telecom}\gdef\@ISSN{2673-4001}\gdef\@continuouspages{yes}}
\DeclareOption{test}{\gdef\@journal{test}\gdef\@journalfull{Test}\gdef\@journalshort{Test}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{textiles}{\gdef\@journal{textiles}\gdef\@journalfull{Textiles}\gdef\@journalshort{Textiles}\gdef\@doiabbr{textiles}\gdef\@ISSN{2673-7248}\gdef\@continuouspages{yes}}
\DeclareOption{thalassrep}{\gdef\@journal{thalassrep}\gdef\@journalfull{Thalassemia Reports}\gdef\@journalshort{Thalass. Rep.}\gdef\@doiabbr{thalassrep}\gdef\@ISSN{2039-4365}\gdef\@continuouspages{yes}}
\DeclareOption{thermo}{\gdef\@journal{thermo}\gdef\@journalfull{Thermo}\gdef\@journalshort{Thermo}\gdef\@doiabbr{thermo}\gdef\@ISSN{2673-7264}\gdef\@continuouspages{yes}}
\DeclareOption{tomography}{\gdef\@journal{tomography}\gdef\@journalfull{Tomography}\gdef\@journalshort{Tomography}\gdef\@doiabbr{tomography}\gdef\@ISSN{2379-139X}\gdef\@continuouspages{yes}}
\DeclareOption{tourismhosp}{\gdef\@journal{tourismhosp}\gdef\@journalfull{Tourism and Hospitality}\gdef\@journalshort{Tour. Hosp.}\gdef\@doiabbr{tourhosp}\gdef\@ISSN{2673-5768}\gdef\@continuouspages{yes}}
\DeclareOption{toxics}{\gdef\@journal{toxics}\gdef\@journalfull{Toxics}\gdef\@journalshort{Toxics}\gdef\@doiabbr{toxics}\gdef\@ISSN{2305-6304}}
\DeclareOption{toxins}{\gdef\@journal{toxins}\gdef\@journalfull{Toxins}\gdef\@journalshort{Toxins}\gdef\@doiabbr{toxins}\gdef\@ISSN{2072-6651}}
\DeclareOption{transplantology}{\gdef\@journal{transplantology}\gdef\@journalfull{Transplantology}\gdef\@journalshort{Transplantology}\gdef\@doiabbr{transplantology}\gdef\@ISSN{2673-3943}\gdef\@continuouspages{yes}}
\DeclareOption{transportation}{\gdef\@journal{transportation}\gdef\@journalfull{Transportation}\gdef\@journalshort{Transportation}\gdef\@doiabbr{transportation}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{traumacare}{\gdef\@journal{traumacare}\gdef\@journalfull{Trauma Care}\gdef\@journalshort{Trauma Care}\gdef\@doiabbr{traumacare}\gdef\@ISSN{2673-866X}\gdef\@continuouspages{yes}}
\DeclareOption{traumas}{\gdef\@journal{traumas}\gdef\@journalfull{Traumas}\gdef\@journalshort{Traumas}\gdef\@doiabbr{traumas}\gdef\@ISSN{2673-7477}\gdef\@continuouspages{yes}}
\DeclareOption{tropicalmed}{\gdef\@journal{tropicalmed}\gdef\@journalfull{Tropical Medicine and Infectious Disease}\gdef\@journalshort{Trop. Med. Infect. Dis.}\gdef\@doiabbr{tropicalmed}\gdef\@ISSN{2414-6366}}
\DeclareOption{universe}{\gdef\@journal{universe}\gdef\@journalfull{Universe}\gdef\@journalshort{Universe}\gdef\@doiabbr{universe}\gdef\@ISSN{2218-1997}}
\DeclareOption{urbansci}{\gdef\@journal{urbansci}\gdef\@journalfull{Urban Science}\gdef\@journalshort{Urban Sci.}\gdef\@doiabbr{urbansci}\gdef\@ISSN{2413-8851}}
\DeclareOption{uro}{\gdef\@journal{uro}\gdef\@journalfull{Uro}\gdef\@journalshort{Uro}\gdef\@doiabbr{uro}\gdef\@ISSN{2673-4397}\gdef\@continuouspages{yes}}
\DeclareOption{vaccines}{\gdef\@journal{vaccines}\gdef\@journalfull{Vaccines}\gdef\@journalshort{Vaccines}\gdef\@doiabbr{vaccines}\gdef\@ISSN{2076-393X}}
\DeclareOption{vehicles}{\gdef\@journal{vehicles}\gdef\@journalfull{Vehicles}\gdef\@journalshort{Vehicles}\gdef\@doiabbr{vehicles}\gdef\@ISSN{2624-8921}\gdef\@continuouspages{yes}}
\DeclareOption{venereology}{\gdef\@journal{venereology}\gdef\@journalfull{Venereology}\gdef\@journalshort{Venereology}\gdef\@doiabbr{venereology}\gdef\@ISSN{2674-0710}\gdef\@continuouspages{yes}}
\DeclareOption{vetsci}{\gdef\@journal{vetsci}\gdef\@journalfull{Veterinary Sciences}\gdef\@journalshort{Vet. Sci.}\gdef\@doiabbr{vetsci}\gdef\@ISSN{2306-7381}}
\DeclareOption{vibration}{\gdef\@journal{vibration}\gdef\@journalfull{Vibration}\gdef\@journalshort{Vibration}\gdef\@doiabbr{vibration}\gdef\@ISSN{2571-631X}\gdef\@continuouspages{yes}}
\DeclareOption{virtualworlds}{\gdef\@journal{virtualworlds}\gdef\@journalfull{Virtual Worlds}\gdef\@journalshort{Virtual Worlds}\gdef\@doiabbr{virtualworlds}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{viruses}{\gdef\@journal{viruses}\gdef\@journalfull{Viruses}\gdef\@journalshort{Viruses}\gdef\@doiabbr{v}\gdef\@ISSN{1999-4915}}
\DeclareOption{vision}{\gdef\@journal{vision}\gdef\@journalfull{Vision}\gdef\@journalshort{Vision}\gdef\@doiabbr{vision}\gdef\@ISSN{2411-5150}}
\DeclareOption{waste}{\gdef\@journal{waste}\gdef\@journalfull{Waste}\gdef\@journalshort{Waste}\gdef\@doiabbr{waste}\gdef\@ISSN{2813-0391}\gdef\@continuouspages{yes}}
\DeclareOption{water}{\gdef\@journal{water}\gdef\@journalfull{Water}\gdef\@journalshort{Water}\gdef\@doiabbr{w}\gdef\@ISSN{2073-4441}}
\DeclareOption{wem}{\gdef\@journal{wem}\gdef\@journalfull{Wildlife Ecology and Management}\gdef\@journalshort{Wildl. Ecol. Manag.}\gdef\@doiabbr{}\gdef\@ISSN{1234-4321}}
\DeclareOption{wevj}{\gdef\@journal{wevj}\gdef\@journalfull{World Electric Vehicle Journal}\gdef\@journalshort{World Electr. Veh. J.}\gdef\@doiabbr{wevj}\gdef\@ISSN{2032-6653}}
\DeclareOption{wind}{\gdef\@journal{wind}\gdef\@journalfull{Wind}\gdef\@journalshort{Wind}\gdef\@doiabbr{wind}\gdef\@ISSN{2674-032X}\gdef\@continuouspages{yes}}
\DeclareOption{women}{\gdef\@journal{women}\gdef\@journalfull{Women}\gdef\@journalshort{Women}\gdef\@doiabbr{women}\gdef\@ISSN{2673-4184}\gdef\@continuouspages{yes}}
\DeclareOption{world}{\gdef\@journal{world}\gdef\@journalfull{World}\gdef\@journalshort{World}\gdef\@doiabbr{world}\gdef\@ISSN{2673-4060}\gdef\@continuouspages{yes}}
\DeclareOption{youth}{\gdef\@journal{youth}\gdef\@journalfull{Youth}\gdef\@journalshort{Youth}\gdef\@doiabbr{youth}\gdef\@ISSN{2673-995X}\gdef\@continuouspages{yes}}
\DeclareOption{zoonoticdis}{\gdef\@journal{zoonoticdis}\gdef\@journalfull{Zoonotic Diseases}\gdef\@journalshort{Zoonotic Dis.}\gdef\@doiabbr{zoonoticdis}\gdef\@ISSN{2813-0227}\gdef\@continuouspages{yes}}

### 2022-03-16 paper/MDPI_template/template.tex
Removed paper/ folder from .gitignore

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[sensors,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, alloys, analytica, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, currophthalmol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, ent, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, futureinternet, futureparasites, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, kidneydial, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology, pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
% MDPI internal commands
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2022}
\copyrightyear{2022}
%\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{} 
\dateaccepted{} 
\datepublished{} 
%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{A Deep Learning Approach for Gait Event Detection from a Single Shank-Worn IMU: Validation in Healthy and Neurological Cohorts}

% MDPI internal command: Title for citation in the left column
\TitleCitation{A Deep Learning Approach for Gait Event Detection from a Single Shank-Worn IMU: Validation in Healthy and Neurological Cohorts}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-2507-0924} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Robbin Romijnders$^{1}$\orcidA{}, Elke Warmerdam$^{2}$, Clint Hansen$^{1}$*, Gerhard Schmidt$^{3}$ and Walter Maetzler$^{1,}$}

%\longauthorlist{yes}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Robbin Romijnders, Elke Warmerdam, Clint Hansen, Gerhard Schmidt and Walter Maetzler}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Romijnders, R.; Warmerdam, E.; Hansen, C.; Schmidt, G.; Maetzler, W.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Department of Neurology, Kiel University, 24105 Kiel, Germany; r.romijnders@neurologie.uni-kiel.de (R.R.), c.hansen@neurologie.uni-kiel.de (C.H.), w.maetzler@neurologie.uni-kiel.de (W.M.)\\
$^{2}$ \quad xxxxx, xxxxx, xxxxx Homburg, Germany; elke.warmerdam@uni-saarland.de (E.W.)\\
$^{3}$ \quad Institute of Electrical Engineering and Information Technology, Faculty of Engineering, Kiel University, 24143 Kiel, Germany; gus@tf.uni-kiel.de (G.S.)}

% Contact information of the corresponding author
\corres{Correspondence: r.romijnders@neurologie.uni-kiel.de (R.R.)}

% Current address and/or shared authorship
%\firstnote{Current address: Affiliation 3.} 
%\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{A single paragraph of about 200 words maximum. For research articles, abstracts should give a pertinent overview of the work. We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: describe briefly the main methods or treatments applied; (3) Results: summarize the article's main findings; (4) Conclusions: indicate the main conclusions or interpretations. The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}

% Keywords
\keyword{keyword 1; keyword 2; keyword 3 (List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.)}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia
%\encyclopediadef{Instead of the abstract}
%\entrylink{The Link to this entry published on the encyclopedia platform.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Gait deficits are common in older adults and possibly reflect the presence of an underlying neurodegenerative disease \cite{Snijders2007,Hodgins2008}. For example, conversion to Parkinson's Disease \cite{DelDin2019} or from mild cognitive impairment to Alzheimer's Disease \cite{Koenig2017,Bertoli2018} are linked with changes in spatiotemporal gait parameters. Similarly, temporal gait parameters are different for stroke patients \cite{SchroederVon1995,Mohan2021} and patients with multiple sclerosis \cite{Griskevicius2016,Flachenecker2019} when compared to healthy controls. To objectively quantify gait deficits, stride-specific parameters such as stride time or stride length are often used \cite{Hannink2016}, where the beginning and end of a stride are determined from two successive initial contacts (ICs) of the same foot \cite{Perry2010,Whittle2012}. The IC is when the foot contacts the ground and together with the instant at which the foot leaves the ground (final contact, FC), each stride can be divided in a stance and swing phase \cite{Rueterbories2010,Bruening2014}.  The events of IC and FC, also referred to as \emph{gait events}, are commonly determined using force or pressure measuring devices \cite{Bruening2014}, or stereophotogrammetry systems based on reflective markers using a multi-camera setup \cite{Chiari2005}. These systems are relatively expensive, and restricted to usage in expertise laboratories \cite{Iosa2016,Jarchi2018}. As there is increasing evidence that gait measured in the lab does not reflect daily-life gait \cite{Hillel2019,Warmerdam2020,Atrsaei2021}, there is more and more interest in measurement systems that allow for continuous gait analysis in ambulatory settings. Therefore, the use of inertial measurement units (IMUs) is especially attractive, as these can be used to measure gait in ecologically valid environments, such as the home environment, thereby painting a more complete picture of health status \cite{DelDin2016,Shah2020} and providing clinical information that is complementary to standardized lab-based assessments \cite{Warmerdam2020,Fasano2020,Atrsaei2021,Corra2021}.

Previous research suggests that gait event detection is more accurate using an IMU worn on a lower limb (e.g., shank or foot) compared to an IMU worn on the low back \cite{BenMansour2015,Storm2016,Panebianco2018}. Now, in order to get from abstract IMU sensor readings to clinically relevant gait parameters (e.g., from accelerations and angular velocities to stride times) \cite{Hannink2016}, different algorithmic approaches have been developed in the last twenty years of clinical gait research. A recent study has evaluated a cross-section of these algorithms for different sensor locations on the lower leg and foot \cite{Niswander2021}. The algorithms were categorized according to which signals were analyzed, for example the angular velocity about the medio-lateral axis, or the accelerations along vertical and antero-posterior axis. This means the sensor readings need to be linked with the anatomical axes, that is, one needs to know which sensor axis aligns with for example the medio-lateral axis. In most approaches, it is simply assumed that due to sensor attachment the sensor axis aligns roughly with the anatomical axis of interest (\cite{Salarian2004,Sabatini2005,Jasiewicz2006,Catalfamo2010,Trojaniello2014,Maqbool2016,Romijnders2021}) or an additional calibration procedure (e.g., \cite{Ferraris1995}) is required (\cite{Greene2010,Niswander2021}). In ambulatory assessments however, study participants often attach the sensor themselves, and therefore the sensor location and alignment cannot be controlled for. Furthermore, it is unlikely that each time the sensor is (re-)attached study participants, especially those with gait deficits, perform a calibration procedure that usually consists of holding a pre-defined pose and performing some known movement sequences (TODO: reference?! Kong? Seel?).

Taken together, this drives the need for an approach that is invariant to sensor orientation, and is applicable across a variety of pathological gait patterns. As pointed out by \cite{Hannink2016}, in the field of image analysis similar requirements have been successfully addressed by algorithms that share a common underlying methodology referred to as deep learning \cite{LeCun2015,TerHaarRomeny2019}. Recent applications of deep learning algorithms have already shown improved performance in detecting gait events from marker-based motion capture when compared to conventional, often heuristics-based, algorithms \cite{Kidzinski2019,Lempereur2020,Filtjens2020}. Another study used a deep learning approach to detect gait events from either three IMUs (worn on the low back, and both ankles) or a single IMU (worn on the low back), and showed that the time error was considerably smaller for the deep learning algorithm than for a commonly applied wavelet-based approach \cite{Gadaleta2019}.

In this study, we further these works by validating this deep learning approach for detecting gait events in a heterogeneous cohort of healthy and neurologically diseased adults considering a single IMU setup, worn on the lower leg.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

\subsection{Data Collection}
Gait analyses were performed in the Universit\"{a}tsklinikum Schleswig-Holstein (UKSH) campus Kiel, Germany. The study \cite{Warmerdam2021} was approved by the ethical committee of the medical faculty at the UKSH (no: D438/18). In total, data from 160 participants were included for the current analysis, including data from young adults (YA; age: 18 - 60 years), older adults (OA; age: $>$60 years), people with Parkinson's Disease (PD; according to the UK Brain Bank criteria \cite{Gibb1988}), people with a recent ($<$4 weeks) symptomatic stroke (stroke), people with multiple sclerosis (MS; according to the McDonalds criteria \cite{Thompson2018}), people with chronic low back pain (cLBP), and people with other diagnoses that were assumed not to affect mobility (Table \ref{tab:demographics_data}). Inclusion criteria were an age of 18 years or older, and the ability to walk independently without a walking aid. Participants were excluded from the study with a Montreal Cognitive Assessment \cite{Nasreddine2005} score $<$15 and other movement disorders that affected mobility, as noticed by the clinical assessor.

\begin{table}[H] 
	\caption{\label{tab:demographics_data}Demographics data of the study participants. Age, height, and weight are presented as mean (standard deviation).}
	\newcolumntype{C}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{CCCCCC}
		\toprule
		\textbf{Group}	& \textbf{Gender}	& \textbf{Number of}	& \textbf{Age}	& \textbf{Height}	& \textbf{Weight}\\
		 & & \textbf{subjects} & years	& cm	& kg\\
		\midrule
		YA		& F		& 21	& 27 (7)	& 173 (5)	& 67 (8)\\
		 & M	& 22	& 30 (9)	& 185 (8) & 81 (13)\\ 
		\midrule
		OA		& F		& 11	& 70 (6)	& 167 (6)	& 72 (17)\\
		 & M	& 11	& 73 (6)	& 180 (6) & 83 (11)\\
		\midrule
		PD		& F		& 12	& 67 (6)	& 168 (6)	& 70 (14)\\
		 & M	& 20	& 62 (11)	& 178 (6) & 87 (13)\\
		\midrule
		MS		& F		& 12	& 37 (9)	& 174 (9)	& 75 (9)\\
		 & M	& 9	& 42 (15)	& 189 (8) & 96 (30)\\
		\midrule
		stroke	& F		& 4	& 66 (10)	& 160 (6)	& 65 (11)\\
		 & M	& 17	& 67 (17)	& 178 (7) & 84 (14)\\
		\midrule
		cLBP	& F		& 3	& 64 (10)	& 166 (5)	& 65 (5)\\
		 & M	& 7	& 63 (16)	& 178 (7) & 90 (16)\\ 
		\midrule
		other	& F		& 3	& 60 (13)	& 166 (3)	& 79 (15)\\
		 & M	& 8	& 68 (18)	& 182 (7) & 85 (13)\\ 
		\bottomrule
	\end{tabularx}
	\noindent{\footnotesize{\textbf{Group}: YA: younger adults, OA: older adults, PD: Parkinson's Disease, MS: multiple sclerosis, cLBP: chronic low back pain; \textbf{Gender}: F: female, M: male.}}
\end{table}

Participants performed three walking trials consisting of walking 5 meter at either (1) preferred speed ("\emph{Please walk at your normal walking speed.}"), (2) slow speed ("\emph{Please walk half of your normal walking speed.}"), or (3) fast speed ("\emph{Please walk as fast as possible, without running or falling.}"). The 5 meter distance was marked with two cones on both ends, and participants were asked to start walking approximately two steps before the cones on one end, and stop walking approximately two steps after passing the cones on the other end.

For the current analysis data from four IMUs (Noraxon USA Inc., myoMOTION, Scottsdale, AZ, USA) were considered, namely those that were attached laterally above the left and right ankle joint and those attached proximally at the left and right shank. IMUs were secured to participants using elastic bands with a special hold for the IMU. Furthermore, reflective markers were attached on top of the usual foot wear at the heel and toe of both feet. Marker data were recorded using a twelve-camera stereophotogrammetry system (Qualisys AB, G\"{o}teborg, Sweden) at a sampling frequency of 200 Hz. IMU data were recorded at the same sampling frequency, and both systems were synchronized using TTL signal \cite{Warmerdam2021}. For some recordings, the sampling frequency of the IMUs was erroneously set at 100 Hz, and therefore data from these trials were upsampled before further analysis.

\subsection{Data Pre-processing \label{subsec:data_preprocessing}}
\subsubsection{Reference Values}
The raw reflective marker data were first used to determine the start and end of each trial. The start of the trial was defined as the time for which the first toe marker (left or right) crossed the \emph{virtual} starting line. The end was defined as the time for which the last heel marker crossed the end line. For both marker and IMU systems, data were then cropped from start to the end of the trial.

Any remaining gaps in the marker data were filled by interpolation making use of inter-correlations between markers \cite{Federolf2013,Gloersen2016}. The data were then low-pass filtered using a double pass 6th order Butterworth filter with a cut-off frequency of 20 Hz \cite{Kormylo1974,Racz2021}. The filtered data were differentiated to get velocity signals, and timings of ICs and FCs were determined from local maxima and minima in the heel and toe vertical velocity signals \cite{Pijnappels2001,OConnor2007}. Like in \cite{Carcreff2018,Romijnders2021}, all identified ICs and FCs were manually checked using Qualisys Track Manager 2018.1 software (QTM; Qualisys AB, Göteborg, Sweden).

\subsubsection{IMU Data}
For the deep learning model, the data from randomly selected one-third of participants were used as a "training set", another one-third was used as a "validation set", and the rest was used as "test set", where randomization was stratified by both group and gender. Accelerometer and gyroscope data from the four IMUs were normalized by subtracting the channel-wise mean, and dividing by the channel-wise standard deviation. Then, for the training and validation set, the time series data were partitioned into equal length time windows of 400 samples, with an overlap of 50\% between successive windows.

\subsection{Model}
\subsubsection{Notation}
Data from the IMUs' 3D accelerometer and 3D gyroscope were used. A signal was considered a sequence of real-valued numbers: $\mathbf{x} = \begin{array}{ccccc}
	\cdots & x[n-1] & x[n] & x[n+1] & \cdots
\end{array}$, with $n = 1, \cdots, N$ the discrete-time sample index. For any given channel, e.g., acceleration in $X$-direction, the signal was denoted in vector notation as: $\mathbf{x}_{d} = \begin{bmatrix}
x_{d}[1] & x_{d}[2] & \cdots & x_{d}[N]
\end{bmatrix}^{\mathrm{T}}$, where $d$ referred to the $d$-th channel.

Data from all channels of a single IMU were collected in a $ N \times D$ data matrix, like:
\begin{equation}
	\mathbf{X} = \begin{bmatrix}
		\vdots & \vdots &  & \vdots\\
		\mathbf{x}_{1} & \mathbf{x}_{2} & \cdots & \mathbf{x}_{D}\\
		\vdots & \vdots &  & \vdots
	\end{bmatrix} = \begin{bmatrix}
		x_{1}[1] & x_{2}[1] & & x_{D}[1]\\
		x_{1}[2] & x_{2}[2] & & x_{D}[2]\\
		\vdots & \vdots & \cdots & \vdots\\
		x_{1}[N] & x_{2}[1] & & x_{D}[N]\end{bmatrix}, \quad \mathbf{X} \in \mathbb{R}^{N \times D}
	\label{eqn:train_data_single_instance}
\end{equation}

The corresponding labels (or targets) were then denoted as:
\begin{equation}
	\mathbf{y}_{\mathrm{IC}} = \begin{bmatrix}
		y_{1}[1]\\
		y_{1}[2]\\
		\vdots\\
		y_{1}[N]
	\end{bmatrix}, \quad \mathbf{y}_{\mathrm{FC}} = \begin{bmatrix}
		y_{2}[1]\\
		y_{2}[2]\\
		\vdots\\
		y_{2}[N]
	\end{bmatrix}, \quad y_{i}[n] \in [0, 1]
	\label{eqn:train_labels_single_instace}
\end{equation}

\subsubsection{Model Architecture}
The basic architecture for the deep learning model was a temporal convolutional network (TCN) \cite{Bai2018,Remy2020,Filtjens2020}. The TCN consisted of repeating blocks of dilated convolutions (CONV) \cite{YuKoltun2016,Bai2018} that were followed by batch normalization (BN) \cite{Ioffe2015}, rectified linear unit (ReLU) activation, and dropout (DropOut) \cite{Srivastava2014}. For each given dilation factor, the sequence of layers CONV-BN-ReLU-DropOut was repeated twice \cite{Remy2020}. Dilation factors were given as a sequence of increasing powers of 2, e.g., $\left\{1, 2, 4, 8\right\}$ \cite{VanDenOord2016,YuKoltun2016,Bai2018}. These repeating blocks were followed by a fully-connected (dense) layer with sigmoid activation, and outputs were predicted separately for ICs and FCs. The mean squared error (MSE) was used as loss function, and a gradient descent-based optimization algorithm with adaptive moment (Adam) optimizer was used to iteratively learn the weights \cite{Kingma2014,Schmidt2021}.

\subsubsection{Hyperparameter Optimization}
In order to find the best model architecture, hyperparameter tuning was perfomed using KerasTuner \cite{OMalley2019}. Here, the number of filters, the kernel size, and the maximum dilation factor (Table \ref{tab:hyperparameter_optimization}) were optimized for using a random search strategy \cite{Bergstra2012}.

\begin{table}[H] 
	\caption{Model hyperparameters that were optimized for, and the corresponding sets of possible values.\label{tab:hyperparameter_optimization}}
	\newcolumntype{C}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{CC}
		\toprule
		\textbf{Description}	& \textbf{Possible values}\\
		\midrule
		Number of filters	& 8, 16, 32, 64, 128\\
		Kernel size			& 3, 5, 7\\
		Dilations 			& [1, 2], [1, 2, 4], [1, 2, 4, 8]\\
		\bottomrule
	\end{tabularx}
\end{table}

The model architecture that resulted from the hyperparameter optimization was then trained on the combined set of training and validation data. The trained model was used to predict occurrence of gait events from the hold-out test set.

\subsection{Analysis}
The predictions of the model on the test set data were compared with the labels from the test set. The model performance was evaluated for (1) overall detection performance, (2) time agreement between the predicted events and the (marker-based) annotated events, (3) agreement between subsequently derived gait parameters.
\subsubsection{Overall detection performance \label{subsubsec:overall_detection_performance}}
The overall detection performance quantified how many of the annotated evens were detected by the model (true positives, TP), how many of the annotated events were not detected (false negatives, FN), and how many event that were detected, were actually not annotated (false positives, FP). From these metrics, the recall (or sensitivity), precision and F$_{1}$ score were calculated as:
\begin{equation}
	\textrm{recall} = \frac{\textrm{TP}}{\textrm{TP} + \textrm{FN}} \nonumber
	\label{eqn:recall}
\end{equation}
\begin{equation}
	\textrm{precision} = \frac{\textrm{TP}}{\textrm{TP} + \textrm{FP}} \nonumber
	\label{eqn:precision}
\end{equation}
\begin{equation}
	\textrm{F$_{1}$ score} = 2 \cdot \frac{\textrm{recall} \cdot \textrm{precision}}{\textrm{recall} + \textrm{precision}}  \nonumber
	\label{eqn:f1_score}
\end{equation}

\subsubsection{Time agreement}
For all correctly detected gait events (TP, Section \ref{subsubsec:overall_detection_performance}), the time error between the annotated and detect gait event was defined as:
\begin{equation}
	\textrm{time error} = t_{\textrm{ref}} - t_{\textrm{pred}}
	\label{eqn:time_agreement}
\end{equation}
with $t_{\mathrm{ref}}$ the gait event time from the marker-based annotations, and $t_{\mathrm{pred}}$ the gait event time from the model predictions. As a robust measure for the average time error and its spread, the median time error and the inter-quartile range (IQR) were reported \cite{OpenIntro2019}.

\subsubsection{Gait parameters}
For those trials for which all gait events were detected, and no spurious events were detected, the following stride parameters were calculated:
\begin{equation}
	\textrm{stride time} = t_{\textrm{IC}_{k}} - t_{\textrm{IC}_{k-1}}
	\label{eqn:stride_time}
\end{equation}
\begin{equation}
	\textrm{stance time} = t_{\textrm{FC}_{k}} - t_{\textrm{IC}_{k-1}}
	\label{eqn:stance_time}
\end{equation}
\begin{equation}
	\textrm{swing time} = t_{\textrm{IC}_{k}} - t_{\textrm{FC}_{k}}
	\label{eqn:swing_time}
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

\subsection{Overall detection performance}
The performance of detecting initial contacts and final contacts was objectively quantified by the number of annotated events that were detected (true positives, TP), the number of annotated events that were not detected (false negatives, FN), and the number of detected events that were not annotated (false positives, FP). From these, recall, precision and F$_{1}$ score were calculated (Table \ref{tab:overall_detection_performance}).
\begin{table}[H]
	\caption{Overall detection performance for initial contacts and final contacts as quantified by recall, precision and F$_{1}$ score.\label{tab:overall_detection_performance}}
	\begin{adjustwidth}{-\extralength}{0cm}
		\newcolumntype{C}{>{\centering\arraybackslash}X}
		\begin{tabularx}{\fulllength}{r|CCCCCC|CCCCCC}
			\toprule
			 & \multicolumn{6}{c}{\textbf{Initial contacts}}	& \multicolumn{6}{c}{\textbf{Final contacts}}\\
			\textbf{Tracked point}	& \textbf{TP}	& \textbf{FN}	& \textbf{FP}	& \textbf{recall}	& \textbf{precision}	& \textbf{F1}	& \textbf{TP}	& \textbf{FN}	& \textbf{FP}	& \textbf{recall}	& \textbf{precision} 	& \textbf{F1}\\
			\midrule
			left ankle		& 624	& 19	& 5		& 97\%	& 99\%	& 98\%		& 606	& 32	& 10	& 95\%	& 98\%	& 97\%\\
			right ankle		& 599	& 42	& 8 	& 93\%	& 99\%	& 96\%		& 614	& 17	& 12	& 97\%	& 98\%	& 98\%\\
			left shank		& 605	& 38	& 15	& 94\%	& 98\%	& 96\%		& 585	& 53	& 18	& 92\%	& 97\%	& 94\%\\
			right shank		& 603	& 36	& 15 	& 94\%	& 98\%	& 96\%		& 595	& 30	& 9		& 95\%	& 99\%	& 97\%\\
			\bottomrule
		\end{tabularx}
	\end{adjustwidth}
	\noindent{\footnotesize{TP: true positives, FN: false negatives, FP: false positives, F1: F$_{1}$ score.}}
\end{table}

For both ICs and FCs, recall is high for each of the tracked points (i.e, $\ge 92\%$), and so is precision (i.e, $\ge 97\%$). Differences between the tracked points are small, i.e. the minimum recall is $92\%$ and the maximum recall is $97\%$, and the minimum precision is $97\%$ and the maximum precision is $99\%$.

\subsection{Time error}
\begin{figure}[H]
	\includegraphics[width=10.5 cm]{fig/box_plots_tracked_points_with_outliers.png}
	\caption{Time errors for initial (left) and final (right) contacts detection, for each of the different tracked points.\label{fig:time_error_box_plots}}
\end{figure}

Time errors for ICs and FCs are visually depicted using boxplots for each tracked point. Data were not normally distributed, thus Wilcoxon signed-rank tests were used to evaluate whether the median time error was zero.
\begin{table}[H] 
	\caption{Time errors for the correctly detected gait events. \label{tab:time_errors}}
	\newcolumntype{C}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{r|CCC|CCC}
		\toprule
		 & \multicolumn{3}{c}{\textbf{Initial contacts}} & \multicolumn{3}{c}{\textbf{Final contacts}}\\
		\textbf{Tracked point} & \textbf{median} & \textbf{IQR} & (\textbf{Q25}, \textbf{Q75}) & \textbf{median} & \textbf{IQR} & (\textbf{Q25}, \textbf{Q75})\\
		 & ms & ms &  (ms, ms) & ms & ms & (ms, ms)\\
		\midrule
		left ankle & 0 & 20 & (-10, 10) & 0 & 10 & (-5, 5)\\
		right ankle & 0 & 20 & (-15, 5) & -5 & 15 & (-10, 5)\\
		left shank & -5 & 20 & (-10, 10) & -5 & 20 & (-15, 5)\\
		right shank & -2.5 & 20 & (-15, 5) & -5 & 20 & (-15, 5)\\
		\bottomrule
	\end{tabularx}
	\noindent{\footnotesize{IQR: inter-quartile range, Q25: 25th percentile, Q75: 75th percentile.}}
\end{table}

\subsection{Gait parameters}
\begin{figure}[H]
	\begin{adjustwidth}{-\extralength}{0cm}
		\centering
		\includegraphics[width=13.5cm]{fig/bland_altman_plots_stride_params.png}
	\end{adjustwidth}
	\caption{The agreement of extracted gait parameters between the sensor-based and marker-based methods.\label{fig:gait_parameters_bland_altman_plots}}
\end{figure}

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
\subsection{Subsection}
\subsubsection{Subsubsection}

Bulleted lists look like this:
\begin{itemize}
\item	First bullet;
\item	Second bullet;
\item	Third bullet.
\end{itemize}

Numbered lists can be added as follows:
\begin{enumerate}
\item	First item; 
\item	Second item;
\item	Third item.
\end{enumerate}

The text continues here.

\subsection{Figures, Tables and Schemes}

All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, Table~\ref{tab2}, etc.

\begin{figure}[H]
\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
\caption{This is a figure. Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.\label{fig1}}
\end{figure}   
\unskip

\begin{table}[H] 
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCC}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data\\
\bottomrule
\end{tabularx}
\end{table}
\unskip

\begin{table}[H]
\caption{This is a wide table.\label{tab2}}
	\begin{adjustwidth}{-\extralength}{0cm}
		\newcolumntype{C}{>{\centering\arraybackslash}X}
		\begin{tabularx}{\fulllength}{CCCC}
			\toprule
			\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}     & \textbf{Title 4}\\
			\midrule
			Entry 1		& Data			& Data			& Data\\
			Entry 2		& Data			& Data			& Data \textsuperscript{1}\\
			\bottomrule
		\end{tabularx}
	\end{adjustwidth}
	\noindent{\footnotesize{\textsuperscript{1} This is a table footnote.}}
\end{table}

%\begin{listing}[H]
%\caption{Title of the listing}
%\rule{\columnwidth}{1pt}
%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
%\rule{\columnwidth}{1pt}
%\end{listing}

Text.

Text.

\subsection{Formatting of Mathematical Components}

This is the example 1 of equation:
\begin{linenomath}
\begin{equation}
a = 1,
\end{equation}
\end{linenomath}
the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.

This is the example 2 of equation:
\begin{adjustwidth}{-\extralength}{0cm}
\begin{equation}
a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
\end{equation}
\end{adjustwidth}

% Example of a page in landscape format (with table and table footnote).
%\startlandscape
%\begin{table}[H] %% Table in wide page
%\caption{This is a very wide table.\label{tab3}}
%	\begin{tabularx}{\textwidth}{CCCC}
%		\toprule
%		\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}	& \textbf{Title 4}\\
%		\midrule
%		Entry 1		& Data			& Data			& This cell has some longer content that runs over two lines.\\
%		Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
%		\bottomrule
%	\end{tabularx}
%	\begin{adjustwidth}{+\extralength}{0cm}
%		\noindent\footnotesize{\textsuperscript{1} This is a table footnote.}
%	\end{adjustwidth}
%\end{table}
%\finishlandscape

% Example of a figure that spans the whole page width. The same concept works for tables, too.
\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=13.5cm]{Definitions/logo-mdpi}
\end{adjustwidth}
\caption{This is a wide figure.\label{fig2}}
\end{figure}

Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
%% Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

%% Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Patents}

This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title. A supporting video article is available at doi: link.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y. and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y. All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work~reported.}

\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''. Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}

\institutionalreview{In this section, you should add the Institutional Review Board Statement and approval number, if relevant to your study. You might choose to exclude this statement if the study did not require ethical approval. Please note that the Editorial Office might ask you for further information. Please add “The study was conducted in accordance with the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving humans. OR “The animal study protocol was approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving animals. OR “Ethical review and approval were waived for this study due to REASON (please provide a detailed justification).” OR “Not applicable” for studies not involving humans or animals.}

\informedconsent{Any research article describing a study involving humans should contain this statement. Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans. You might also choose to exclude this statement if the study did not involve humans.

Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves). Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}

\dataavailability{In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study. Please refer to suggested Data Availability Statements in section ``MDPI Research Data Policies'' at \url{https://www.mdpi.com/ethics}. If the study did not report any data, you might add ``Not applicable'' here.}

\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections. This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}

\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results. Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section. If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, or in the decision to publish the~results''.}

%% Optional
\sampleavailability{Samples of the compounds ... are available from the authors.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Only for journal Encyclopedia
%\entrylink{The Link to this entry published on the encyclopedia platform.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\abbreviations{Abbreviations}{
The following abbreviations are used in this manuscript:\\

\noindent 
\begin{tabular}{@{}ll}
	cLBP & chronic low back pain\\
	CNN & convolutional neural network\\
	IMU & inertial measurement unit\\
	MS & multiple sclerosis\\
	OA & older adults\\
	PD & Parkinson's Disease\\
	TCN & temporal convolutional network\\
	YA & younger adults
\end{tabular}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixstart
\appendix
\section[\appendixname~\thesection]{}
\subsection[\appendixname~\thesubsection]{}
The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data. Mathematical proofs of results not central to the paper can be added as an appendix.

\begin{table}[H] 
\caption{This is a table caption.\label{tab5}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCC}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data\\
\bottomrule
\end{tabularx}
\end{table}

\section[\appendixname~\thesection]{}
All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{adjustwidth}{-\extralength}{0cm}
%\printendnotes[custom] % Un-comment to print a list of endnotes

\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================
%\bibliography{your_external_BibTeX_file}

%=====================================
% References, variant B: internal bibliography
%=====================================
\begin{thebibliography}{999}
	\bibitem[Snijders(2007)]{Snijders2007}
	Snijders,~A.H.; {van de Warrenburg},~B.P.; Giladi,~N.; Bloem,~B.R. Neurological gait disorders in elderly people: clinical approach and classification. {\em Lancet Neurol.} {\bf 2007}, {\em 6}(1), 63--74.
	\bibitem[Hodgins(2008)]{Hodgins2008}
	Hodgins,~D. The importance of measuring human gait. {\em Med. Device Technol.} {\bf 2008}, {\em 19}(5):42, 44-7.
	\bibitem[DelDin(2019)]{DelDin2019}
	{Del Din},~S.; Elshehabi,~M.; Galna,~B.; Hobert,~M.A.; Warmerdam,~E.; Suenkel,~U.; Brockmann,~K.; Metzger,~F.; Hansen,~C.; Berg,~D.; Rochester,~L.; Maetzler,~W. Gait analysis with wearables predicts conversion to Parkinson disease. {\em Ann. Neurol.} {\bf 2019}, {\em 86}(3), 357--367.
	\bibitem[Koenig(2017]{Koenig2017}
	K\"{o}nig,~A.; Klaming,~L.; Pijl,~M.; Demeurraux,~A.; Davis,~R.; Robert,~P. Objective measurement of gait parameters in healthy and cognitively impaired elderly using the dual-task paradigm. {\em Aging. Clin. Exp. Res.} {\bf 2017}, {\em 29}(6), 1181--1189.
	\bibitem[Bertoli(2018)]{Bertoli2018}
	Bertoli,~M.; Cereatti,~A.; Trojaniello,~D.; Avanzino,~L.; Pelosin,~E.; Del Din,~S.; Rochester,~L.; Ginis,~P.; Bekkers,~E.M.J.; Mirelman,~A.; Hausdorff,~J.M.; {Della Croce},~U. Estimation of spatio-temporal parameters of gait from magneto-inertial measurement units: multicenter validation among Parkinson, mildly cognitively impaired and healthy older adults. {\em Biomed. Eng. Online} {\bf 2018}, {\em 17}(58).
	\bibitem[SchroederVon(1995)]{SchroederVon1995}
	von Schroeder,~H.P.; Coutts,~R.D.; Lyden,~P.D.; Billings,~E.,~Jr; Nickel,~V. L. Gait parameters following stroke: a practical assessment. {\em J. Rehabil. Res. Dev.} {\bf 1995}, {\em 32}(1), 25--31.
	\bibitem[Mohan(2021)]{Mohan2021}
	Mohan,~D.M.; Khandoker,~A.H.; Wasti,~S.A.; Ismail~Ibrahim~Ismail~Alali,~S.; Jelinek,~H.F.; Khalaf,~K. Assessment methods of post-stroke gait: A scoping review of technology-driven approaches to gait characterization and analysis. {\em Front. Neurol.} {\bf 2021}, {\em 12}.
	\bibitem[Griskevicius(2016)]{Griskevicius2016}
	Gri\v{s}kevi\v{c}ius,~J.; Apanskien\.{e},~V.; \v{Z}i\v{z}ien\.{e},~J.; Daunoravi\v{c}ien\.{e},~K.; Ov\v{c}inikova,~A.; Kizlaitien\.{e},~R.; Sereik\.{e},~I.; Kaubrys,~G.; Pauk,~J.; Id\'{z}kowski,~A. Estimation of temporal gait parameters of multiple sclerosis patients in clinical setting using inertial sensors. In Proceedings of the 11th Int Conf BIOMDLORE 2016, Druskininkai, Lithuania, 20--22 Oct 2016; 80--82.
	\bibitem[Flachenecker(2019)]{Flachenecker2019}
	Flachenecker,~F.; Ga{\ss}ner,~H.; Hannik,~J.; Lee,~D.H.; Flachenecker,~P.; Winkler,~J.; Eskofier,~B.; Linker,~R.A.; Klucken,~J. Objective sensor-based gait measures reflect motor impairment in multiple sclerosis patients: Reliability and clinical validation of a wearable sensor device. {\em Mult. Scler. Relat. Dis.} {\bf 2019}, {\em 39}, 101903.
	\bibitem[Hannink(2016)]{Hannink2016}
	Hannink,~J.; Kautz,~T.; Pasluosta,~C.F.; Ga{\ss}mann,~K.-G.; Klucken,~J.; Eskofier,~B.M. Sensor-Based Gait Parameter Extraction With Deep Convolutional Neural Networks. {\em IEEE J. Biomed. Health} {\bf 2017}, {\em 21}(1), 85--93.
	\bibitem[Perry(2010)]{Perry2010}
	Perry,~J; Burnfield,~J.M. \textit{Gait analysis: normal and pathological gait}, 2nd ed.; SLACK Inc.: Thorofare, NJ, USA, 2010.
	\bibitem[Whittle(2012)]{Whittle2012}
	Richards,~J.; Levine,~D.; Whittle,~M. \textit{Whittle's Gait Analysis}, 5th ed.; Churchill Livingstone: London, UK, 2012.
	\bibitem[Rueterbories(2010)]{Rueterbories2010}
	Rueterbories,~J.; Spaich,~E.G.; Larsen,~B.; Andersen,~O.K. Methods for gait event detection and analysis in ambulatory systems. {\em Med. Eng. Phys.} {\bf 2010}, {\em 32}(6), 545--552.
	\bibitem[Bruening(2014)]{Bruening2014}
	Bruening,~D.A.; Ridge,~S.T. Automated event detection algorithms in pathological gait. {\em Gait Posture} {\bf 2014}, {\em 39}(1), 472--477.
	\bibitem[Chiari(2005)]{Chiari2005}
	Chiari,~L.; Della~Croce,~U.; Leardini,~A.; Cappozzo,~A. Human movement analysis using stereophotogrammetry: Part 2: Instrumental errors {\em Gait Posture} {\bf 2005}, {\em 21}(2), 197--211.
	\bibitem[Iosa(2016)]{Iosa2016}
	Iosa,~M.; Picerno,~P.; Paolucci,~S.; Morone,~G. Wearable inertial sensors for human movement analysis. {\em Expert Rev. Med. Devic.} {\bf 2016}, {\em 13}(7), 641--659.
	\bibitem[Jarchi(2018)]{Jarchi2018}
	Jarchi,~D.; Pope,~J.; Lee,~T.K.M.; Tamjidi,~L.; Mirzaei,~A.; Sanei,~S. A Review on Accelerometry-Based Gait Analysis and Emerging Clinical Applications. {\em IEEE Rev. Biomed. Eng.} {\bf 2018}, {\em 11}, 177--194.
	\bibitem[Hillel(2019)]{Hillel2019}
	Hillel,~I; Gazit,~E.; Nieuwboer,~A.; Avanzino,~L.; Rochester,~L.; Cereatti,~A.; Della~Croce,~U.; Rikkert,~M.O.; Bloem,~B.R.; Pelosin,~E.; Del~Din,~S.; Ginis,~P.; Giladi,~N.;  Mirelman,~A.; Hausdorff,~J.M. Is every-day walking in older adults more analogous to dual-task walking or to usual walking? Elucidating the gaps between gait performance in the lab and during 24/7 monitoring. {\em Eur. Rev. Aging Phys. A.} {\bf 2019}, {\em 16}(6).
	\bibitem[Warmerdam(2020)]{Warmerdam2020}
	Warmerdam,~E.; Hausdorff,~J.M.; Atrsaei,~A.; Zhou,~Y.; Mirelman,~A.; Aminian,~K.; Espay,~A.J.; Hansen,~C.; Evers,~L.J.W.; Keller,~A.; Lamoth,~C.; Pilotto,~A.; Rochester,~L.; Schmidt,~G.; Bloem,~B.R.; Maetzler,~W. Long-term unsupervised mobility assessment in movement disorders. {\em Lancet Neurol.} {\bf 2020}, {\em 19}(5), 462--470.
	\bibitem[Atrsaei(2021)]{Atrsaei2021}
	Atrsaei,~A.; Corr\'{a},~M.F.; Dadashi,~F.; Vila-Ch\~{a},~N.; Maia,~L.; Mariani,~B.; Maetzler,~W.; Aminian,~K. Gait speed in clinical and daily living assessments in Parkinson’s disease patients: performance versus capacity. {\em npj Parkinsons Dis.} {\bf 2021}, {\em 7}(1):24.
	\bibitem[DelDin(2016)]{DelDin2016}
	Del~Din,~S.; Godfrey,~A.; Mazz\`{a},~C.; Lord,~S.; Rochester,~L. Free-living monitoring of Parkinson's disease: Lessons from the field. {\em Movement Disord.} {\bf 2016}, {\em 31}(9), 1293--1313.
	\bibitem[Shah(2020)]{Shah2020}
	Shah,~V.V.; McNames,~J.; Mancini,~M.; Carlson-Kuhta,~P.; Nutt,~J.G.; El-Gohary,~M.; Lapidus,~J.A.; Horak,~F.B.; Curtze,~C. Digital Biomarkers of Mobility in Parkinson's Disease During Daily Living. {\em J. Parkinson Dis.} {\bf 2020}, {\em 10}(3), 1099--1111.
	\bibitem[Fasano(2020)]{Fasano2020}
	Fasano,~A.; Mancini,~M. Wearable-based mobility monitoring: the long road ahead. {\em Lancet Neurol.} {\bf 2020}, {\em 19}(5), 378--379.
	\bibitem[Corra(2021)]{Corra2021}
	Corr\'{a},~M.F.; Atrsaei,~A.; Sardoreira,~A.; Hansen,~C.; Aminian,~K.; Correia,~M.; Vila-Ch\~{a},~N.; Maetzler,~W.; Maia,~L. Comparison of Laboratory and Daily-Life Gait Speed Assessment during ON and OFF States in Parkinson’s Disease. {\em Sensors} {\bf 2021}, {\em 21}(12):3974.
	\bibitem[BenMansour(2015)]{BenMansour2015}
	Ben~Mansour,~K.; Rezzoug,~N.; Gorce,~P. Analysis of several methods and inertial sensors locations to assess gait parameters in able-bodied subjects. {\em Gait Posture} {\bf 2015}, {\em 42}, 409--414.
	\bibitem[Storm(2016)]{Storm2016}
	Storm,~F.A.; Buckley,~C.J.; Mazz\`{a},~C. Gait event detection in laboratory and real life settings: Accuracy of ankle and waist sensor based methods. {\em Gait Posture} {\bf 2016}, {\em 50}, 42--46.
	\bibitem[Panebianco(2018)]{Panebianco2018}
	Panebianco,~G.P.; Bisi,~M.C.; Stagni,~R.; Fantozzi,~S. Analysis of the performance of 17 algorithms from a systematic review: Influence of sensor position, analysed variable and computational approach in gait timing estimation from IMU measurements. {\em Gait Posture} {\bf 2018}, {\em 66}, 76--82.
	\bibitem[Niswander(2021)]{Niswander2021}
	Niswander,~W.; Kontson,~K. Evaluating the Impact of IMU Sensor Location and Walking Task on Accuracy of Gait Event Detection Algorithms. {\em Sensors} {\bf 2021}, {\em 21}(12):3989.
	\bibitem[Salarian(2004)]{Salarian2004}
	Salarian,~A.; Russmann,~H.; Vingerhoets,~F.J.; Dehollain,~C.; Blanc,~Y.; Burkhard,~P.R.; Aminian,~K. Gait assessment in Parkinson's
	disease: Toward an ambulatory system for long-term monitoring. {\em IEEE Trans. Biomed. Eng.} {\bf 2004}, {\em 51}(8), 1434--1443. 
	\bibitem[Catalfamo(2010)]{Catalfamo2010}
	Catalfamo,~P.; Ghoussayni,~S.; Ewins,~D. Gait Event Detection on Level Ground and Incline Walking Using a Rate Gyroscope. {\em Sensors} {\bf 2010}, {\em 10}(6), 5683--5702. 
	\bibitem[Sabatini(2005)]{Sabatini2005}
	Sabatini,~A.; Martelloni,~C.; Scapellato,~S.; Cavallo,~F. Assessment of Walking Features from Foot Inertial Sensing. {\em IEEE Trans. Biomed. Eng.} {\bf 2005}, {\em 52}(3), 486--494.
	\bibitem[Maqbool(2016)]{Maqbool2016}
	Maqbool,~H.F.; Husman,~M.A.B.; Awad,~M.; Abouhossein,~A.; Mehryar,~P.; Iqbal,~N.; Dehghani-Sanij,~A.A. Real-time gait event detection for lower limb amputees using a single wearable sensor. In Proceedings of the 2016 38th Ann. Int. Conf. of the IEEE Eng. in Med. Biol. Soc. (EMBC), Orlando, FL, USA, 16--20 Aug. 2016, IEEE: Piscataway, NJ, USA, 2016. 
	\bibitem[Romijnders(2021)]{Romijnders2021}
	Romijnders,~R.; Warmerdam,~E.; Hansen,~C.; Welzel,~J.; Schmidt,~G.; Maetzler,~W. Validation of IMU-based gait event detection during curved walking and turning in older adults and Parkinson's Disease patients. {\em J. Neuroeng. Rehabil.} {\bf 2021}, {\em 18}:28.
	\bibitem[Jasiewicz(2006)]{Jasiewicz2006}
	Jasiewicz,~J.M.; Allum,~J.H.; Middleton,~J.W.; Barriskill,~A.; Condie,~P.; Purcell,~B.; Li,~R.C.T. Gait event detection using linear accelerometers or angular velocity transducers in able-bodied and spinal-cord injured individuals. {\em Gait Posture} {\bf 2006}, {\em 24}(4), 502--509.
	\bibitem[Trojaniello(2014)]{Trojaniello2014}
	Trojaniello,~D.; Cereatti,~A.; Pelosin,~E.; Avanzino,~L.; Mirelman,~A.; Hausdorff,~J.M.; Della~Croce,~U. Estimation of step-by-step spatio-temporal parameters of normal and impaired gait using shank-mounted magneto-inertial sensors: Application to elderly, hemiparetic, parkinsonian and choreic gait. {\em J. Neuroeng. Rehabil.} {\bf 2014}, {\em 11}:152.
	\bibitem[Ferraris(1995)]{Ferraris1995}
	Ferraris,~F.; Grimaldi,~U.; Parvis,~M. Procedure for effortless in-field calibration of three-axis rate gyros and accelerometers. {\em Sensor. Mater.} {\bf 1995}, {\em 7}(5), 311--330.
	\bibitem[Greene(2010)]{Greene2010}
	Greene,~B.R.; McGrath,~D.; O'Neill,~R.; O'Donovan,~K.J.; Burns,~A.; Caulfield,~B. An adaptive gyroscope-based algorithm for temporal gait analysis. {\em Med. Biol. Eng. Comput.} {\bf 2010}, {\em 48}(12), 1251--1260.
	\bibitem[LeCun(2015)]{LeCun2015}
	LeCun,~Y.; Bengio,~Y.; Hinton,~G. Deep learning. {\em Nature} {\bf 2015}, {\em 521}, 436-444.
	\bibitem[TerHaarRomeny(2019)]{TerHaarRomeny2019}
	Ter Haar Romeny,~B.M. A Deeper Understanding of Deep Learning. In {\em Artificial Intelligence in Medical Imaging: Opportunities, Applications and Risks}; Ranschaert,~E.R., Morozov,~S., Algra,~P.R., Eds.; Springer Int. Publish.: Cham, Switzerland, 2019; pp. 25--38.	
	\bibitem[Kidzinski(2019)]{Kidzinski2019}
	Kidzi\'{n}ski,~{\L}.; Delp,~S.; Schwartz,~M. Automatic real-time gait event detection in children using deep neural networks. {\em PLoS ONE} {\bf 2019}, {\em 14}(1):e0211466.
	\bibitem[Lempereur(2020)]{Lempereur2020}
	Lempereur,~M.; Rousseau,~F.; R\'{e}my-N\'{e}ris,~O.; Pons,~C.; Houx,~L.; Quellec,~G.; Brochard,~S. A new deep learning-based method for the detection of gait events in children with gait disorders: Proof-of-concept and concurrent validity. {\em J. Biomech.} {\bf 2020}, {\em 98}, 109490.
	\bibitem[Filtjens(2020)]{Filtjens2020}
	Filtjens,~B.; Nieuwboer,~A.; D'cruz,~N.; Spildooren,~J.; Slaets,~P.; Vanrumste,~B. A data-driven approach for detecting gait events during turning in people with Parkinson's disease and freezing of gait. {\em Gait Posture} {\bf 2020}, {\em 80}, 130--136.
	\bibitem[Gadaleta(2019)]{Gadaleta2019}
	Gadaleta,~M.; Cisotto,~G.; Rossi,~M.; Ur~Rehman,~R.Z.; Rochester,~L.; Del~Din,~S. Deep Learning Techniques for Improving Digital Gait Segmentation. In Proceedings of the 2019 41st Ann. Int. Conf. of the IEEE Eng. in Med. Biol. Soc. (EMBC), Berlin, Germany, 23--27 Jul. 2019, IEEE: Piscataway, NJ, USA, 2019.

	% Materials and Methods
	\bibitem[Warmerdam(2021)]{Warmerdam2021}
	Warmerdam,~E.; Romijnders,~R.; Geritz,~J.; Elshehabi,~M.; Maetzler,~C.; Otto,~J.C.; Reimer,~M.; Stuerner,~K.; Baron,~R.; Paschen,~S.; Beyer,~T.; Dopcke,~D.; Eiken,~T.; Ortmann,~H.; Peters,~F.; von~der~Recke,~F.; Riesen,~M.; Rohwedder,~G.; Schaade,~A.; Schumacher,~M.; Sondermann,~A; Maetzler,~W.; Hansen,~C. Proposed Mobility Assessments with Simultaneous Full-Body Inertial Measurement Units and Optical Motion Capture in Healthy Adults and Neurological Patients for Future Validation Studies: Study Protocol. {\em Sensors} {\bf 2021}, {\em 21}(17):5833.
	\bibitem[Gibb(1988)]{Gibb1988}
	Gibb,~W.R.; Lees,~A.J. The relevance of the Lewy body to the pathogenesis of idiopathic Parkinson's disease. {\em J. Neurol. Neurosur. Ps.} {\bf 1988}, {\em 51}(6), 745--752.
	\bibitem[Thompson(2018)]{Thompson2018}
	Thompson,~A.J.; Banwell,~B.L.; Barkhof,~F.; Carroll,~W.M.; Coetzee,~T.; Comi,~G.; Correale,~J.; Fazekas,~F.; Filippi,~M.; Freedman,~M.S.; Fujihara,~K.; Galetta,~S.L.; Hartung,~H.P.; Kappos,~L.; Lublin,~F.D.; Marrie,~R.A.; Miller,~A.E.; Miller,~D.H.; Montalban,~X.; Mowry,~E.M.; Soelberg~Sorensen,~P.; Tintor\'{e},~M.; Traboulsee,~A.L.; Trojano,~M.; Uitdehaag,~B.M.J.; Vukusic,~S.; Waubant,~E.; Weinshenker,~B.G.; Reingold,~S.C.; Cohen,~J.A. Diagnosis of multiple sclerosis: 2017 revisions of the McDonald criteria. {\em Lancet Neurol.} {\bf 2018}, {\em 17}(2), 162--173.
	\bibitem[Nasreddine(2005)]{Nasreddine2005}
	Nasreddine,~Z.S.; Phillips,~N.A.; B\'{e}dirian,~V.; Charbonneau,~S.; Whitehead,~V.; Collin,~I.; Cummings,~J.L.; Chertkow,~H. The Montreal Cognitive Assessment, MoCA: A Brief Screening Tool For Mild Cognitive Impairment. {\em J. Am. Geriatr. Soc.} {\bf 2005}, {\em 53}(4), 695--699.
	\bibitem[Federolf(2013)]{Federolf2013}
	Federolf,~P.A. A Novel Approach to Solve the “Missing Marker Problem” in Marker-Based Motion Analysis That Exploits the Segment Coordination Patterns in Multi-Limb Motion Data. {\em PLoS ONE} {\bf 2013}, {\em 8}(10), 1--13.
	\bibitem[Gloersen(2016)]{Gloersen2016}
	Gl{\o}ersen,~{\O}; Federolf,~P. Predicting Missing Marker Trajectories in Human Motion Data Using Marker Intercorrelations. {\em PLoS ONE} {\bf 2016}, {\em 11}(3), 1--14.
	\bibitem[Kormylo(1974)]{Kormylo1974}
	Kormylo,~J.; Jain,~V. Two-pass recursive digital filter with zero phase shift. {\em IEEE T. Acoust. Speech} {\bf 1974}, {\em 22}(5), 384--387.
	\bibitem[Racz(2021)]{Racz2021}
	R\'{a}cz,~K.; Rita,~M.K. Marker displacement data filtering in gait analysis: A technical note. {\em Biomed. Signal Proces.} {\bf 2021}, {\em 70}:102974.
	\bibitem[Pijnappels(2001)]{Pijnappels2001}
	Pijnappels,~M.; Bobbert,~M.F.; Van Die\"{e}n,~J.H. Changes in walking pattern caused by the possibility of a tripping reaction. {\em Gait Posture} {\bf 2001}, {\em 14}(1), 11--18.
	\bibitem[OConnor(2007)]{OConnor2007}
	O'Connor,~C.M.; Thorpe,~S.K.; O'Malley,~M.J.; Vaughan,~C.L. Automatic detection of gait events using kinematic data. {\em Gait Posture} {\bf 2007}, {\em 25}(3), 469--474.
	\bibitem[Carcreff(2018)]{Carcreff2018}
	Carcreff,~L.; Gerber,~C.; Paraschiv-Ionescu,~A.; De~Coulon,~G,; Newman,~C.; Armand,~S.; Aminian,~K. What is the best configuration of wearable sensors
	to measure spatiotemporal gait parameters in children with cerebral palsy? {\em Sensors} {\bf 2018}, {\em 18}(2):394.
	\bibitem[YuKoltun(2016)]{YuKoltun2016}
	Yu,~F.; Koltun,~V. Multi-Scale Context Aggregation by Dilated Convolutions. In Proceedings of the 4th Int. Conf. on Learning Representations (ICLR), San Juan, Puerto Rico, 2--4 May 2016, Conference Track Proceedings, 2016.
	\bibitem[Bai(2018)]{Bai2018}
	Bai,~S.; Kolter,~J.Z.; Koltun,~V. An Empirical Evaluation of Generic Convolutional and Recurrent Networks for Sequence Modeling. {\em arXiv:1803.01271} {\bf 2018}.
	\bibitem[Remy(2020)]{Remy2020}
	R\'{e}my,~P. Temporal Convolutional Networks for Keras. {\em GitHub repository} {\bf 2020}, {\em GitHub}, \url{https://github.com/philipperemy/keras-tcn}.
	\bibitem[LeCun(1989)]{LeCun1989}
	LeCun,~Y.; Boser,~B.; Denker,~J.S.; Henderson,~D.; Howard,~R.E.; Hubbard,~W.; Jackel,~L.D. Backpropagation Applied to Handwritten Zip Code Recognition. {\em Neural Comput.} {\bf 1989}, {\em 1}(4), 541--551.
	\bibitem[Ioffe(2015)]{Ioffe2015}
	Ioffe,~S.; Szegedy,~C. Batch Normalization: Accelerating Deep Network Training by
	Reducing Internal Covariate Shift. {\em arXiv:1502.03167} {\bf 2015}.
	\bibitem[Srivastava(2014)]{Srivastava2014}
	Srivastava,~N.; Hinton,~G.; Krizhevsky,~A.; Sutskever,~I.; Salakhutdinov,~R. Dropout: a
	simple way to prevent neural networks from overfitting. {\em J. Mach. Learn. Res.} {\bf 2014} {\em 15}, 1929--1958.
	\bibitem[VanDenOord(2016)]{VanDenOord2016}
	van~den~Oord,~A.; Dieleman,~S.; Zen,~H.; Simonyan,~K.; Vinyals,~O.; Graves,~A.; Kalchbrenner,~N.; Senior,~A.W.; Kavukcuoglu,~K. WaveNet: A generative	model for raw audio. {\em arXiv:1609.03499} {\bf 2016}.
	\bibitem[OMalley(2019)]{OMalley2019}
	O'Malley,~T.; Bursztein,~E.; Long,~J.; Chollet,~F.; Jin,~H.; Invernizzi,~L.; and others; KerasTuner. {\em GitHub repository} {\bf 2019}, {\em GitHub}, \url{https://github.com/keras-team/keras-tuner}.
	\bibitem[Kingma(2014)]{Kingma2014}
	Kingma,~D.P.; Ba,~J. Adam: A Method for Stochastic Optimization {\em arXiv:1412.6980v9} {\bf 2014}.
	\bibitem[Schmidt(2021)]{Schmidt2021}
	Schmidt,~R.M.; Schneider,~F.; Henning,~P. Multi-Scale Context Aggregation by Dilated Convolutions. In Proceedings of the 38th Int. Conf. on Machine Learning (ICML), {\em online}, 18--24 Jul. 2021, PMLR, 2021.
	\bibitem[Bergstra(2012)]{Bergstra2012}
	Bergstra,~J.; Bengio,~Y. Random Search for Hyper-Parameter Optimization. {\em J. Mach. Learn. Res.} {\bf 2012}, {\em 13}(10), 281--305.
	\bibitem[Mishra(2019)]{Mishra2019}
	Mishra,~P.; Pandey,~C.M.; Singh,~U.; Gupta,~A.; Sahu,~C.; Keshri,~A. Descriptive Statistics and Normality Tests for Statistical Data. {\em Ann. Card. Anaesth.} {\bf 2019}, {\em 22}(1), 67--72. 	
	\bibitem[Wilcoxon(1945)]{Wilcoxon1945}
	Wilcoxon,~F. Individual Comparisons by Ranking Methods. {\em Biometrics Bull.} {\bf 1945}, {\em 1}, 80--83.
	\bibitem[McDonald(2014)]{McDonald2014}
	McDonald,~J.H. \textit{Handbook of Biological Statistics}, 3rd ed.; Sparky House Publishing: Sparky House Publishing, USA, 2014; pp. 186--189.
	\bibitem[OpenIntro(2019)]{OpenIntro2019}
	Diez,~D.; \c{C}etinkaya-Rundel,~M.; Barr,~C.D. \textit{OpenIntro Statistics}, 4th ed.; 2019. \url{https://www.openintro.org/book/os/}

	% Reference 1
	\bibitem[Author1(year)]{ref-journal}
	Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
	% Reference 2
	\bibitem[Author2(year)]{ref-book1}
	Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor 1, F., Editor 2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
	% Reference 3
	\bibitem[Author3(year)]{ref-book2}
	Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
	% Reference 4
	\bibitem[Author4(year)]{ref-unpublish}
	Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
	% Reference 5
	\bibitem[Author5(year)]{ref-communication}
	Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
	% Reference 6
	\bibitem[Author6(year)]{ref-proceeding}
	Author 1, A.B.; Author 2, C.D.; Author 3, E.F. Title of presentation. In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
	% Reference 7
	\bibitem[Author7(year)]{ref-thesis}
	Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
	% Reference 8
	\bibitem[Author8(year)]{ref-url}
	Title of Site. Available online: URL (accessed on Day Month Year).
\end{thebibliography}

% If authors have biography, please use the format below
%\section*{Short Biography of Authors}
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
%{\textbf{Firstname Lastname} Biography of first author}
%
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
%{\textbf{Firstname Lastname} Biography of second author}

% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{adjustwidth}
\end{document}

### 2022-03-16 paper/MDPI_template/article.tex
Initial draft Discussion section

--- 2022-03-16 paper/MDPI_template/template.tex
@@
 % Authors, for the paper (add full first names)
-\Author{Robbin Romijnders$^{1}$\orcidA{}, Elke Warmerdam$^{2}$, Clint Hansen$^{1}$*, Gerhard Schmidt$^{3}$ and Walter Maetzler$^{1,}$}
+\Author{Robbin Romijnders$^{1}$*\orcidA{}, Elke Warmerdam$^{2}$, Clint Hansen$^{1}$*, Gerhard Schmidt$^{3}$ and Walter Maetzler$^{1}$}
 
@@
 \subsection{Gait parameters}
+For those trials for which all gait events were correctly detected (and no spurious events were detected, i.e., no false positives), stride time, stance time and swing time were calculated.
+The mean difference and the limits of agreement between the NN-derived gait parameters and the marker-based annotations were calculated.
+
+For all stride-specific gait parameters, and for all tracked points, the mean difference compared to the marker-based reference values was close to zero, i.e., the maxmum mean difference was 0.003 s.
+Furthermore, for all gait parameters and for all tracked points the limits of agreement, based on a 95\% confidence interval were distributed around zero with the overall span between -0.049 s and 0.051 s.
+\begin{table}[H] 
+	\caption{Time agreement between the stride-specific parameters. \label{tab:stride_parameters}}
+	\newcolumntype{C}{>{\centering\arraybackslash}X}
+	\begin{tabularx}{\textwidth}{rrCC}
+		\toprule
+		\textbf{Tracked point} & \textbf{Parameters} & \textbf{Mean difference} & \textbf{Limits of Agreement}\\
+		 & & ms & (ms, ms)\\
+		\midrule
+		left ankle & stride time & 0.001 & (-0.035, 0.036)\\
+		 & stance time & 0.002 & (-0.039, 0.042)\\
+		 & swing time & -0.001 & (-0.045, 0.043)\\
+		\midrule
+		right ankle & stride time & 0.000 & (-0.039, 0.040)\\
+		 & stance time & -0.002 & (-0.048, 0.044)\\
+		 & swing time & 0.003 & (-0.046, 0.051)\\
+		\midrule
+		left shank & stride time & 0.001 & (-0.039, 0.041)\\
+		& stance time & 0.002 & (-0.043, 0.046)\\
+		& swing time & -0.001 & (-0.049, 0.047)\\
+		\midrule
+		right shank & stride time & -0.000 & (-0.031, 0.031)\\
+		& stance time & 0.002 & (-0.046, 0.049)\\
+		& swing time & -0.002 & (-0.049, 0.046)\\
+		\bottomrule
+	\end{tabularx}
+	\noindent{}
+\end{table}
+
 \begin{figure}[H]
@@
 
-This section may be divided by subheadings.
-It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
-\subsection{Subsection}
-\subsubsection{Subsubsection}
-
-Bulleted lists look like this:
-\begin{itemize}
-\item	First bullet;
-\item	Second bullet;
-\item	Third bullet.
-\end{itemize}
-
-Numbered lists can be added as follows:
-\begin{enumerate}
-\item	First item; 
-\item	Second item;
-\item	Third item.
-\end{enumerate}
-
-The text continues here.
-
-\subsection{Figures, Tables and Schemes}
-
-All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, Table~\ref{tab2}, etc.
-
-\begin{figure}[H]
-\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
-\caption{This is a figure.
-Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.\label{fig1}}
-\end{figure}   
-\unskip
-
-\begin{table}[H] 
-\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
-\newcolumntype{C}{>{\centering\arraybackslash}X}
-\begin{tabularx}{\textwidth}{CCC}
-\toprule
-\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-\midrule
-Entry 1		& Data			& Data\\
-Entry 2		& Data			& Data\\
-\bottomrule
-\end{tabularx}
-\end{table}
-\unskip
-
-\begin{table}[H]
-\caption{This is a wide table.\label{tab2}}
-	\begin{adjustwidth}{-\extralength}{0cm}
-		\newcolumntype{C}{>{\centering\arraybackslash}X}
-		\begin{tabularx}{\fulllength}{CCCC}
-			\toprule
-			\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}     & \textbf{Title 4}\\
-			\midrule
-			Entry 1		& Data			& Data			& Data\\
-			Entry 2		& Data			& Data			& Data \textsuperscript{1}\\
-			\bottomrule
-		\end{tabularx}
-	\end{adjustwidth}
-	\noindent{\footnotesize{\textsuperscript{1} This is a table footnote.}}
-\end{table}
-
-%\begin{listing}[H]
-%\caption{Title of the listing}
-%\rule{\columnwidth}{1pt}
-%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
-%\rule{\columnwidth}{1pt}
-%\end{listing}
-
-Text.
-
-Text.
-
-\subsection{Formatting of Mathematical Components}
-
-This is the example 1 of equation:
-\begin{linenomath}
-\begin{equation}
-a = 1,
-\end{equation}
-\end{linenomath}
-the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
-%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
-This ensures correct linenumbering.
-The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
-
-This is the example 2 of equation:
-\begin{adjustwidth}{-\extralength}{0cm}
-\begin{equation}
-a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
-\end{equation}
-\end{adjustwidth}
-
-% Example of a page in landscape format (with table and table footnote).
-%\startlandscape
-%\begin{table}[H] %% Table in wide page
-%\caption{This is a very wide table.\label{tab3}}
-%	\begin{tabularx}{\textwidth}{CCCC}
-%		\toprule
-%		\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}	& \textbf{Title 4}\\
-%		\midrule
-%		Entry 1		& Data			& Data			& This cell has some longer content that runs over two lines.\\
-%		Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
-%		\bottomrule
-%	\end{tabularx}
-%	\begin{adjustwidth}{+\extralength}{0cm}
-%		\noindent\footnotesize{\textsuperscript{1} This is a table footnote.}
-%	\end{adjustwidth}
-%\end{table}
-%\finishlandscape
-
-% Example of a figure that spans the whole page width. The same concept works for tables, too.
-\begin{figure}[H]
-\begin{adjustwidth}{-\extralength}{0cm}
-\centering
-\includegraphics[width=13.5cm]{Definitions/logo-mdpi}
-\end{adjustwidth}
-\caption{This is a wide figure.\label{fig2}}
-\end{figure}
-
-Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
-%% Example of a theorem:
-\begin{Theorem}
-Example text of a theorem.
-\end{Theorem}
-
-The text continues here. Proofs must be formatted as follows:
-
-%% Example of a proof:
-\begin{proof}[Proof of Theorem 1]
-Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
-\end{proof}
-The text continues here.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Discussion}
+The current study aimed to validate a deep learning approach for detecting gait events from a single IMU worn on the lower leg.
+Data from left and right ankle- and shank-worn IMUs were used for training a neural network to detect gait events from walking trials performed by healthy younger and older adults, participants diagnosed with Parkinson's Disease, multiple sclerosis, or chronic low back pain, participants who had a recent symptomatic stroke, and participants diagnosed with other neurological diseases.
+Participants walked a 5 meter distance at three different self-selected walking speeds.
+The gait event timings that were predicted by the neural network were compared to a common reference method, i.e., stereophotogrammetry, and clinically relevant stride-specific gait parameters were extracted.
 
-Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
+A first measure for the model performance was given by the recall (how many annotated events were detected) and precision (how many detected events were annotated).
+For both initial contacts and final contacts, a high recall ($\ge 95\%$) and high precision ($\ge 98\%$) were observed, meaning that most events can be detected and most detected events were actually true events.
+There was little difference in recall and precision between tracked points (Table~\ref{tab:overall_detection_performance}) confirming that the deep learning approach is relatively invariant to exact sensor localization.
+These values for recall and precision were slightly lower than our previously reported $100 \%$ \cite{Romijnders2021} that used a heuristics-based approach \cite{Salarian2004}, but in the current study more trials were included and from a more heterogeneous study population.
+
+Next, the time error, that is the difference between the annotated event and the detected event, was of interest.
+For both initial contacts and final contacts, and for all tracked points, the observed time error was small, and the middle $50\%$ of the time errors were within a range of $\left[-0.015,0.010\right]$ s (Table~\ref{tab:time_errors}, Figure~\ref{fig:time_error_box_plots}).
+These data showed that the deep learning-based is approach is precise in detecting initial and final contacts.
+Time errors were slightly smaller than our previously reported results \cite{Romijnders2021} that used a heuristics-based approach \cite{Salarian2004}.
+The heuristics-based approach determined ICs and FCs as local minima in the medio-lateral angular velocity \cite{Salarian2004} and it could be that these minima do not exactly coincide with the referent event timing as determined from the stereophotogrammetry.
+
+From the correctly detected gait events, stride-specific gait parameters were derived.
+These are probably of greatest clinical relevance, as changes in stride-specific gait parameters have been linked directly with disease onset and progression \cite{DelDin2019,Koenig2017,Bertoli2018,SchroederVon1995,Mohan2021,Griskevicius2016,Flachenecker2019}.
+Therefore, stride time, stance time, and swing time were calculated, and the differences between the deep learning-based approach and the marker-based reference method were quantified (Table~\ref{tab:stride_parameters}, Figure~\ref{fig:gait_parameters_bland_altman_plots}).
+The limits of agreement for a $95\%$ confidence interval were calculated, and for all metrics the zero mean difference was enclosed in the limit of agreement.
 
@@
 This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Patents}
-
-This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
 

### 2022-03-18 paper/MDPI_template/article.tex
Updated paper

@@
 %--------------------
-%----------
-% journal
-%----------
-% Choose between the following MDPI journals:
-% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, alloys, analytica, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, currophthalmol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, ent, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, futureinternet, futureparasites, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, kidneydial, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology, pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis
-
-%---------
-% article
-%---------
-% The default type of manuscript is "article", but can be replaced by: 
-% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
-% supfile = supplementary materials
-
 %----------
@@
 The IC is when the foot contacts the ground and together with the instant at which the foot leaves the ground (final contact, FC), each stride can be divided in a stance and swing phase \cite{Rueterbories2010,Bruening2014}.
-The events of IC and FC, also referred to as \emph{gait events}, are commonly determined using force or pressure measuring devices \cite{Bruening2014}, or stereophotogrammetry systems based on reflective markers using a multi-camera setup \cite{Chiari2005}.
+The events of IC and FC, also referred to as \emph{gait events}, are commonly determined using force or pressure measuring devices \cite{Bruening2014}, or passive, retro-reflective marker-based optoelectronic motion capture systems (henceforth referred to as the \emph{marker-based} system or method) \cite{Chiari2005,Topley2020}.
 These systems are relatively expensive, and restricted to usage in expertise laboratories \cite{Iosa2016,Jarchi2018}.
@@
 \section{Materials and Methods}
-
 \subsection{Data Collection}
@@
 
+\begin{figure}[H]
+	\begin{adjustwidth}{-\extralength}{0cm}
+		\centering
+		\includegraphics[width=13.5cm]{fig/methods_overall_workflow.pdf}
+	\end{adjustwidth}
+	\caption{Schematic depiction$^{1}$ of the current study.
+Study participants wore IMUs on the ankle and shanks, and reflective markers were adhered on the heel and toe of usual footwear (shown on the left).
+Marker data were used to obtain reference values for the timings of initial and final contacts (top), where accelerometer and gyroscope data from each tracked point were inputted to a neural network that predicted timings of the same initial and final contacts (bottom).
+\newline \noindent{\footnotesize{\textsuperscript{1} Picture from: \url{https://www.vecteezy.com/free-vector/man-walking }.}} \label{fig:methods_marker_vs_imu}}
+\end{figure}
+
 Participants performed three walking trials consisting of walking 5 meter at either (1) preferred speed ("\emph{Please walk at your normal walking speed.}"), (2) slow speed ("\emph{Please walk half of your normal walking speed.}"), or (3) fast speed ("\emph{Please walk as fast as possible, without running or falling.}").
@@
 IMUs were secured to participants using elastic bands with a special hold for the IMU.
-Furthermore, reflective markers were attached on top of the usual foot wear at the heel and toe of both feet.
-Marker data were recorded using a twelve-camera stereophotogrammetry system (Qualisys AB, G\"{o}teborg, Sweden) at a sampling frequency of 200 Hz.
-IMU data were recorded at the same sampling frequency, and both systems were synchronized using TTL signal \cite{Warmerdam2021}.
+Furthermore, reflective markers were attached on top of the usual foot wear at the heel and toe of both feet (Figure~\ref{fig:methods_marker_vs_imu}).
+Marker data were recorded using a twelve-camera optoelectronic motion capture system (Qualisys AB, G\"{o}teborg, Sweden) at a sampling frequency of 200 Hz.
+IMU data were recorded at the same sampling frequency, and both systems were synchronized using a TTL signal \cite{Warmerdam2021}.
 For some recordings, the sampling frequency of the IMUs was erroneously set at 100 Hz, and therefore data from these trials were upsampled before further analysis.
@@
 \subsection{Data Pre-processing \label{subsec:data_preprocessing}}
-\subsubsection{Reference Values}
-The raw reflective marker data were first used to determine the start and end of each trial.
+\subsubsection{Marker Data}
+The reflective marker data were first used to determine start and end of each trial.
 The start of the trial was defined as the time for which the first toe marker (left or right) crossed the \emph{virtual} starting line.
@@
 The filtered data were differentiated to get velocity signals, and timings of ICs and FCs were determined from local maxima and minima in the heel and toe vertical velocity signals \cite{Pijnappels2001,OConnor2007}.
-Like in \cite{Carcreff2018,Romijnders2021}, all identified ICs and FCs were manually checked using Qualisys Track Manager 2018.1 software (QTM; Qualisys AB, Göteborg, Sweden).
+Like in \cite{Carcreff2018,Romijnders2021}, all identified ICs and FCs were manually checked, and corrected if necessary, using Qualisys Track Manager 2018.1 software (Qualisys AB, Göteborg, Sweden).
+The resulting annotated ICs and FCs were considered the \emph{true} events (also \emph{labels} or \emph{targets}), and were used as reference timings to derive stride-specific gait parameters.
 
 \subsubsection{IMU Data}
-For the deep learning model, the data from randomly selected one-third of participants were used as a "training set", another one-third was used as a "validation set", and the rest was used as "test set", where randomization was stratified by both group and gender.
-Accelerometer and gyroscope data from the four IMUs were normalized by subtracting the channel-wise mean, and dividing by the channel-wise standard deviation.
-Then, for the training and validation set, the time series data were partitioned into equal length time windows of 400 samples, with an overlap of 50\% between successive windows.
+The idea behind the deep learning approach was that a \emph{model} was trained to predict the likelihood of an IC and FC, given accelerometer and gyroscope data from a single IMU.
+In other words, the model was iteratively trained to learn a mapping $h_{\mathbf{W}}(\mathbf{X}): \mathbf{X} \rightarrow \mathbf{y}$, where $h_{\mathbf{W}}$ was also referred to as the \emph{hypothesis} parameterized by the weights, collectively denoted by $\mathbf{W}$, $\mathbf{X}$ was the matrix of IMU data, and $\mathbf{y}$ was the vector of annotated events.
 
-\subsection{Model}
-\subsubsection{Notation}
-Data from the IMUs' 3D accelerometer and 3D gyroscope were used. A signal was considered a sequence of real-valued numbers: $\mathbf{x} = \begin{array}{ccccc}
-	\cdots & x[n-1] & x[n] & x[n+1] & \cdots
-\end{array}$, with $n = 1, \cdots, N$ the discrete-time sample index.
-For any given channel, e.g., acceleration in $X$-direction, the signal was denoted in vector notation as: $\mathbf{x}_{d} = \begin{bmatrix}
-x_{d}[1] & x_{d}[2] & \cdots & x_{d}[N]
-\end{bmatrix}^{\mathrm{T}}$, where $d$ referred to the $d$-th channel.
-
-Data from all channels of a single IMU were collected in a $ N \times D$ data matrix, like:
+Here, the matrix $\mathbf{X}$ consisted of the IMU data, arranged as:
 \begin{equation}
 	\mathbf{X} = \begin{bmatrix}
-		\vdots & \vdots &  & \vdots\\
+		\rule[0ex]{0.5pt}{2.5ex} & \rule[0ex]{0.5pt}{2.5ex} &  & \rule[0ex]{0.5pt}{2.5ex}\\
 		\mathbf{x}_{1} & \mathbf{x}_{2} & \cdots & \mathbf{x}_{D}\\
-		\vdots & \vdots &  & \vdots
+		\rule[0ex]{0.5pt}{2.5ex} & \rule[0ex]{0.5pt}{2.5ex} &  & \rule[0ex]{0.5pt}{2.5ex}
 	\end{bmatrix} = \begin{bmatrix}
@@
 \end{equation}
+where $\mathbf{x}_{d} = \begin{bmatrix}x_{d}[1] & x_{d}[2] & \cdots & x_{d}[n] & \cdots & x_{d}[N]\end{bmatrix}^{\mathrm{T}}$, with $d = 1, \cdots, D$ referred to the $d$-th channel, and $n = 1, \cdots, N$ referred to the $n$-th sample (or discrete time step).
 
-The corresponding labels (or targets) were then denoted as:
+Accordingly, the vector $\mathbf{y}$ consisted of the annotated events, arranged as:
 \begin{equation}
@@
 
+The data were split in three independent data sets, namely a training set, a validation set, and a test set.
+Each set contained data from approximately one-third of the participants.
+Participants were randomly assigned to one of the sets, stratified by both group (i.e., diagnosis) and gender (Table~\ref{tab:demographics_data}).
+
+Accelerometer and gyroscope data were normalized by subtracting the channel-wise mean, and dividing by the channel-wise standard deviation.
+Then, for the training and validation data set, the data were partitioned into equal length time windows \cite{Filtjens2020} of 400~samples, with an overlap of 50\% between successive windows (corresponding to 2 s windows, and 1 s overlap, respectively).
+
+\subsection{Model}
 \subsubsection{Model Architecture}
@@
 
-\subsubsection{Time agreement}
+\subsubsection{Time Error}
 For all correctly detected gait events (TP, Section \ref{subsubsec:overall_detection_performance}), the time error between the annotated and detect gait event was defined as:
@@
 
-\subsubsection{Gait parameters}
-For those trials for which all gait events were detected, and no spurious events were detected, the following stride parameters were calculated:
-\begin{equation}
-	\textrm{stride time} = t_{\textrm{IC}_{k}} - t_{\textrm{IC}_{k-1}}
-	\label{eqn:stride_time}
-\end{equation}
-\begin{equation}
-	\textrm{stance time} = t_{\textrm{FC}_{k}} - t_{\textrm{IC}_{k-1}}
-	\label{eqn:stance_time}
-\end{equation}
-\begin{equation}
-	\textrm{swing time} = t_{\textrm{IC}_{k}} - t_{\textrm{FC}_{k}}
-	\label{eqn:swing_time}
-\end{equation}
+\subsubsection{Stride Parameters}
+For those trials for which all gait events were detected, and no spurious events were detected, the stride time, stance time and swing were calculated.
+Stride was the time between two successive ICs of the same foot.
+Stance time was the time between FC and the preceding IC of the same foot.
+Swing time was the time between the IC following the last FC of the same foot.
 
@@
 
-For both ICs and FCs, recall is high for each of the tracked points (i.e, $\ge 92\%$), and so is precision (i.e, $\ge 97\%$).
+For both ICs and FCs, recall is high for each of the tracked points (i.e., $\ge 92\%$), and so is precision (i.e., $\ge 97\%$).
 Differences between the tracked points are small, i.e.
@@
 
-\subsection{Time error}
+\subsection{Time Error}
 \begin{figure}[H]
-	\includegraphics[width=10.5 cm]{fig/box_plots_tracked_points_with_outliers.png}
+	\centering
+	\includegraphics[width=13.5 cm]{fig/box_plots_tracked_points_with_outliers.png}
 	\caption{Time errors for initial (left) and final (right) contacts detection, for each of the different tracked points.\label{fig:time_error_box_plots}}
@@
 	\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabularx}{\textwidth}{r|CCC|CCC}
+	\begin{tabularx}{\textwidth}{r|CC|CC}
 		\toprule
-		 & \multicolumn{3}{c}{\textbf{Initial contacts}} & \multicolumn{3}{c}{\textbf{Final contacts}}\\
-		\textbf{Tracked point} & \textbf{median} & \textbf{IQR} & (\textbf{Q25}, \textbf{Q75}) & \textbf{median} & \textbf{IQR} & (\textbf{Q25}, \textbf{Q75})\\
-		 & ms & ms &  (ms, ms) & ms & ms & (ms, ms)\\
+		 & \multicolumn{2}{c}{\textbf{Initial contacts}} & \multicolumn{2}{c}{\textbf{Final contacts}}\\
+		\textbf{Tracked point} & \textbf{median} & \textbf{IQR} & \textbf{median} & \textbf{IQR}\\
+		 & s & s & s & s \\
 		\midrule
-		left ankle & 0 & 20 & (-10, 10) & 0 & 10 & (-5, 5)\\
-		right ankle & 0 & 20 & (-15, 5) & -5 & 15 & (-10, 5)\\
-		left shank & -5 & 20 & (-10, 10) & -5 & 20 & (-15, 5)\\
-		right shank & -2.5 & 20 & (-15, 5) & -5 & 20 & (-15, 5)\\
+		left ankle & 0.000 & 0.020 & 0.000 & 0.010\\
+		right ankle & 0.000 & 0.020 & -0.005 & 0.015\\
+		left shank & -0.005 & 0.020 & -0.005 & 0.020\\
+		right shank & -0.003 & 0.020 & -0.005 & 0.020\\
 		\bottomrule
 	\end{tabularx}
-	\noindent{\footnotesize{IQR: inter-quartile range, Q25: 25th percentile, Q75: 75th percentile.}}
+	\noindent{\footnotesize{IQR: inter-quartile range.}}
 \end{table}
@@
 \begin{figure}[H]
-	\begin{adjustwidth}{-\extralength}{0cm}
 	\centering
 	\includegraphics[width=13.5cm]{fig/bland_altman_plots_stride_params.png}
-	\end{adjustwidth}
 	\caption{The agreement of extracted gait parameters between the sensor-based and marker-based methods.\label{fig:gait_parameters_bland_altman_plots}}
@@
 \section{Conclusions}
-
-This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
+In this study we have validated a deep learning-based approach to detect gait events and subsequently extract clinically relevant stride parameters from a single inertial measurement unit.
+Performance analysis showed an excellent detection rate, and low time errors in both event detection and stride parameter calculation for different walking speeds and across both healthy and neurological cohorts.
+Our next step is to validate these methods under more challenging conditions, that involve real-life walking sequences.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
-The following statements should be used ``Conceptualization, X.X.
-and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y.
-and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y.
-All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation.
-Authorship must be limited to those who have contributed substantially to the work~reported.}
+\authorcontributions{Conceptualization, R.R., G.S., and W.M.; methodology, R.R., G.S.; software, R.R.; validation, R.R.,; formal analysis, R.R.; investigation, R.R., G.S., W.M.; resources, C.H, W.M..; data curation, E.W., R.R.,; writing---original draft preparation, R.R.; writing---review and editing, E.W., C.H., G.S., W.M.; visualization, R.R.; supervision, G.S., W.M.; project administration, R.R., E.W., C.H., G.S., W.M.; funding acquisition, W.M.
+All authors have read and agreed to the published version of the manuscript.}
 
-\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''.
-Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}
+\funding{This research received funding from the DFG Open Access fund.}
 
-\institutionalreview{In this section, you should add the Institutional Review Board Statement and approval number, if relevant to your study.
-You might choose to exclude this statement if the study did not require ethical approval.
-Please note that the Editorial Office might ask you for further information.
-Please add “The study was conducted in accordance with the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving humans.
-OR “The animal study protocol was approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving animals.
-OR “Ethical review and approval were waived for this study due to REASON (please provide a detailed justification).” OR “Not applicable” for studies not involving humans or animals.}
+\institutionalreview{The study was conducted in accordance with the Declaration of Helsinki, and approved by the Ethics Committee of the medical faculty of the Christian-Albrechts-Universit\"{a}t zu Kiel (D438/18, approved on 8 May 2018).}
 
-\informedconsent{Any research article describing a study involving humans should contain this statement.
-Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans.
-You might also choose to exclude this statement if the study did not involve humans.
+\informedconsent{Informed consent was obtained from all subjects involved in the study.}
 
-Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves).
-Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}
+\dataavailability{Data from the first 10 participant are available online at \url{https://github.com/neurogeriatricskiel/Validation-dataset}.
+Additionally, we are preparing the open-source release of all data from the healthy younger and older adults.
+Data from ptient groups }
 
-\dataavailability{In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study.
-Please refer to suggested Data Availability Statements in section ``MDPI Research Data Policies'' at \url{https://www.mdpi.com/ethics}.
-If the study did not report any data, you might add ``Not applicable'' here.}
+\acknowledgments{The authors sincerely thank all people that were involved in the data collection, from study participants to students who aided and assisted during measurements and subsequent marker labeling.
+The authors appreciate the off- and on-topic discussions with Julius Welzel, and his positive contributions to the organization of the research data.
+The authors give a thumbs up to Johannes Hoffmann for his tips and tricks regarding the \LaTeX typesetting.}
 
-\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections.
-This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}
-
-\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results.
-Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section.
-If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, or in the decision to publish the~results''.}
+\conflictsofinterest{The authors declare no conflict of interest.}
 
 %% Optional
-\sampleavailability{Samples of the compounds ... are available from the authors.}
+% \sampleavailability{Samples of the compounds ... are available from the authors.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Optional
-\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
-\appendixstart
-\appendix
-\section[\appendixname~\thesection]{}
-\subsection[\appendixname~\thesubsection]{}
-The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data.
+%%% Optional
+%\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A").
+If the appendix sections contain a heading then change the argument to "yes".
+%\appendixstart
+%\appendix
+%\section[\appendixname~\thesection]{}
+%\subsection[\appendixname~\thesubsection]{}
+%The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data.
 Mathematical proofs of results not central to the paper can be added as an appendix.
-
-\begin{table}[H] 
-\caption{This is a table caption.\label{tab5}}
-\newcolumntype{C}{>{\centering\arraybackslash}X}
-\begin{tabularx}{\textwidth}{CCC}
-\toprule
-\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-\midrule
-Entry 1		& Data			& Data\\
-Entry 2		& Data			& Data\\
-\bottomrule
-\end{tabularx}
-\end{table}
-
-\section[\appendixname~\thesection]{}
-All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.
+%
+%\begin{table}[H] 
+%\caption{This is a table caption.\label{tab5}}
+%\newcolumntype{C}{>{\centering\arraybackslash}X}
+%\begin{tabularx}{\textwidth}{CCC}
+%\toprule
+%\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
+%\midrule
+%Entry 1		& Data			& Data\\
+%Entry 2		& Data			& Data\\
+%\bottomrule
+%\end{tabularx}
+%\end{table}
+%
+%\section[\appendixname~\thesection]{}
+%All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.
 
@@
 	Chiari,~L.; Della~Croce,~U.; Leardini,~A.; Cappozzo,~A. Human movement analysis using stereophotogrammetry: Part 2: Instrumental errors {\em Gait Posture} {\bf 2005}, {\em 21}(2), 197--211.
+	\bibitem[Topley(2020)]{Topley2020}
+	Topley,~M.; Richards,~J.G. A A comparison of currently available optoelectronic motion capture systems. {\em J. Biomech.} {\bf 2020}, {\em 106}:109820.	
 	\bibitem[Iosa(2016)]{Iosa2016}
@@
 	Schmidt,~R.M.; Schneider,~F.; Henning,~P.
-Multi-Scale Context Aggregation by Dilated Convolutions.
+Descending through a crowded valley-benchmarking deep learning optimizers.
 In Proceedings of the 38th Int.
@@
 on Machine Learning (ICML), {\em online}, 18--24 Jul.
-2021, PMLR, 2021.
+2021, pp.
+9367--9376.
 	\bibitem[Bergstra(2012)]{Bergstra2012}
@@
 	Diez,~D.; \c{C}etinkaya-Rundel,~M.; Barr,~C.D. \textit{OpenIntro Statistics}, 4th ed.; 2019. \url{https://www.openintro.org/book/os/}
-
-	% Reference 1
-	\bibitem[Author1(year)]{ref-journal}
-	Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
-	% Reference 2
-	\bibitem[Author2(year)]{ref-book1}
-	Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor 1, F., Editor 2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
-	% Reference 3
-	\bibitem[Author3(year)]{ref-book2}
-	Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
-	% Reference 4
-	\bibitem[Author4(year)]{ref-unpublish}
-	Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
-	% Reference 5
-	\bibitem[Author5(year)]{ref-communication}
-	Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
-	% Reference 6
-	\bibitem[Author6(year)]{ref-proceeding}
-	Author 1, A.B.; Author 2, C.D.; Author 3, E.F.
-Title of presentation.
-In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
-	% Reference 7
-	\bibitem[Author7(year)]{ref-thesis}
-	Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
-	% Reference 8
-	\bibitem[Author8(year)]{ref-url}
-	Title of Site. Available online: URL (accessed on Day Month Year).
 \end{thebibliography}

### 2022-03-18 paper/MDPI_template/template.tex
Updated paper

@@
 %=================================================================
-\documentclass[sensors,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
+\documentclass[journal,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
 % For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept".
@@
 % Full title of the paper (Capitalized)
-\Title{A Deep Learning Approach for Gait Event Detection from a Single Shank-Worn IMU: Validation in Healthy and Neurological Cohorts}
+\Title{Title}
 
 % MDPI internal command: Title for citation in the left column
-\TitleCitation{A Deep Learning Approach for Gait Event Detection from a Single Shank-Worn IMU: Validation in Healthy and Neurological Cohorts}
+\TitleCitation{Title}
 
 % Author Orchid ID: enter ID or remove command
-\newcommand{\orcidauthorA}{0000-0002-2507-0924} % Add \orcidA{} behind the author's name
+\newcommand{\orcidauthorA}{0000-0000-0000-000X} % Add \orcidA{} behind the author's name
 %\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
@@
 % Authors, for the paper (add full first names)
-\Author{Robbin Romijnders$^{1}$\orcidA{}, Elke Warmerdam$^{2}$, Clint Hansen$^{1}$*, Gerhard Schmidt$^{3}$ and Walter Maetzler$^{1,}$}
+\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{2,\ddagger}$ and Firstname Lastname $^{2,}$*}
 
@@
 % MDPI internal command: Authors, for metadata in PDF
-\AuthorNames{Robbin Romijnders, Elke Warmerdam, Clint Hansen, Gerhard Schmidt and Walter Maetzler}
+\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}
 
 % MDPI internal command: Authors, for citation in the left column
-\AuthorCitation{Romijnders, R.; Warmerdam, E.; Hansen, C.; Schmidt, G.; Maetzler, W.}
+\AuthorCitation{Lastname, F.; Lastname, F.; Lastname, F.}
 % If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
@@
 \address{%
-$^{1}$ \quad Department of Neurology, Kiel University, 24105 Kiel, Germany; r.romijnders@neurologie.uni-kiel.de (R.R.), c.hansen@neurologie.uni-kiel.de (C.H.), w.maetzler@neurologie.uni-kiel.de (W.M.)\\
-$^{2}$ \quad xxxxx, xxxxx, xxxxx Homburg, Germany; elke.warmerdam@uni-saarland.de (E.W.)\\
-$^{3}$ \quad Institute of Electrical Engineering and Information Technology, Faculty of Engineering, Kiel University, 24143 Kiel, Germany; gus@tf.uni-kiel.de (G.S.)}
+$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
+$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}
 
 % Contact information of the corresponding author
-\corres{Correspondence: r.romijnders@neurologie.uni-kiel.de (R.R.)}
+\corres{Correspondence: e-mail@e-mail.com; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}
 
 % Current address and/or shared authorship
-%\firstnote{Current address: Affiliation 3.} 
-%\secondnote{These authors contributed equally to this work.}
+\firstnote{Current address: Affiliation 3.} 
+\secondnote{These authors contributed equally to this work.}
 % The commands \thirdnote{} till \eighthnote{} are available for further notes
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\setcounter{section}{-1} %% Remove this when starting to work on the template.
+\section{How to Use this Template}
+
+The template details the sections that can be used in a manuscript.
+Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section).
+Please check the instructions on the authors' page of the journal to verify the correct order and names.
+For any questions, please contact the editorial office of the journal or support@mdpi.com.
+For LaTeX-related questions please contact latex@mdpi.com.%\endnote{This is an endnote.} % To use endnotes, please un-comment \printendnotes below (before References).
+Only journal Laws uses \footnote.
+
+% The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision
+
 \section{Introduction}
-Gait deficits are common in older adults and possibly reflect the presence of an underlying neurodegenerative disease \cite{Snijders2007,Hodgins2008}.
-For example, conversion to Parkinson's Disease \cite{DelDin2019} or from mild cognitive impairment to Alzheimer's Disease \cite{Koenig2017,Bertoli2018} are linked with changes in spatiotemporal gait parameters.
-Similarly, temporal gait parameters are different for stroke patients \cite{SchroederVon1995,Mohan2021} and patients with multiple sclerosis \cite{Griskevicius2016,Flachenecker2019} when compared to healthy controls.
-To objectively quantify gait deficits, stride-specific parameters such as stride time or stride length are often used \cite{Hannink2016}, where the beginning and end of a stride are determined from two successive initial contacts (ICs) of the same foot \cite{Perry2010,Whittle2012}.
-The IC is when the foot contacts the ground and together with the instant at which the foot leaves the ground (final contact, FC), each stride can be divided in a stance and swing phase \cite{Rueterbories2010,Bruening2014}.
-The events of IC and FC, also referred to as \emph{gait events}, are commonly determined using force or pressure measuring devices \cite{Bruening2014}, or stereophotogrammetry systems based on reflective markers using a multi-camera setup \cite{Chiari2005}.
-These systems are relatively expensive, and restricted to usage in expertise laboratories \cite{Iosa2016,Jarchi2018}.
-As there is increasing evidence that gait measured in the lab does not reflect daily-life gait \cite{Hillel2019,Warmerdam2020,Atrsaei2021}, there is more and more interest in measurement systems that allow for continuous gait analysis in ambulatory settings.
-Therefore, the use of inertial measurement units (IMUs) is especially attractive, as these can be used to measure gait in ecologically valid environments, such as the home environment, thereby painting a more complete picture of health status \cite{DelDin2016,Shah2020} and providing clinical information that is complementary to standardized lab-based assessments \cite{Warmerdam2020,Fasano2020,Atrsaei2021,Corra2021}.
 
-Previous research suggests that gait event detection is more accurate using an IMU worn on a lower limb (e.g., shank or foot) compared to an IMU worn on the low back \cite{BenMansour2015,Storm2016,Panebianco2018}.
-Now, in order to get from abstract IMU sensor readings to clinically relevant gait parameters (e.g., from accelerations and angular velocities to stride times) \cite{Hannink2016}, different algorithmic approaches have been developed in the last twenty years of clinical gait research.
-A recent study has evaluated a cross-section of these algorithms for different sensor locations on the lower leg and foot \cite{Niswander2021}.
-The algorithms were categorized according to which signals were analyzed, for example the angular velocity about the medio-lateral axis, or the accelerations along vertical and antero-posterior axis.
-This means the sensor readings need to be linked with the anatomical axes, that is, one needs to know which sensor axis aligns with for example the medio-lateral axis.
-In most approaches, it is simply assumed that due to sensor attachment the sensor axis aligns roughly with the anatomical axis of interest (\cite{Salarian2004,Sabatini2005,Jasiewicz2006,Catalfamo2010,Trojaniello2014,Maqbool2016,Romijnders2021}) or an additional calibration procedure (e.g., \cite{Ferraris1995}) is required (\cite{Greene2010,Niswander2021}).
-In ambulatory assessments however, study participants often attach the sensor themselves, and therefore the sensor location and alignment cannot be controlled for.
-Furthermore, it is unlikely that each time the sensor is (re-)attached study participants, especially those with gait deficits, perform a calibration procedure that usually consists of holding a pre-defined pose and performing some known movement sequences (TODO: reference?!
-Kong?
-Seel?).
-
-Taken together, this drives the need for an approach that is invariant to sensor orientation, and is applicable across a variety of pathological gait patterns.
-As pointed out by \cite{Hannink2016}, in the field of image analysis similar requirements have been successfully addressed by algorithms that share a common underlying methodology referred to as deep learning \cite{LeCun2015,TerHaarRomeny2019}.
-Recent applications of deep learning algorithms have already shown improved performance in detecting gait events from marker-based motion capture when compared to conventional, often heuristics-based, algorithms \cite{Kidzinski2019,Lempereur2020,Filtjens2020}.
-Another study used a deep learning approach to detect gait events from either three IMUs (worn on the low back, and both ankles) or a single IMU (worn on the low back), and showed that the time error was considerably smaller for the deep learning algorithm than for a commonly applied wavelet-based approach \cite{Gadaleta2019}.
-
-In this study, we further these works by validating this deep learning approach for detecting gait events in a heterogeneous cohort of healthy and neurologically diseased adults considering a single IMU setup, worn on the lower leg.
+The introduction should briefly place the study in a broad context and highlight why it is important.
+It should define the purpose of the work and its significance.
+The current state of the research field should be reviewed carefully and key publications cited.
+Please highlight controversial and diverging hypotheses when necessary.
+Finally, briefly mention the main aim of the work and highlight the principal conclusions.
+As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
+Citing a journal paper \cite{ref-journal}.
+Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}.
+Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences, Literature.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\subsection{Data Collection}
-Gait analyses were performed in the Universit\"{a}tsklinikum Schleswig-Holstein (UKSH) campus Kiel, Germany.
-The study \cite{Warmerdam2021} was approved by the ethical committee of the medical faculty at the UKSH (no: D438/18).
-In total, data from 160 participants were included for the current analysis, including data from young adults (YA; age: 18 - 60 years), older adults (OA; age: $>$60 years), people with Parkinson's Disease (PD; according to the UK Brain Bank criteria \cite{Gibb1988}), people with a recent ($<$4 weeks) symptomatic stroke (stroke), people with multiple sclerosis (MS; according to the McDonalds criteria \cite{Thompson2018}), people with chronic low back pain (cLBP), and people with other diagnoses that were assumed not to affect mobility (Table \ref{tab:demographics_data}).
-Inclusion criteria were an age of 18 years or older, and the ability to walk independently without a walking aid.
-Participants were excluded from the study with a Montreal Cognitive Assessment \cite{Nasreddine2005} score $<$15 and other movement disorders that affected mobility, as noticed by the clinical assessor.
+Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
+Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers.
+Please disclose at the submission stage any restrictions on the availability of materials or information.
+New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
 
-\begin{table}[H] 
-	\caption{\label{tab:demographics_data}Demographics data of the study participants. Age, height, and weight are presented as mean (standard deviation).}
-	\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabularx}{\textwidth}{CCCCCC}
-		\toprule
-		\textbf{Group}	& \textbf{Gender}	& \textbf{Number of}	& \textbf{Age}	& \textbf{Height}	& \textbf{Weight}\\
-		 & & \textbf{subjects} & years	& cm	& kg\\
-		\midrule
-		YA		& F		& 21	& 27 (7)	& 173 (5)	& 67 (8)\\
-		 & M	& 22	& 30 (9)	& 185 (8) & 81 (13)\\ 
-		\midrule
-		OA		& F		& 11	& 70 (6)	& 167 (6)	& 72 (17)\\
-		 & M	& 11	& 73 (6)	& 180 (6) & 83 (11)\\
-		\midrule
-		PD		& F		& 12	& 67 (6)	& 168 (6)	& 70 (14)\\
-		 & M	& 20	& 62 (11)	& 178 (6) & 87 (13)\\
-		\midrule
-		MS		& F		& 12	& 37 (9)	& 174 (9)	& 75 (9)\\
-		 & M	& 9	& 42 (15)	& 189 (8) & 96 (30)\\
-		\midrule
-		stroke	& F		& 4	& 66 (10)	& 160 (6)	& 65 (11)\\
-		 & M	& 17	& 67 (17)	& 178 (7) & 84 (14)\\
-		\midrule
-		cLBP	& F		& 3	& 64 (10)	& 166 (5)	& 65 (5)\\
-		 & M	& 7	& 63 (16)	& 178 (7) & 90 (16)\\ 
-		\midrule
-		other	& F		& 3	& 60 (13)	& 166 (3)	& 79 (15)\\
-		 & M	& 8	& 68 (18)	& 182 (7) & 85 (13)\\ 
-		\bottomrule
-	\end{tabularx}
-	\noindent{\footnotesize{\textbf{Group}: YA: younger adults, OA: older adults, PD: Parkinson's Disease, MS: multiple sclerosis, cLBP: chronic low back pain; \textbf{Gender}: F: female, M: male.}}
-\end{table}
+Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers.
+If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
+They must be provided prior to publication.
 
-Participants performed three walking trials consisting of walking 5 meter at either (1) preferred speed ("\emph{Please walk at your normal walking speed.}"), (2) slow speed ("\emph{Please walk half of your normal walking speed.}"), or (3) fast speed ("\emph{Please walk as fast as possible, without running or falling.}").
-The 5 meter distance was marked with two cones on both ends, and participants were asked to start walking approximately two steps before the cones on one end, and stop walking approximately two steps after passing the cones on the other end.
-
-For the current analysis data from four IMUs (Noraxon USA Inc., myoMOTION, Scottsdale, AZ, USA) were considered, namely those that were attached laterally above the left and right ankle joint and those attached proximally at the left and right shank.
-IMUs were secured to participants using elastic bands with a special hold for the IMU.
-Furthermore, reflective markers were attached on top of the usual foot wear at the heel and toe of both feet.
-Marker data were recorded using a twelve-camera stereophotogrammetry system (Qualisys AB, G\"{o}teborg, Sweden) at a sampling frequency of 200 Hz.
-IMU data were recorded at the same sampling frequency, and both systems were synchronized using TTL signal \cite{Warmerdam2021}.
-For some recordings, the sampling frequency of the IMUs was erroneously set at 100 Hz, and therefore data from these trials were upsampled before further analysis.
-
-\subsection{Data Pre-processing \label{subsec:data_preprocessing}}
-\subsubsection{Reference Values}
-The raw reflective marker data were first used to determine the start and end of each trial.
-The start of the trial was defined as the time for which the first toe marker (left or right) crossed the \emph{virtual} starting line.
-The end was defined as the time for which the last heel marker crossed the end line.
-For both marker and IMU systems, data were then cropped from start to the end of the trial.
-
-Any remaining gaps in the marker data were filled by interpolation making use of inter-correlations between markers \cite{Federolf2013,Gloersen2016}.
-The data were then low-pass filtered using a double pass 6th order Butterworth filter with a cut-off frequency of 20 Hz \cite{Kormylo1974,Racz2021}.
-The filtered data were differentiated to get velocity signals, and timings of ICs and FCs were determined from local maxima and minima in the heel and toe vertical velocity signals \cite{Pijnappels2001,OConnor2007}.
-Like in \cite{Carcreff2018,Romijnders2021}, all identified ICs and FCs were manually checked using Qualisys Track Manager 2018.1 software (QTM; Qualisys AB, Göteborg, Sweden).
-
-\subsubsection{IMU Data}
-For the deep learning model, the data from randomly selected one-third of participants were used as a "training set", another one-third was used as a "validation set", and the rest was used as "test set", where randomization was stratified by both group and gender.
-Accelerometer and gyroscope data from the four IMUs were normalized by subtracting the channel-wise mean, and dividing by the channel-wise standard deviation.
-Then, for the training and validation set, the time series data were partitioned into equal length time windows of 400 samples, with an overlap of 50\% between successive windows.
-
-\subsection{Model}
-\subsubsection{Notation}
-Data from the IMUs' 3D accelerometer and 3D gyroscope were used. A signal was considered a sequence of real-valued numbers: $\mathbf{x} = \begin{array}{ccccc}
-	\cdots & x[n-1] & x[n] & x[n+1] & \cdots
-\end{array}$, with $n = 1, \cdots, N$ the discrete-time sample index.
-For any given channel, e.g., acceleration in $X$-direction, the signal was denoted in vector notation as: $\mathbf{x}_{d} = \begin{bmatrix}
-x_{d}[1] & x_{d}[2] & \cdots & x_{d}[N]
-\end{bmatrix}^{\mathrm{T}}$, where $d$ referred to the $d$-th channel.
-
-Data from all channels of a single IMU were collected in a $ N \times D$ data matrix, like:
-\begin{equation}
-	\mathbf{X} = \begin{bmatrix}
-		\vdots & \vdots &  & \vdots\\
-		\mathbf{x}_{1} & \mathbf{x}_{2} & \cdots & \mathbf{x}_{D}\\
-		\vdots & \vdots &  & \vdots
-	\end{bmatrix} = \begin{bmatrix}
-		x_{1}[1] & x_{2}[1] & & x_{D}[1]\\
-		x_{1}[2] & x_{2}[2] & & x_{D}[2]\\
-		\vdots & \vdots & \cdots & \vdots\\
-		x_{1}[N] & x_{2}[1] & & x_{D}[N]\end{bmatrix}, \quad \mathbf{X} \in \mathbb{R}^{N \times D}
-	\label{eqn:train_data_single_instance}
-\end{equation}
-
-The corresponding labels (or targets) were then denoted as:
-\begin{equation}
-	\mathbf{y}_{\mathrm{IC}} = \begin{bmatrix}
-		y_{1}[1]\\
-		y_{1}[2]\\
-		\vdots\\
-		y_{1}[N]
-	\end{bmatrix}, \quad \mathbf{y}_{\mathrm{FC}} = \begin{bmatrix}
-		y_{2}[1]\\
-		y_{2}[2]\\
-		\vdots\\
-		y_{2}[N]
-	\end{bmatrix}, \quad y_{i}[n] \in [0, 1]
-	\label{eqn:train_labels_single_instace}
-\end{equation}
-
-\subsubsection{Model Architecture}
-The basic architecture for the deep learning model was a temporal convolutional network (TCN) \cite{Bai2018,Remy2020,Filtjens2020}.
-The TCN consisted of repeating blocks of dilated convolutions (CONV) \cite{YuKoltun2016,Bai2018} that were followed by batch normalization (BN) \cite{Ioffe2015}, rectified linear unit (ReLU) activation, and dropout (DropOut) \cite{Srivastava2014}.
-For each given dilation factor, the sequence of layers CONV-BN-ReLU-DropOut was repeated twice \cite{Remy2020}.
-Dilation factors were given as a sequence of increasing powers of 2, e.g., $\left\{1, 2, 4, 8\right\}$ \cite{VanDenOord2016,YuKoltun2016,Bai2018}.
-These repeating blocks were followed by a fully-connected (dense) layer with sigmoid activation, and outputs were predicted separately for ICs and FCs.
-The mean squared error (MSE) was used as loss function, and a gradient descent-based optimization algorithm with adaptive moment (Adam) optimizer was used to iteratively learn the weights \cite{Kingma2014,Schmidt2021}.
-
-\subsubsection{Hyperparameter Optimization}
-In order to find the best model architecture, hyperparameter tuning was perfomed using KerasTuner \cite{OMalley2019}.
-Here, the number of filters, the kernel size, and the maximum dilation factor (Table \ref{tab:hyperparameter_optimization}) were optimized for using a random search strategy \cite{Bergstra2012}.
-
-\begin{table}[H] 
-	\caption{Model hyperparameters that were optimized for, and the corresponding sets of possible values.\label{tab:hyperparameter_optimization}}
-	\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabularx}{\textwidth}{CC}
-		\toprule
-		\textbf{Description}	& \textbf{Possible values}\\
-		\midrule
-		Number of filters	& 8, 16, 32, 64, 128\\
-		Kernel size			& 3, 5, 7\\
-		Dilations 			& [1, 2], [1, 2, 4], [1, 2, 4, 8]\\
-		\bottomrule
-	\end{tabularx}
-\end{table}
-
-The model architecture that resulted from the hyperparameter optimization was then trained on the combined set of training and validation data.
-The trained model was used to predict occurrence of gait events from the hold-out test set.
-
-\subsection{Analysis}
-The predictions of the model on the test set data were compared with the labels from the test set.
-The model performance was evaluated for (1) overall detection performance, (2) time agreement between the predicted events and the (marker-based) annotated events, (3) agreement between subsequently derived gait parameters.
-\subsubsection{Overall detection performance \label{subsubsec:overall_detection_performance}}
-The overall detection performance quantified how many of the annotated evens were detected by the model (true positives, TP), how many of the annotated events were not detected (false negatives, FN), and how many event that were detected, were actually not annotated (false positives, FP).
-From these metrics, the recall (or sensitivity), precision and F$_{1}$ score were calculated as:
-\begin{equation}
-	\textrm{recall} = \frac{\textrm{TP}}{\textrm{TP} + \textrm{FN}} \nonumber
-	\label{eqn:recall}
-\end{equation}
-\begin{equation}
-	\textrm{precision} = \frac{\textrm{TP}}{\textrm{TP} + \textrm{FP}} \nonumber
-	\label{eqn:precision}
-\end{equation}
-\begin{equation}
-	\textrm{F$_{1}$ score} = 2 \cdot \frac{\textrm{recall} \cdot \textrm{precision}}{\textrm{recall} + \textrm{precision}}  \nonumber
-	\label{eqn:f1_score}
-\end{equation}
-
-\subsubsection{Time agreement}
-For all correctly detected gait events (TP, Section \ref{subsubsec:overall_detection_performance}), the time error between the annotated and detect gait event was defined as:
-\begin{equation}
-	\textrm{time error} = t_{\textrm{ref}} - t_{\textrm{pred}}
-	\label{eqn:time_agreement}
-\end{equation}
-with $t_{\mathrm{ref}}$ the gait event time from the marker-based annotations, and $t_{\mathrm{pred}}$ the gait event time from the model predictions.
-As a robust measure for the average time error and its spread, the median time error and the inter-quartile range (IQR) were reported \cite{OpenIntro2019}.
-
-\subsubsection{Gait parameters}
-For those trials for which all gait events were detected, and no spurious events were detected, the following stride parameters were calculated:
-\begin{equation}
-	\textrm{stride time} = t_{\textrm{IC}_{k}} - t_{\textrm{IC}_{k-1}}
-	\label{eqn:stride_time}
-\end{equation}
-\begin{equation}
-	\textrm{stance time} = t_{\textrm{FC}_{k}} - t_{\textrm{IC}_{k-1}}
-	\label{eqn:stance_time}
-\end{equation}
-\begin{equation}
-	\textrm{swing time} = t_{\textrm{IC}_{k}} - t_{\textrm{FC}_{k}}
-	\label{eqn:swing_time}
-\end{equation}
+Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
+\begin{quote}
+This is an example of a quote.
+\end{quote}
 
@@
 \section{Results}
-
-\subsection{Overall detection performance}
-The performance of detecting initial contacts and final contacts was objectively quantified by the number of annotated events that were detected (true positives, TP), the number of annotated events that were not detected (false negatives, FN), and the number of detected events that were not annotated (false positives, FP).
-From these, recall, precision and F$_{1}$ score were calculated (Table \ref{tab:overall_detection_performance}).
-\begin{table}[H]
-	\caption{Overall detection performance for initial contacts and final contacts as quantified by recall, precision and F$_{1}$ score.\label{tab:overall_detection_performance}}
-	\begin{adjustwidth}{-\extralength}{0cm}
-		\newcolumntype{C}{>{\centering\arraybackslash}X}
-		\begin{tabularx}{\fulllength}{r|CCCCCC|CCCCCC}
-			\toprule
-			 & \multicolumn{6}{c}{\textbf{Initial contacts}}	& \multicolumn{6}{c}{\textbf{Final contacts}}\\
-			\textbf{Tracked point}	& \textbf{TP}	& \textbf{FN}	& \textbf{FP}	& \textbf{recall}	& \textbf{precision}	& \textbf{F1}	& \textbf{TP}	& \textbf{FN}	& \textbf{FP}	& \textbf{recall}	& \textbf{precision} 	& \textbf{F1}\\
-			\midrule
-			left ankle		& 624	& 19	& 5		& 97\%	& 99\%	& 98\%		& 606	& 32	& 10	& 95\%	& 98\%	& 97\%\\
-			right ankle		& 599	& 42	& 8 	& 93\%	& 99\%	& 96\%		& 614	& 17	& 12	& 97\%	& 98\%	& 98\%\\
-			left shank		& 605	& 38	& 15	& 94\%	& 98\%	& 96\%		& 585	& 53	& 18	& 92\%	& 97\%	& 94\%\\
-			right shank		& 603	& 36	& 15 	& 94\%	& 98\%	& 96\%		& 595	& 30	& 9		& 95\%	& 99\%	& 97\%\\
-			\bottomrule
-		\end{tabularx}
-	\end{adjustwidth}
-	\noindent{\footnotesize{TP: true positives, FN: false negatives, FP: false positives, F1: F$_{1}$ score.}}
-\end{table}
-
-For both ICs and FCs, recall is high for each of the tracked points (i.e, $\ge 92\%$), and so is precision (i.e, $\ge 97\%$).
-Differences between the tracked points are small, i.e.
-the minimum recall is $92\%$ and the maximum recall is $97\%$, and the minimum precision is $97\%$ and the maximum precision is $99\%$.
-
-\subsection{Time error}
-\begin{figure}[H]
-	\includegraphics[width=10.5 cm]{fig/box_plots_tracked_points_with_outliers.png}
-	\caption{Time errors for initial (left) and final (right) contacts detection, for each of the different tracked points.\label{fig:time_error_box_plots}}
-\end{figure}
-
-Time errors for ICs and FCs are visually depicted using boxplots for each tracked point.
-Data were not normally distributed, thus Wilcoxon signed-rank tests were used to evaluate whether the median time error was zero.
-\begin{table}[H] 
-	\caption{Time errors for the correctly detected gait events. \label{tab:time_errors}}
-	\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabularx}{\textwidth}{r|CCC|CCC}
-		\toprule
-		 & \multicolumn{3}{c}{\textbf{Initial contacts}} & \multicolumn{3}{c}{\textbf{Final contacts}}\\
-		\textbf{Tracked point} & \textbf{median} & \textbf{IQR} & (\textbf{Q25}, \textbf{Q75}) & \textbf{median} & \textbf{IQR} & (\textbf{Q25}, \textbf{Q75})\\
-		 & ms & ms &  (ms, ms) & ms & ms & (ms, ms)\\
-		\midrule
-		left ankle & 0 & 20 & (-10, 10) & 0 & 10 & (-5, 5)\\
-		right ankle & 0 & 20 & (-15, 5) & -5 & 15 & (-10, 5)\\
-		left shank & -5 & 20 & (-10, 10) & -5 & 20 & (-15, 5)\\
-		right shank & -2.5 & 20 & (-15, 5) & -5 & 20 & (-15, 5)\\
-		\bottomrule
-	\end{tabularx}
-	\noindent{\footnotesize{IQR: inter-quartile range, Q25: 25th percentile, Q75: 75th percentile.}}
-\end{table}
-
-\subsection{Gait parameters}
-\begin{figure}[H]
-	\begin{adjustwidth}{-\extralength}{0cm}
-		\centering
-		\includegraphics[width=13.5cm]{fig/bland_altman_plots_stride_params.png}
-	\end{adjustwidth}
-	\caption{The agreement of extracted gait parameters between the sensor-based and marker-based methods.\label{fig:gait_parameters_bland_altman_plots}}
-\end{figure}
 
@@
 \begin{tabular}{@{}ll}
-	cLBP & chronic low back pain\\
-	CNN & convolutional neural network\\
-	IMU & inertial measurement unit\\
-	MS & multiple sclerosis\\
-	OA & older adults\\
-	PD & Parkinson's Disease\\
-	TCN & temporal convolutional network\\
-	YA & younger adults
+MDPI & Multidisciplinary Digital Publishing Institute\\
+DOAJ & Directory of open access journals\\
+TLA & Three letter acronym\\
+LD & Linear dichroism
 \end{tabular}}
@@
 \begin{thebibliography}{999}
-	\bibitem[Snijders(2007)]{Snijders2007}
-	Snijders,~A.H.; {van de Warrenburg},~B.P.; Giladi,~N.; Bloem,~B.R.
-Neurological gait disorders in elderly people: clinical approach and classification.
-{\em Lancet Neurol.} {\bf 2007}, {\em 6}(1), 63--74.
-	\bibitem[Hodgins(2008)]{Hodgins2008}
-	Hodgins,~D. The importance of measuring human gait. {\em Med. Device Technol.} {\bf 2008}, {\em 19}(5):42, 44-7.
-	\bibitem[DelDin(2019)]{DelDin2019}
-	{Del Din},~S.; Elshehabi,~M.; Galna,~B.; Hobert,~M.A.; Warmerdam,~E.; Suenkel,~U.; Brockmann,~K.; Metzger,~F.; Hansen,~C.; Berg,~D.; Rochester,~L.; Maetzler,~W.
-Gait analysis with wearables predicts conversion to Parkinson disease.
-{\em Ann.
-Neurol.} {\bf 2019}, {\em 86}(3), 357--367.
-	\bibitem[Koenig(2017]{Koenig2017}
-	K\"{o}nig,~A.; Klaming,~L.; Pijl,~M.; Demeurraux,~A.; Davis,~R.; Robert,~P.
-Objective measurement of gait parameters in healthy and cognitively impaired elderly using the dual-task paradigm.
-{\em Aging.
-Clin.
-Exp.
-Res.} {\bf 2017}, {\em 29}(6), 1181--1189.
-	\bibitem[Bertoli(2018)]{Bertoli2018}
-	Bertoli,~M.; Cereatti,~A.; Trojaniello,~D.; Avanzino,~L.; Pelosin,~E.; Del Din,~S.; Rochester,~L.; Ginis,~P.; Bekkers,~E.M.J.; Mirelman,~A.; Hausdorff,~J.M.; {Della Croce},~U.
-Estimation of spatio-temporal parameters of gait from magneto-inertial measurement units: multicenter validation among Parkinson, mildly cognitively impaired and healthy older adults.
-{\em Biomed.
-Eng.
-Online} {\bf 2018}, {\em 17}(58).
-	\bibitem[SchroederVon(1995)]{SchroederVon1995}
-	von Schroeder,~H.P.; Coutts,~R.D.; Lyden,~P.D.; Billings,~E.,~Jr; Nickel,~V. L. Gait parameters following stroke: a practical assessment. {\em J. Rehabil. Res. Dev.} {\bf 1995}, {\em 32}(1), 25--31.
-	\bibitem[Mohan(2021)]{Mohan2021}
-	Mohan,~D.M.; Khandoker,~A.H.; Wasti,~S.A.; Ismail~Ibrahim~Ismail~Alali,~S.; Jelinek,~H.F.; Khalaf,~K.
-Assessment methods of post-stroke gait: A scoping review of technology-driven approaches to gait characterization and analysis.
-{\em Front.
-Neurol.} {\bf 2021}, {\em 12}.
-	\bibitem[Griskevicius(2016)]{Griskevicius2016}
-	Gri\v{s}kevi\v{c}ius,~J.; Apanskien\.{e},~V.; \v{Z}i\v{z}ien\.{e},~J.; Daunoravi\v{c}ien\.{e},~K.; Ov\v{c}inikova,~A.; Kizlaitien\.{e},~R.; Sereik\.{e},~I.; Kaubrys,~G.; Pauk,~J.; Id\'{z}kowski,~A.
-Estimation of temporal gait parameters of multiple sclerosis patients in clinical setting using inertial sensors.
-In Proceedings of the 11th Int Conf BIOMDLORE 2016, Druskininkai, Lithuania, 20--22 Oct 2016; 80--82.
-	\bibitem[Flachenecker(2019)]{Flachenecker2019}
-	Flachenecker,~F.; Ga{\ss}ner,~H.; Hannik,~J.; Lee,~D.H.; Flachenecker,~P.; Winkler,~J.; Eskofier,~B.; Linker,~R.A.; Klucken,~J.
-Objective sensor-based gait measures reflect motor impairment in multiple sclerosis patients: Reliability and clinical validation of a wearable sensor device.
-{\em Mult.
-Scler.
-Relat.
-Dis.} {\bf 2019}, {\em 39}, 101903.
-	\bibitem[Hannink(2016)]{Hannink2016}
-	Hannink,~J.; Kautz,~T.; Pasluosta,~C.F.; Ga{\ss}mann,~K.-G.; Klucken,~J.; Eskofier,~B.M.
-Sensor-Based Gait Parameter Extraction With Deep Convolutional Neural Networks.
-{\em IEEE J.
-Biomed.
-Health} {\bf 2017}, {\em 21}(1), 85--93.
-	\bibitem[Perry(2010)]{Perry2010}
-	Perry,~J; Burnfield,~J.M. \textit{Gait analysis: normal and pathological gait}, 2nd ed.; SLACK Inc.: Thorofare, NJ, USA, 2010.
-	\bibitem[Whittle(2012)]{Whittle2012}
-	Richards,~J.; Levine,~D.; Whittle,~M. \textit{Whittle's Gait Analysis}, 5th ed.; Churchill Livingstone: London, UK, 2012.
-	\bibitem[Rueterbories(2010)]{Rueterbories2010}
-	Rueterbories,~J.; Spaich,~E.G.; Larsen,~B.; Andersen,~O.K. Methods for gait event detection and analysis in ambulatory systems. {\em Med. Eng. Phys.} {\bf 2010}, {\em 32}(6), 545--552.
-	\bibitem[Bruening(2014)]{Bruening2014}
-	Bruening,~D.A.; Ridge,~S.T. Automated event detection algorithms in pathological gait. {\em Gait Posture} {\bf 2014}, {\em 39}(1), 472--477.
-	\bibitem[Chiari(2005)]{Chiari2005}
-	Chiari,~L.; Della~Croce,~U.; Leardini,~A.; Cappozzo,~A. Human movement analysis using stereophotogrammetry: Part 2: Instrumental errors {\em Gait Posture} {\bf 2005}, {\em 21}(2), 197--211.
-	\bibitem[Iosa(2016)]{Iosa2016}
-	Iosa,~M.; Picerno,~P.; Paolucci,~S.; Morone,~G. Wearable inertial sensors for human movement analysis. {\em Expert Rev. Med. Devic.} {\bf 2016}, {\em 13}(7), 641--659.
-	\bibitem[Jarchi(2018)]{Jarchi2018}
-	Jarchi,~D.; Pope,~J.; Lee,~T.K.M.; Tamjidi,~L.; Mirzaei,~A.; Sanei,~S.
-A Review on Accelerometry-Based Gait Analysis and Emerging Clinical Applications.
-{\em IEEE Rev.
-Biomed.
-Eng.} {\bf 2018}, {\em 11}, 177--194.
-	\bibitem[Hillel(2019)]{Hillel2019}
-	Hillel,~I; Gazit,~E.; Nieuwboer,~A.; Avanzino,~L.; Rochester,~L.; Cereatti,~A.; Della~Croce,~U.; Rikkert,~M.O.; Bloem,~B.R.; Pelosin,~E.; Del~Din,~S.; Ginis,~P.; Giladi,~N.;  Mirelman,~A.; Hausdorff,~J.M.
-Is every-day walking in older adults more analogous to dual-task walking or to usual walking?
-Elucidating the gaps between gait performance in the lab and during 24/7 monitoring.
-{\em Eur.
-Rev.
-Aging Phys.
-A.} {\bf 2019}, {\em 16}(6).
-	\bibitem[Warmerdam(2020)]{Warmerdam2020}
-	Warmerdam,~E.; Hausdorff,~J.M.; Atrsaei,~A.; Zhou,~Y.; Mirelman,~A.; Aminian,~K.; Espay,~A.J.; Hansen,~C.; Evers,~L.J.W.; Keller,~A.; Lamoth,~C.; Pilotto,~A.; Rochester,~L.; Schmidt,~G.; Bloem,~B.R.; Maetzler,~W.
-Long-term unsupervised mobility assessment in movement disorders.
-{\em Lancet Neurol.} {\bf 2020}, {\em 19}(5), 462--470.
-	\bibitem[Atrsaei(2021)]{Atrsaei2021}
-	Atrsaei,~A.; Corr\'{a},~M.F.; Dadashi,~F.; Vila-Ch\~{a},~N.; Maia,~L.; Mariani,~B.; Maetzler,~W.; Aminian,~K.
-Gait speed in clinical and daily living assessments in Parkinson’s disease patients: performance versus capacity.
-{\em npj Parkinsons Dis.} {\bf 2021}, {\em 7}(1):24.
-	\bibitem[DelDin(2016)]{DelDin2016}
-	Del~Din,~S.; Godfrey,~A.; Mazz\`{a},~C.; Lord,~S.; Rochester,~L. Free-living monitoring of Parkinson's disease: Lessons from the field. {\em Movement Disord.} {\bf 2016}, {\em 31}(9), 1293--1313.
-	\bibitem[Shah(2020)]{Shah2020}
-	Shah,~V.V.; McNames,~J.; Mancini,~M.; Carlson-Kuhta,~P.; Nutt,~J.G.; El-Gohary,~M.; Lapidus,~J.A.; Horak,~F.B.; Curtze,~C.
-Digital Biomarkers of Mobility in Parkinson's Disease During Daily Living.
-{\em J.
-Parkinson Dis.} {\bf 2020}, {\em 10}(3), 1099--1111.
-	\bibitem[Fasano(2020)]{Fasano2020}
-	Fasano,~A.; Mancini,~M. Wearable-based mobility monitoring: the long road ahead. {\em Lancet Neurol.} {\bf 2020}, {\em 19}(5), 378--379.
-	\bibitem[Corra(2021)]{Corra2021}
-	Corr\'{a},~M.F.; Atrsaei,~A.; Sardoreira,~A.; Hansen,~C.; Aminian,~K.; Correia,~M.; Vila-Ch\~{a},~N.; Maetzler,~W.; Maia,~L.
-Comparison of Laboratory and Daily-Life Gait Speed Assessment during ON and OFF States in Parkinson’s Disease.
-{\em Sensors} {\bf 2021}, {\em 21}(12):3974.
-	\bibitem[BenMansour(2015)]{BenMansour2015}
-	Ben~Mansour,~K.; Rezzoug,~N.; Gorce,~P.
-Analysis of several methods and inertial sensors locations to assess gait parameters in able-bodied subjects.
-{\em Gait Posture} {\bf 2015}, {\em 42}, 409--414.
-	\bibitem[Storm(2016)]{Storm2016}
-	Storm,~F.A.; Buckley,~C.J.; Mazz\`{a},~C. Gait event detection in laboratory and real life settings: Accuracy of ankle and waist sensor based methods. {\em Gait Posture} {\bf 2016}, {\em 50}, 42--46.
-	\bibitem[Panebianco(2018)]{Panebianco2018}
-	Panebianco,~G.P.; Bisi,~M.C.; Stagni,~R.; Fantozzi,~S.
-Analysis of the performance of 17 algorithms from a systematic review: Influence of sensor position, analysed variable and computational approach in gait timing estimation from IMU measurements.
-{\em Gait Posture} {\bf 2018}, {\em 66}, 76--82.
-	\bibitem[Niswander(2021)]{Niswander2021}
-	Niswander,~W.; Kontson,~K. Evaluating the Impact of IMU Sensor Location and Walking Task on Accuracy of Gait Event Detection Algorithms. {\em Sensors} {\bf 2021}, {\em 21}(12):3989.
-	\bibitem[Salarian(2004)]{Salarian2004}
-	Salarian,~A.; Russmann,~H.; Vingerhoets,~F.J.; Dehollain,~C.; Blanc,~Y.; Burkhard,~P.R.; Aminian,~K. Gait assessment in Parkinson's
-	disease: Toward an ambulatory system for long-term monitoring. {\em IEEE Trans. Biomed. Eng.} {\bf 2004}, {\em 51}(8), 1434--1443. 
-	\bibitem[Catalfamo(2010)]{Catalfamo2010}
-	Catalfamo,~P.; Ghoussayni,~S.; Ewins,~D. Gait Event Detection on Level Ground and Incline Walking Using a Rate Gyroscope. {\em Sensors} {\bf 2010}, {\em 10}(6), 5683--5702. 
-	\bibitem[Sabatini(2005)]{Sabatini2005}
-	Sabatini,~A.; Martelloni,~C.; Scapellato,~S.; Cavallo,~F. Assessment of Walking Features from Foot Inertial Sensing. {\em IEEE Trans. Biomed. Eng.} {\bf 2005}, {\em 52}(3), 486--494.
-	\bibitem[Maqbool(2016)]{Maqbool2016}
-	Maqbool,~H.F.; Husman,~M.A.B.; Awad,~M.; Abouhossein,~A.; Mehryar,~P.; Iqbal,~N.; Dehghani-Sanij,~A.A.
-Real-time gait event detection for lower limb amputees using a single wearable sensor.
-In Proceedings of the 2016 38th Ann.
-Int.
-Conf.
-of the IEEE Eng.
-in Med.
-Biol.
-Soc.
-(EMBC), Orlando, FL, USA, 16--20 Aug.
-2016, IEEE: Piscataway, NJ, USA, 2016.
-	\bibitem[Romijnders(2021)]{Romijnders2021}
-	Romijnders,~R.; Warmerdam,~E.; Hansen,~C.; Welzel,~J.; Schmidt,~G.; Maetzler,~W.
-Validation of IMU-based gait event detection during curved walking and turning in older adults and Parkinson's Disease patients.
-{\em J.
-Neuroeng.
-Rehabil.} {\bf 2021}, {\em 18}:28.
-	\bibitem[Jasiewicz(2006)]{Jasiewicz2006}
-	Jasiewicz,~J.M.; Allum,~J.H.; Middleton,~J.W.; Barriskill,~A.; Condie,~P.; Purcell,~B.; Li,~R.C.T.
-Gait event detection using linear accelerometers or angular velocity transducers in able-bodied and spinal-cord injured individuals.
-{\em Gait Posture} {\bf 2006}, {\em 24}(4), 502--509.
-	\bibitem[Trojaniello(2014)]{Trojaniello2014}
-	Trojaniello,~D.; Cereatti,~A.; Pelosin,~E.; Avanzino,~L.; Mirelman,~A.; Hausdorff,~J.M.; Della~Croce,~U.
-Estimation of step-by-step spatio-temporal parameters of normal and impaired gait using shank-mounted magneto-inertial sensors: Application to elderly, hemiparetic, parkinsonian and choreic gait.
-{\em J.
-Neuroeng.
-Rehabil.} {\bf 2014}, {\em 11}:152.
-	\bibitem[Ferraris(1995)]{Ferraris1995}
-	Ferraris,~F.; Grimaldi,~U.; Parvis,~M. Procedure for effortless in-field calibration of three-axis rate gyros and accelerometers. {\em Sensor. Mater.} {\bf 1995}, {\em 7}(5), 311--330.
-	\bibitem[Greene(2010)]{Greene2010}
-	Greene,~B.R.; McGrath,~D.; O'Neill,~R.; O'Donovan,~K.J.; Burns,~A.; Caulfield,~B.
-An adaptive gyroscope-based algorithm for temporal gait analysis.
-{\em Med.
-Biol.
-Eng.
-Comput.} {\bf 2010}, {\em 48}(12), 1251--1260.
-	\bibitem[LeCun(2015)]{LeCun2015}
-	LeCun,~Y.; Bengio,~Y.; Hinton,~G. Deep learning. {\em Nature} {\bf 2015}, {\em 521}, 436-444.
-	\bibitem[TerHaarRomeny(2019)]{TerHaarRomeny2019}
-	Ter Haar Romeny,~B.M.
-A Deeper Understanding of Deep Learning.
-In {\em Artificial Intelligence in Medical Imaging: Opportunities, Applications and Risks}; Ranschaert,~E.R., Morozov,~S., Algra,~P.R., Eds.; Springer Int.
-Publish.: Cham, Switzerland, 2019; pp.
-25--38.
-	\bibitem[Kidzinski(2019)]{Kidzinski2019}
-	Kidzi\'{n}ski,~{\L}.; Delp,~S.; Schwartz,~M. Automatic real-time gait event detection in children using deep neural networks. {\em PLoS ONE} {\bf 2019}, {\em 14}(1):e0211466.
-	\bibitem[Lempereur(2020)]{Lempereur2020}
-	Lempereur,~M.; Rousseau,~F.; R\'{e}my-N\'{e}ris,~O.; Pons,~C.; Houx,~L.; Quellec,~G.; Brochard,~S.
-A new deep learning-based method for the detection of gait events in children with gait disorders: Proof-of-concept and concurrent validity.
-{\em J.
-Biomech.} {\bf 2020}, {\em 98}, 109490.
-	\bibitem[Filtjens(2020)]{Filtjens2020}
-	Filtjens,~B.; Nieuwboer,~A.; D'cruz,~N.; Spildooren,~J.; Slaets,~P.; Vanrumste,~B.
-A data-driven approach for detecting gait events during turning in people with Parkinson's disease and freezing of gait.
-{\em Gait Posture} {\bf 2020}, {\em 80}, 130--136.
-	\bibitem[Gadaleta(2019)]{Gadaleta2019}
-	Gadaleta,~M.; Cisotto,~G.; Rossi,~M.; Ur~Rehman,~R.Z.; Rochester,~L.; Del~Din,~S.
-Deep Learning Techniques for Improving Digital Gait Segmentation.
-In Proceedings of the 2019 41st Ann.
-Int.
-Conf.
-of the IEEE Eng.
-in Med.
-Biol.
-Soc.
-(EMBC), Berlin, Germany, 23--27 Jul.
-2019, IEEE: Piscataway, NJ, USA, 2019.
-
-	% Materials and Methods
-	\bibitem[Warmerdam(2021)]{Warmerdam2021}
-	Warmerdam,~E.; Romijnders,~R.; Geritz,~J.; Elshehabi,~M.; Maetzler,~C.; Otto,~J.C.; Reimer,~M.; Stuerner,~K.; Baron,~R.; Paschen,~S.; Beyer,~T.; Dopcke,~D.; Eiken,~T.; Ortmann,~H.; Peters,~F.; von~der~Recke,~F.; Riesen,~M.; Rohwedder,~G.; Schaade,~A.; Schumacher,~M.; Sondermann,~A; Maetzler,~W.; Hansen,~C.
-Proposed Mobility Assessments with Simultaneous Full-Body Inertial Measurement Units and Optical Motion Capture in Healthy Adults and Neurological Patients for Future Validation Studies: Study Protocol.
-{\em Sensors} {\bf 2021}, {\em 21}(17):5833.
-	\bibitem[Gibb(1988)]{Gibb1988}
-	Gibb,~W.R.; Lees,~A.J. The relevance of the Lewy body to the pathogenesis of idiopathic Parkinson's disease. {\em J. Neurol. Neurosur. Ps.} {\bf 1988}, {\em 51}(6), 745--752.
-	\bibitem[Thompson(2018)]{Thompson2018}
-	Thompson,~A.J.; Banwell,~B.L.; Barkhof,~F.; Carroll,~W.M.; Coetzee,~T.; Comi,~G.; Correale,~J.; Fazekas,~F.; Filippi,~M.; Freedman,~M.S.; Fujihara,~K.; Galetta,~S.L.; Hartung,~H.P.; Kappos,~L.; Lublin,~F.D.; Marrie,~R.A.; Miller,~A.E.; Miller,~D.H.; Montalban,~X.; Mowry,~E.M.; Soelberg~Sorensen,~P.; Tintor\'{e},~M.; Traboulsee,~A.L.; Trojano,~M.; Uitdehaag,~B.M.J.; Vukusic,~S.; Waubant,~E.; Weinshenker,~B.G.; Reingold,~S.C.; Cohen,~J.A.
-Diagnosis of multiple sclerosis: 2017 revisions of the McDonald criteria.
-{\em Lancet Neurol.} {\bf 2018}, {\em 17}(2), 162--173.
-	\bibitem[Nasreddine(2005)]{Nasreddine2005}
-	Nasreddine,~Z.S.; Phillips,~N.A.; B\'{e}dirian,~V.; Charbonneau,~S.; Whitehead,~V.; Collin,~I.; Cummings,~J.L.; Chertkow,~H.
-The Montreal Cognitive Assessment, MoCA: A Brief Screening Tool For Mild Cognitive Impairment.
-{\em J.
-Am.
-Geriatr.
-Soc.} {\bf 2005}, {\em 53}(4), 695--699.
-	\bibitem[Federolf(2013)]{Federolf2013}
-	Federolf,~P.A.
-A Novel Approach to Solve the “Missing Marker Problem” in Marker-Based Motion Analysis That Exploits the Segment Coordination Patterns in Multi-Limb Motion Data.
-{\em PLoS ONE} {\bf 2013}, {\em 8}(10), 1--13.
-	\bibitem[Gloersen(2016)]{Gloersen2016}
-	Gl{\o}ersen,~{\O}; Federolf,~P. Predicting Missing Marker Trajectories in Human Motion Data Using Marker Intercorrelations. {\em PLoS ONE} {\bf 2016}, {\em 11}(3), 1--14.
-	\bibitem[Kormylo(1974)]{Kormylo1974}
-	Kormylo,~J.; Jain,~V. Two-pass recursive digital filter with zero phase shift. {\em IEEE T. Acoust. Speech} {\bf 1974}, {\em 22}(5), 384--387.
-	\bibitem[Racz(2021)]{Racz2021}
-	R\'{a}cz,~K.; Rita,~M.K. Marker displacement data filtering in gait analysis: A technical note. {\em Biomed. Signal Proces.} {\bf 2021}, {\em 70}:102974.
-	\bibitem[Pijnappels(2001)]{Pijnappels2001}
-	Pijnappels,~M.; Bobbert,~M.F.; Van Die\"{e}n,~J.H. Changes in walking pattern caused by the possibility of a tripping reaction. {\em Gait Posture} {\bf 2001}, {\em 14}(1), 11--18.
-	\bibitem[OConnor(2007)]{OConnor2007}
-	O'Connor,~C.M.; Thorpe,~S.K.; O'Malley,~M.J.; Vaughan,~C.L. Automatic detection of gait events using kinematic data. {\em Gait Posture} {\bf 2007}, {\em 25}(3), 469--474.
-	\bibitem[Carcreff(2018)]{Carcreff2018}
-	Carcreff,~L.; Gerber,~C.; Paraschiv-Ionescu,~A.; De~Coulon,~G,; Newman,~C.; Armand,~S.; Aminian,~K. What is the best configuration of wearable sensors
-	to measure spatiotemporal gait parameters in children with cerebral palsy? {\em Sensors} {\bf 2018}, {\em 18}(2):394.
-	\bibitem[YuKoltun(2016)]{YuKoltun2016}
-	Yu,~F.; Koltun,~V.
-Multi-Scale Context Aggregation by Dilated Convolutions.
-In Proceedings of the 4th Int.
-Conf.
-on Learning Representations (ICLR), San Juan, Puerto Rico, 2--4 May 2016, Conference Track Proceedings, 2016.
-	\bibitem[Bai(2018)]{Bai2018}
-	Bai,~S.; Kolter,~J.Z.; Koltun,~V. An Empirical Evaluation of Generic Convolutional and Recurrent Networks for Sequence Modeling. {\em arXiv:1803.01271} {\bf 2018}.
-	\bibitem[Remy(2020)]{Remy2020}
-	R\'{e}my,~P. Temporal Convolutional Networks for Keras. {\em GitHub repository} {\bf 2020}, {\em GitHub}, \url{https://github.com/philipperemy/keras-tcn}.
-	\bibitem[LeCun(1989)]{LeCun1989}
-	LeCun,~Y.; Boser,~B.; Denker,~J.S.; Henderson,~D.; Howard,~R.E.; Hubbard,~W.; Jackel,~L.D.
-Backpropagation Applied to Handwritten Zip Code Recognition.
-{\em Neural Comput.} {\bf 1989}, {\em 1}(4), 541--551.
-	\bibitem[Ioffe(2015)]{Ioffe2015}
-	Ioffe,~S.; Szegedy,~C. Batch Normalization: Accelerating Deep Network Training by
-	Reducing Internal Covariate Shift. {\em arXiv:1502.03167} {\bf 2015}.
-	\bibitem[Srivastava(2014)]{Srivastava2014}
-	Srivastava,~N.; Hinton,~G.; Krizhevsky,~A.; Sutskever,~I.; Salakhutdinov,~R. Dropout: a
-	simple way to prevent neural networks from overfitting. {\em J. Mach. Learn. Res.} {\bf 2014} {\em 15}, 1929--1958.
-	\bibitem[VanDenOord(2016)]{VanDenOord2016}
-	van~den~Oord,~A.; Dieleman,~S.; Zen,~H.; Simonyan,~K.; Vinyals,~O.; Graves,~A.; Kalchbrenner,~N.; Senior,~A.W.; Kavukcuoglu,~K.
-WaveNet: A generative	model for raw audio.
-{\em arXiv:1609.03499} {\bf 2016}.
-	\bibitem[OMalley(2019)]{OMalley2019}
-	O'Malley,~T.; Bursztein,~E.; Long,~J.; Chollet,~F.; Jin,~H.; Invernizzi,~L.; and others; KerasTuner. {\em GitHub repository} {\bf 2019}, {\em GitHub}, \url{https://github.com/keras-team/keras-tuner}.
-	\bibitem[Kingma(2014)]{Kingma2014}
-	Kingma,~D.P.; Ba,~J. Adam: A Method for Stochastic Optimization {\em arXiv:1412.6980v9} {\bf 2014}.
-	\bibitem[Schmidt(2021)]{Schmidt2021}
-	Schmidt,~R.M.; Schneider,~F.; Henning,~P.
-Multi-Scale Context Aggregation by Dilated Convolutions.
-In Proceedings of the 38th Int.
-Conf.
-on Machine Learning (ICML), {\em online}, 18--24 Jul.
-2021, PMLR, 2021.
-	\bibitem[Bergstra(2012)]{Bergstra2012}
-	Bergstra,~J.; Bengio,~Y. Random Search for Hyper-Parameter Optimization. {\em J. Mach. Learn. Res.} {\bf 2012}, {\em 13}(10), 281--305.
-	\bibitem[Mishra(2019)]{Mishra2019}
-	Mishra,~P.; Pandey,~C.M.; Singh,~U.; Gupta,~A.; Sahu,~C.; Keshri,~A. Descriptive Statistics and Normality Tests for Statistical Data. {\em Ann. Card. Anaesth.} {\bf 2019}, {\em 22}(1), 67--72. 	
-	\bibitem[Wilcoxon(1945)]{Wilcoxon1945}
-	Wilcoxon,~F. Individual Comparisons by Ranking Methods. {\em Biometrics Bull.} {\bf 1945}, {\em 1}, 80--83.
-	\bibitem[McDonald(2014)]{McDonald2014}
-	McDonald,~J.H. \textit{Handbook of Biological Statistics}, 3rd ed.; Sparky House Publishing: Sparky House Publishing, USA, 2014; pp. 186--189.
-	\bibitem[OpenIntro(2019)]{OpenIntro2019}
-	Diez,~D.; \c{C}etinkaya-Rundel,~M.; Barr,~C.D. \textit{OpenIntro Statistics}, 4th ed.; 2019. \url{https://www.openintro.org/book/os/}
-
 % Reference 1

### 2022-03-18 paper/MDPI_template/article.tex
Extended discussion. Add figure to explain TCN arch

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+\section{Introduction \label{sec:Introduction}}
 Gait deficits are common in older adults and possibly reflect the presence of an underlying neurodegenerative disease \cite{Snijders2007,Hodgins2008}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Materials and Methods}
-\subsection{Data Collection}
+\section{Materials and Methods \label{sec:Materials_and_Methods}}
+\subsection{Data Collection \label{subsec:Data_Collection}}
 Gait analyses were performed in the Universit\"{a}tsklinikum Schleswig-Holstein (UKSH) campus Kiel, Germany.
@@
 IMU data were recorded at the same sampling frequency, and both systems were synchronized using a TTL signal \cite{Warmerdam2021}.
-For some recordings, the sampling frequency of the IMUs was erroneously set at 100 Hz, and therefore data from these trials were upsampled before further analysis.
+For some recordings, the sampling frequency of the IMUs was mistakenly set at 100 Hz, and therefore data from these trials were upsampled before further analysis.
 
-\subsection{Data Pre-processing \label{subsec:data_preprocessing}}
-\subsubsection{Marker Data}
+\subsection{Data Pre-processing \label{subsec:Data_Pre-processing}}
+\subsubsection{Marker Data \label{subsubsec:Marker_Data}}
 The reflective marker data were first used to determine start and end of each trial.
@@
 
-\subsubsection{IMU Data}
+\subsubsection{IMU Data \label{subsubsec:IMU_Data}}
 The idea behind the deep learning approach was that a \emph{model} was trained to predict the likelihood of an IC and FC, given accelerometer and gyroscope data from a single IMU.
-In other words, the model was iteratively trained to learn a mapping $h_{\mathbf{W}}(\mathbf{X}): \mathbf{X} \rightarrow \mathbf{y}$, where $h_{\mathbf{W}}$ was also referred to as the \emph{hypothesis} parameterized by the weights, collectively denoted by $\mathbf{W}$, $\mathbf{X}$ was the matrix of IMU data, and $\mathbf{y}$ was the vector of annotated events.
-
-Here, the matrix $\mathbf{X}$ consisted of the IMU data, arranged as:
+The data from a single sensor channel, e.g., the acceleration in forward direction, or the angular velocity about the vertical direction, was denoted by $\mathbf{x}_{d} = \begin{bmatrix}
+x_{d}[1] & x_{d}[2] & \cdots & x_{d}[N]
+\end{bmatrix}^{\mathrm{T}}$, with $d$ referring to the $d$th sensor channel (i.e., $d = 1, \cdots, D$) and $n$ referring to the $n$th sample or time step (i.e., $n = 1, \cdots, N$).
+Data from all $D$ sensor channels together was then denoted by:
 \begin{equation}
@@
 \end{equation}
-where $\mathbf{x}_{d} = \begin{bmatrix}x_{d}[1] & x_{d}[2] & \cdots & x_{d}[n] & \cdots & x_{d}[N]\end{bmatrix}^{\mathrm{T}}$, with $d = 1, \cdots, D$ referred to the $d$-th channel, and $n = 1, \cdots, N$ referred to the $n$-th sample (or discrete time step).
 
-Accordingly, the vector $\mathbf{y}$ consisted of the annotated events, arranged as:
+Likewise, the \emph{labels} were denoted by:
 \begin{equation}
 	\mathbf{y}_{\mathrm{IC}} = \begin{bmatrix}
-		y_{1}[1]\\
-		y_{1}[2]\\
+		y_{\mathrm{IC}}[1]\\
+		y_{\mathrm{IC}}[2]\\
 		\vdots\\
-		y_{1}[N]
+		y_{\mathrm{IC}}[N]
 		\end{bmatrix}, \quad \mathbf{y}_{\mathrm{FC}} = \begin{bmatrix}
-		y_{2}[1]\\
-		y_{2}[2]\\
+		y_{\mathrm{FC}}[1]\\
+		y_{\mathrm{FC}}[2]\\
 		\vdots\\
-		y_{2}[N]
-	\end{bmatrix}, \quad y_{i}[n] \in [0, 1]
-	\label{eqn:train_labels_single_instace}
+		y_{\mathrm{FC}}[N]
+		\end{bmatrix}, \quad y_{\mathrm{IC}/\mathrm{FC}}[n] \in [0, 1]
+	\label{eqn:train_labels_single_instance}
 \end{equation}
 
-The data were split in three independent data sets, namely a training set, a validation set, and a test set.
+The model was then iteratively trained to learn a mapping $h_{\mathbf{\Theta}}(\mathbf{X}): \mathbf{X} \rightarrow \mathbf{y}$, where $h_{\mathbf{\Theta}}$ was also referred to as the \emph{hypothesis} which was parameterized by the weights and biases, collectively denoted by $\mathbf{\Theta}$.
+
+All participant data were split in three independent data sets, namely a training set, a validation set, and a test set.
 Each set contained data from approximately one-third of the participants.
@@
 
-\subsection{Model}
-\subsubsection{Model Architecture}
-The basic architecture for the deep learning model was a temporal convolutional network (TCN) \cite{Bai2018,Remy2020,Filtjens2020}.
-The TCN consisted of repeating blocks of dilated convolutions (CONV) \cite{YuKoltun2016,Bai2018} that were followed by batch normalization (BN) \cite{Ioffe2015}, rectified linear unit (ReLU) activation, and dropout (DropOut) \cite{Srivastava2014}.
-For each given dilation factor, the sequence of layers CONV-BN-ReLU-DropOut was repeated twice \cite{Remy2020}.
-Dilation factors were given as a sequence of increasing powers of 2, e.g., $\left\{1, 2, 4, 8\right\}$ \cite{VanDenOord2016,YuKoltun2016,Bai2018}.
-These repeating blocks were followed by a fully-connected (dense) layer with sigmoid activation, and outputs were predicted separately for ICs and FCs.
+\subsection{Model \label{subsec:Model}}
+\subsubsection{Model Architecture \label{subsubsec:Model_Architecture}}
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=13.5cm]{fig/methods_tcn_arch.pdf}
+	\caption{The generic model architecture of the deep learning model to predict initial contacts (ICs) and final contacts (FCs).
+The inputs are the accelerometer and gyroscope data from a single inertial measurement unit, and are fed to a temporal convolutional network (TCN) (left).
+The TCN consisted of repeating residual blocks (ResBlock) with exponentially increasing dilation factor (middle).
+Each ResBlock was built from two sequences of a convolutional layer (Conv), batch normalization layer (BatchNorm), a rectified linear unit activation layer (ReLU), and a dropout layer (DropOut) (right).
+\label{fig:methods_tcn_arch}}
+\end{figure} 
+The generic architecture for the deep learning model was based on a temporal convolutional network (TCN) \cite{Bai2018,Remy2020,Filtjens2020}.
+The TCN consisted of a sequence of residual blocks with exponentially increasing dilation factor \cite{YuKoltun2016,Bai2018}.
+Each residual block was built from two sequences of a dilated convolutional layer \cite{YuKoltun2016}, a batch normalization layer \cite{Ioffe2015}, a rectified linear unit (ReLU) activation layer, and dropout layer \cite{Srivastava2014} (Figure~\ref{fig:methods_tcn_arch}).
+The model was built in Python \cite{VanRossum2009} using the high-level TensorFlow API Keras \cite{Chollet2015,Remy2020}.
+
+For the current analysis only convolutions of the "same" type were considered \cite{Remy2020}, i.e., the model was non-causal and zero-padded to account for edge effects, and the likelihood of an IC or FC was based on input data both before and after the current sample, $n$:
+\begin{equation}
+	\hat{y}_{i}[n] = f(\cdots,\mathbf{X}[n-1],\mathbf{X}[n],\mathbf{X}[n+1],\cdots), \quad i \in \left\{ \mathrm{IC}, \mathrm{FC}\right\}
+	\label{eqn:predictions}
+\end{equation}
+The number of samples that the predictions at time $n$ "sees", was referred to as the \emph{receptive field} \cite{Lea2017} and was a function of the kernel size and the dilation factors \cite{Remy2020}.
+Dilation factors were always given as a sequence of increasing powers of 2 \cite{VanDenOord2016,YuKoltun2016,Bai2018}.
+
+The outputs of the TCN block were fed to two separate fully-connected (FCN, or dense) layers, that both were followed by a sigmoid activation layer.
+Outputs were then predicted separately for ICs and FCs.
 The mean squared error (MSE) was used as loss function, and a gradient descent-based optimization algorithm with adaptive moment (Adam) optimizer was used to iteratively learn the weights \cite{Kingma2014,Schmidt2021}.
@@
 In order to find the best model architecture, hyperparameter tuning was perfomed using KerasTuner \cite{OMalley2019}.
-Here, the number of filters, the kernel size, and the maximum dilation factor (Table \ref{tab:hyperparameter_optimization}) were optimized for using a random search strategy \cite{Bergstra2012}.
+Here, the number of filters, the kernel size, and the maximum dilation factor (Table \ref{tab:hyperparameter_optimization}) were optimized using a random search strategy \cite{Bergstra2012}.
 
@@
 The model architecture that resulted from the hyperparameter optimization was then trained on the combined set of training and validation data.
-The trained model was used to predict occurrence of gait events from the hold-out test set.
+The trained model was used to predict the likelihoods of ICs and FCs events on the hold-out test set.
 
@@
 The overall detection performance quantified how many of the annotated evens were detected by the model (true positives, TP), how many of the annotated events were not detected (false negatives, FN), and how many event that were detected, were actually not annotated (false positives, FP).
+An annotated event was considered to be detected if any detected event was within 0.075 s.
+A detected event were defined as peaks in the predicted likelihoods with a minimum height of 0.4, i.e.
+$40\%$ likely that it corresponded to an event.
+
 From these metrics, the recall (or sensitivity), precision and F$_{1}$ score were calculated as:
@@
 
-\subsubsection{Time Error}
-For all correctly detected gait events (TP, Section \ref{subsubsec:overall_detection_performance}), the time error between the annotated and detect gait event was defined as:
+\subsubsection{Time Agreement \label{subsubsec:Methods_Time_Agreement}}
+For all correctly detected gait events (TP, Section \ref{subsubsec:overall_detection_performance}), the time agreement between the annotated and detect gait event was given by the time error:
 \begin{equation}
@@
 \subsubsection{Stride Parameters}
-For those trials for which all gait events were detected, and no spurious events were detected, the stride time, stance time and swing were calculated.
-Stride was the time between two successive ICs of the same foot.
-Stance time was the time between FC and the preceding IC of the same foot.
+For those trials for which all gait events were detected, and no false positives were detected, the stride time, stance time and swing were calculated.
+Stride time was the time between two successive ICs of the same foot.
+Stance time was the time between a FC and the preceding IC of the same foot.
 Swing time was the time between the IC following the last FC of the same foot.
@@
 
-\subsection{Overall detection performance}
-The performance of detecting initial contacts and final contacts was objectively quantified by the number of annotated events that were detected (true positives, TP), the number of annotated events that were not detected (false negatives, FN), and the number of detected events that were not annotated (false positives, FP).
+\subsection{Overall Detection Performance}
+The performance of detecting ICs and FCs was objectively quantified by the number of TPs, the number of FNs, and the number of FPs.
 From these, recall, precision and F$_{1}$ score were calculated (Table \ref{tab:overall_detection_performance}).
@@
 
-\subsection{Time Error}
+\subsection{Time Agreement}
 \begin{figure}[H]
@@
 
-Time errors for ICs and FCs are visually depicted using boxplots for each tracked point.
-Data were not normally distributed, thus Wilcoxon signed-rank tests were used to evaluate whether the median time error was zero.
+Time agreement between the annotated and detected events was quantified for the TPs for each of the tracked points (Figure~\ref{fig:time_error_box_plots}).
+The median time error for each of the tracked points, and for both ICs and FCs was close to zero (Table~\ref{tab:time_errors}), and the largest deviation was -0.005 s, corresponding to one sample period.
+The IQR was at most 0.020 s, corresponding to 4 sample periods.
 \begin{table}[H] 
@@
 
-\subsection{Gait parameters}
-For those trials for which all gait events were correctly detected (and no spurious events were detected, i.e., no false positives), stride time, stance time and swing time were calculated.
-The mean difference and the limits of agreement between the NN-derived gait parameters and the marker-based annotations were calculated.
+\subsection{Stride Parameters}
+For those trials for which all gait events were correctly detected (and no false positives were detected), stride time, stance time and swing time were calculated.
+The mean difference and the limits of agreement between the marker-based annotations and the model-based detections were calculated.
 
-For all stride-specific gait parameters, and for all tracked points, the mean difference compared to the marker-based reference values was close to zero, i.e., the maxmum mean difference was 0.003 s.
-Furthermore, for all gait parameters and for all tracked points the limits of agreement, based on a 95\% confidence interval were distributed around zero with the overall span between -0.049 s and 0.051 s.
+For all stride-specific gait parameters, and for all tracked points, the mean difference was close to zero, i.e., the maximum mean difference was 0.003 s, namely for the calculated swing time of the right ankle (Table~\ref{tab:stride_parameters}).
+Furthermore, for all gait parameters and for all tracked points the limits of agreement, based on a 95\% confidence interval were distributed around a zero mean difference with the overall limits of agreement at -0.049 s and 0.051 s (Figure~\ref{fig:gait_parameters_bland_altman_plots}).
 \begin{table}[H] 
@@
 The current study aimed to validate a deep learning approach for detecting gait events from a single IMU worn on the lower leg.
-Data from left and right ankle- and shank-worn IMUs were used for training a neural network to detect gait events from walking trials performed by healthy younger and older adults, participants diagnosed with Parkinson's Disease, multiple sclerosis, or chronic low back pain, participants who had a recent symptomatic stroke, and participants diagnosed with other neurological diseases.
+Data from a left and right ankle- and shank-worn IMU were used for training a deep learning model to detect gait events from walking trials performed by healthy younger and older adults, participants diagnosed with Parkinson's Disease, multiple sclerosis, or chronic low back pain, participants who had a recent symptomatic stroke, and participants diagnosed with other neurological diseases.
 Participants walked a 5 meter distance at three different self-selected walking speeds.
-The gait event timings that were predicted by the neural network were compared to a common reference method, i.e., stereophotogrammetry, and clinically relevant stride-specific gait parameters were extracted.
+The gait event timings that were predicted by the deep learning model were compared to a common reference method, i.e., optoelectronc motion capture, and clinically relevant stride-specific gait parameters were extracted.
 
-A first measure for the model performance was given by the recall (how many annotated events were detected) and precision (how many detected events were annotated).
-For both initial contacts and final contacts, a high recall ($\ge 95\%$) and high precision ($\ge 98\%$) were observed, meaning that most events can be detected and most detected events were actually true events.
-There was little difference in recall and precision between tracked points (Table~\ref{tab:overall_detection_performance}) confirming that the deep learning approach is relatively invariant to exact sensor localization.
-These values for recall and precision were slightly lower than our previously reported $100 \%$ \cite{Romijnders2021} that used a heuristics-based approach \cite{Salarian2004}, but in the current study more trials were included and from a more heterogeneous study population.
+A first measure for the model performance was given by the recall, precision and F$_{1}$ score.
+For both ICs and FCs, a high recall ($\ge 95\%$) and high precision ($\ge 98\%$) were observed, meaning that most events can be detected and most detected events were actually true events.
+There was little difference in recall and precision between tracked points (Table~\ref{tab:overall_detection_performance}) confirming that the deep learning approach is relatively invariant to exact sensor location.
+These values for recall and precision were slightly lower than our previously reported values \cite{Romijnders2021} that used a heuristics-based approach \cite{Salarian2004}, but in the current study more trials were included and from a more heterogeneous study population.
+The F$_{1}$ score was comparable to the F$_{1}$ score obtained by \cite{Filtjens2020} who compared marker-based gait event detection to manual annotations, and was also comparable to the F$_{1}$ score reported by \cite{Ji2019} for gait event detection from a continuous wavelet-based approach.
 
-Next, the time error, that is the difference between the annotated event and the detected event, was of interest.
-For both initial contacts and final contacts, and for all tracked points, the observed time error was small, and the middle $50\%$ of the time errors were within a range of $\left[-0.015,0.010\right]$ s (Table~\ref{tab:time_errors}, Figure~\ref{fig:time_error_box_plots}).
-These data showed that the deep learning-based is approach is precise in detecting initial and final contacts.
+Next, the time agreement, expressed by the time error the annotated event and the detected event, was of interest.
+For both ICs and FCs, and for all tracked points, the observed time error was small, and the middle $50\%$ of the time errors were within a range of $\left[-0.015,0.010\right]$ s (Table~\ref{tab:time_errors}, Figure~\ref{fig:time_error_box_plots}).
+These data showed that the deep learning-based is approach is precise in detecting ICs and FCs.
 Time errors were slightly smaller than our previously reported results \cite{Romijnders2021} that used a heuristics-based approach \cite{Salarian2004}.
-The heuristics-based approach determined ICs and FCs as local minima in the medio-lateral angular velocity \cite{Salarian2004} and it could be that these minima do not exactly coincide with the referent event timing as determined from the stereophotogrammetry.
+The heuristics-based approach determined ICs and FCs as local minima in the medio-lateral angular velocity \cite{Salarian2004} and it could be that these minima do not exactly coincide with the referent event timing as determined from the optoelectronic motion capture systems.
+The median and IQR of the time errors were in the same range as previously found by \cite{Gadaleta2019} that used a similar model architecture.
+The time errors were lower than previously reported time errors from a continuous wavelet-based approach \cite{Ji2019}.
 
@@
 The limits of agreement for a $95\%$ confidence interval were calculated, and for all metrics the zero mean difference was enclosed in the limit of agreement.
+These data provided evidence that the deep learning-based model was able to derive stride-specific gait parameters.
+The differences between the deep learning model-based stride parameters and the marker-based stride parameters were in a similar range as a recent study that compared IMU-derived stride parameters against stride parameters obtained with a pressure sensing walkway \cite{Gadaleta2019,Niswander2021}, and were also in the same range as a study that compared IMU-derived stride parameters with stride parameters obtained with an optoelectronic motion capture systems \cite{Carcreff2018}.
+
+The main limitations of the current study were that only walking trials involving straight-line walking were considered, and the walking distance was relatively short.
+The observed gait patterns from these walking trials may therefore not fully representative of gait patterns observed in daily-life \cite{Hillel2019,Warmerdam2020,Atrsaei2021}.
+However, as the deep learning-based approach does not rely on fixed thresholds or assumptions regarding to which sensor axis is used, it is theoretically transferable and scalable to other conditions if input data and corresponding labels can be provided.
+For example, in \cite{Gadaleta2019} a similar deep learning model was tested for a setup with three IMUs and for a setup with a single IMU, and observed differences in time errors compared to a pressure sensing walkway were negligible.
 
@@
 \section{Conclusions}
-In this study we have validated a deep learning-based approach to detect gait events and subsequently extract clinically relevant stride parameters from a single inertial measurement unit.
+In this study we have validated a deep learning-based approach to detect gait events and subsequently extract clinically relevant stride parameters from a single inertial measurement unit worn either laterally above the ankle joint or proximally below the knee joint.
 Performance analysis showed an excellent detection rate, and low time errors in both event detection and stride parameter calculation for different walking speeds and across both healthy and neurological cohorts.
-Our next step is to validate these methods under more challenging conditions, that involve real-life walking sequences.
+Our next step is to validate these methods with real-life walking sequences.
 
@@
 	simple way to prevent neural networks from overfitting. {\em J. Mach. Learn. Res.} {\bf 2014} {\em 15}, 1929--1958.
+	\bibitem[VanRossum(2009)]{VanRossum2009}
+	Van~Rossum,~G.; Drake,~F.L. \textit{Python 3 Reference Manual}; CreateSpace, Scotts Valley, CA, USA, 2009.
+	\bibitem[Chollet(2015)]{Chollet2015}
+	Chollet,~F. and others. Keras. {\bf 2015}. \url{https://keras.io}.
+	\bibitem[Lea(2017)]{Lea2017}
+	Lea,~C.; Flynn,~M.D.; Vidal,~R.; Reiter,~A.; Hager,~G.D.
+Temporal convolutional networks for action segmentation and detection.
+In Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition, Honolulu, HI, USA, 22--25 Jul.
+2017; pp.
+156--165.
 	\bibitem[VanDenOord(2016)]{VanDenOord2016}
@@
 {\em arXiv:1609.03499} {\bf 2016}.
-	\bibitem[OMalley(2019)]{OMalley2019}
-	O'Malley,~T.; Bursztein,~E.; Long,~J.; Chollet,~F.; Jin,~H.; Invernizzi,~L.; and others; KerasTuner. {\em GitHub repository} {\bf 2019}, {\em GitHub}, \url{https://github.com/keras-team/keras-tuner}.
 	\bibitem[Kingma(2014)]{Kingma2014}
@@
 9367--9376.
+	\bibitem[OMalley(2019)]{OMalley2019}
+	O'Malley,~T.; Bursztein,~E.; Long,~J.; Chollet,~F.; Jin,~H.; Invernizzi,~L.; and others; KerasTuner. {\em GitHub repository} {\bf 2019}, {\em GitHub}, \url{https://github.com/keras-team/keras-tuner}.
 	\bibitem[Bergstra(2012)]{Bergstra2012}
 	Bergstra,~J.; Bengio,~Y. Random Search for Hyper-Parameter Optimization. {\em J. Mach. Learn. Res.} {\bf 2012}, {\em 13}(10), 281--305.
-	\bibitem[Mishra(2019)]{Mishra2019}
-	Mishra,~P.; Pandey,~C.M.; Singh,~U.; Gupta,~A.; Sahu,~C.; Keshri,~A. Descriptive Statistics and Normality Tests for Statistical Data. {\em Ann. Card. Anaesth.} {\bf 2019}, {\em 22}(1), 67--72. 	
-	\bibitem[Wilcoxon(1945)]{Wilcoxon1945}
-	Wilcoxon,~F. Individual Comparisons by Ranking Methods. {\em Biometrics Bull.} {\bf 1945}, {\em 1}, 80--83.
-	\bibitem[McDonald(2014)]{McDonald2014}
-	McDonald,~J.H. \textit{Handbook of Biological Statistics}, 3rd ed.; Sparky House Publishing: Sparky House Publishing, USA, 2014; pp. 186--189.
 	\bibitem[OpenIntro(2019)]{OpenIntro2019}
 	Diez,~D.; \c{C}etinkaya-Rundel,~M.; Barr,~C.D. \textit{OpenIntro Statistics}, 4th ed.; 2019. \url{https://www.openintro.org/book/os/}
+	\bibitem[Ji(2019)]{Ji2019}
+	Ji,~N.; Zhou,~H.; Guo,~K.; Samuel,~O.W.; Huang,~Z.; Xu,~L.; Li,~G.
+Appropriate Mother Wavelets for Continuous Gait Event Detection Based on Time-Frequency Analysis for Hemiplegic and Healthy Individuals.
+{\em Sensors} {\bf 2019}, {\em 19}(16):3462.
+	\bibitem[Carcreff(2018)]{Carcreff2018}
+	Carcreff,~L.; Gerber,~C.N.; Paraschiv-Ionescu,~A.; De~Coulon,~G.; Newman,~C.J.; Armand,~S.; Aminian,~K.
+What is the Best Configuration of Wearable Sensors to Measure Spatiotemporal Gait Parameters in Children with Cerebral Palsy?
+{\em Sensors} {\bf 2018}, {\em 18}(2):394.
 \end{thebibliography}

### 2022-03-18 paper/MDPI_template/table_demograpics_data.tex
Extended discussion. Add figure to explain TCN arch

--- 2022-03-18 paper/MDPI_template/article.tex
@@
-%  LaTeX support: latex@mdpi.com 
-%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.
-
-%=================================================================
-\documentclass[sensors,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
-% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept".
-The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}.
-This is especially recommended for submission to arXiv, where line numbers should be removed before posting.
-For preprints.org, the editorial staff will make this change immediately prior to posting.
-
-%--------------------
-% Class Options:
-%--------------------
-%----------
-% submit
-%----------
-% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
-This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information.
-Also, line numbering will be removed.
-Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
-
-%------------------
-% moreauthors
-%------------------
-% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
-
-%---------
-% pdftex
-%---------
-% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.
-
-%=================================================================
-% MDPI internal commands
-\firstpage{1} 
-\makeatletter 
-\setcounter{page}{\@firstpage} 
-\makeatother
-\pubvolume{1}
-\issuenum{1}
-\articlenumber{0}
-\pubyear{2022}
-\copyrightyear{2022}
-%\externaleditor{Academic Editor: Firstname Lastname}
-\datereceived{} 
-\dateaccepted{} 
-\datepublished{} 
-%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
-%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
-\hreflink{https://doi.org/} % If needed use \linebreak
-%\doinum{}
-%------------------------------------------------------------------
-% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
-%\pdfoutput=1
-
-%=================================================================
-% Add packages and commands here.
-The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
-
-%=================================================================
-%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
-%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
-
-%=================================================================
-% Full title of the paper (Capitalized)
-\Title{A Deep Learning Approach for Gait Event Detection from a Single Shank-Worn IMU: Validation in Healthy and Neurological Cohorts}
-
-% MDPI internal command: Title for citation in the left column
-\TitleCitation{A Deep Learning Approach for Gait Event Detection from a Single Shank-Worn IMU: Validation in Healthy and Neurological Cohorts}
-
-% Author Orchid ID: enter ID or remove command
-\newcommand{\orcidauthorA}{0000-0002-2507-0924} % Add \orcidA{} behind the author's name
-%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
-
-% Authors, for the paper (add full first names)
-\Author{Robbin Romijnders$^{1}$*\orcidA{}, Elke Warmerdam$^{2}$, Clint Hansen$^{1}$*, Gerhard Schmidt$^{3}$ and Walter Maetzler$^{1}$}
-
-%\longauthorlist{yes}
-
-% MDPI internal command: Authors, for metadata in PDF
-\AuthorNames{Robbin Romijnders, Elke Warmerdam, Clint Hansen, Gerhard Schmidt and Walter Maetzler}
-
-% MDPI internal command: Authors, for citation in the left column
-\AuthorCitation{Romijnders, R.; Warmerdam, E.; Hansen, C.; Schmidt, G.; Maetzler, W.}
-% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
-
-% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-\address{%
-$^{1}$ \quad Department of Neurology, Kiel University, 24105 Kiel, Germany; r.romijnders@neurologie.uni-kiel.de (R.R.), c.hansen@neurologie.uni-kiel.de (C.H.), w.maetzler@neurologie.uni-kiel.de (W.M.)\\
-$^{2}$ \quad xxxxx, xxxxx, xxxxx Homburg, Germany; elke.warmerdam@uni-saarland.de (E.W.)\\
-$^{3}$ \quad Institute of Electrical Engineering and Information Technology, Faculty of Engineering, Kiel University, 24143 Kiel, Germany; gus@tf.uni-kiel.de (G.S.)}
-
-% Contact information of the corresponding author
-\corres{Correspondence: r.romijnders@neurologie.uni-kiel.de (R.R.)}
-
-% Current address and/or shared authorship
-%\firstnote{Current address: Affiliation 3.} 
-%\secondnote{These authors contributed equally to this work.}
-% The commands \thirdnote{} till \eighthnote{} are available for further notes
-
-%\simplesumm{} % Simple summary
-
-%\conference{} % An extended version of a conference paper
-
-% Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{A single paragraph of about 200 words maximum.
-For research articles, abstracts should give a pertinent overview of the work.
-We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: describe briefly the main methods or treatments applied; (3) Results: summarize the article's main findings; (4) Conclusions: indicate the main conclusions or interpretations.
-The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}
-
-% Keywords
-\keyword{keyword 1; keyword 2; keyword 3 (List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.)}
-
-% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
-%\PACS{J0101}
-%\MSC{}
-%\JEL{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Diversity
-%\LSID{\url{http://}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Applied Sciences:
-%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Data:
-%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately.
-If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal.
-In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}
-
-%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Toxins
-%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Encyclopedia
-%\encyclopediadef{Instead of the abstract}
-%\entrylink{The Link to this entry published on the encyclopedia platform.}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
-Gait deficits are common in older adults and possibly reflect the presence of an underlying neurodegenerative disease \cite{Snijders2007,Hodgins2008}.
-For example, conversion to Parkinson's Disease \cite{DelDin2019} or from mild cognitive impairment to Alzheimer's Disease \cite{Koenig2017,Bertoli2018} are linked with changes in spatiotemporal gait parameters.
-Similarly, temporal gait parameters are different for stroke patients \cite{SchroederVon1995,Mohan2021} and patients with multiple sclerosis \cite{Griskevicius2016,Flachenecker2019} when compared to healthy controls.
-To objectively quantify gait deficits, stride-specific parameters such as stride time or stride length are often used \cite{Hannink2016}, where the beginning and end of a stride are determined from two successive initial contacts (ICs) of the same foot \cite{Perry2010,Whittle2012}.
-The IC is when the foot contacts the ground and together with the instant at which the foot leaves the ground (final contact, FC), each stride can be divided in a stance and swing phase \cite{Rueterbories2010,Bruening2014}.
-The events of IC and FC, also referred to as \emph{gait events}, are commonly determined using force or pressure measuring devices \cite{Bruening2014}, or passive, retro-reflective marker-based optoelectronic motion capture systems (henceforth referred to as the \emph{marker-based} system or method) \cite{Chiari2005,Topley2020}.
-These systems are relatively expensive, and restricted to usage in expertise laboratories \cite{Iosa2016,Jarchi2018}.
-As there is increasing evidence that gait measured in the lab does not reflect daily-life gait \cite{Hillel2019,Warmerdam2020,Atrsaei2021}, there is more and more interest in measurement systems that allow for continuous gait analysis in ambulatory settings.
-Therefore, the use of inertial measurement units (IMUs) is especially attractive, as these can be used to measure gait in ecologically valid environments, such as the home environment, thereby painting a more complete picture of health status \cite{DelDin2016,Shah2020} and providing clinical information that is complementary to standardized lab-based assessments \cite{Warmerdam2020,Fasano2020,Atrsaei2021,Corra2021}.
-
-Previous research suggests that gait event detection is more accurate using an IMU worn on a lower limb (e.g., shank or foot) compared to an IMU worn on the low back \cite{BenMansour2015,Storm2016,Panebianco2018}.
-Now, in order to get from abstract IMU sensor readings to clinically relevant gait parameters (e.g., from accelerations and angular velocities to stride times) \cite{Hannink2016}, different algorithmic approaches have been developed in the last twenty years of clinical gait research.
-A recent study has evaluated a cross-section of these algorithms for different sensor locations on the lower leg and foot \cite{Niswander2021}.
-The algorithms were categorized according to which signals were analyzed, for example the angular velocity about the medio-lateral axis, or the accelerations along vertical and antero-posterior axis.
-This means the sensor readings need to be linked with the anatomical axes, that is, one needs to know which sensor axis aligns with for example the medio-lateral axis.
-In most approaches, it is simply assumed that due to sensor attachment the sensor axis aligns roughly with the anatomical axis of interest (\cite{Salarian2004,Sabatini2005,Jasiewicz2006,Catalfamo2010,Trojaniello2014,Maqbool2016,Romijnders2021}) or an additional calibration procedure (e.g., \cite{Ferraris1995}) is required (\cite{Greene2010,Niswander2021}).
-In ambulatory assessments however, study participants often attach the sensor themselves, and therefore the sensor location and alignment cannot be controlled for.
-Furthermore, it is unlikely that each time the sensor is (re-)attached study participants, especially those with gait deficits, perform a calibration procedure that usually consists of holding a pre-defined pose and performing some known movement sequences (TODO: reference?!
-Kong?
-Seel?).
-
-Taken together, this drives the need for an approach that is invariant to sensor orientation, and is applicable across a variety of pathological gait patterns.
-As pointed out by \cite{Hannink2016}, in the field of image analysis similar requirements have been successfully addressed by algorithms that share a common underlying methodology referred to as deep learning \cite{LeCun2015,TerHaarRomeny2019}.
-Recent applications of deep learning algorithms have already shown improved performance in detecting gait events from marker-based motion capture when compared to conventional, often heuristics-based, algorithms \cite{Kidzinski2019,Lempereur2020,Filtjens2020}.
-Another study used a deep learning approach to detect gait events from either three IMUs (worn on the low back, and both ankles) or a single IMU (worn on the low back), and showed that the time error was considerably smaller for the deep learning algorithm than for a commonly applied wavelet-based approach \cite{Gadaleta2019}.
-
-In this study, we further these works by validating this deep learning approach for detecting gait events in a heterogeneous cohort of healthy and neurologically diseased adults considering a single IMU setup, worn on the lower leg.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Materials and Methods}
-\subsection{Data Collection}
-Gait analyses were performed in the Universit\"{a}tsklinikum Schleswig-Holstein (UKSH) campus Kiel, Germany.
-The study \cite{Warmerdam2021} was approved by the ethical committee of the medical faculty at the UKSH (no: D438/18).
-In total, data from 160 participants were included for the current analysis, including data from young adults (YA; age: 18 - 60 years), older adults (OA; age: $>$60 years), people with Parkinson's Disease (PD; according to the UK Brain Bank criteria \cite{Gibb1988}), people with a recent ($<$4 weeks) symptomatic stroke (stroke), people with multiple sclerosis (MS; according to the McDonalds criteria \cite{Thompson2018}), people with chronic low back pain (cLBP), and people with other diagnoses that were assumed not to affect mobility (Table \ref{tab:demographics_data}).
-Inclusion criteria were an age of 18 years or older, and the ability to walk independently without a walking aid.
-Participants were excluded from the study with a Montreal Cognitive Assessment \cite{Nasreddine2005} score $<$15 and other movement disorders that affected mobility, as noticed by the clinical assessor.
-
 \begin{table}[H] 
@@
 
-\begin{figure}[H]
-	\begin{adjustwidth}{-\extralength}{0cm}
-		\centering
-		\includegraphics[width=13.5cm]{fig/methods_overall_workflow.pdf}
-	\end{adjustwidth}
-	\caption{Schematic depiction$^{1}$ of the current study.
-Study participants wore IMUs on the ankle and shanks, and reflective markers were adhered on the heel and toe of usual footwear (shown on the left).
-Marker data were used to obtain reference values for the timings of initial and final contacts (top), where accelerometer and gyroscope data from each tracked point were inputted to a neural network that predicted timings of the same initial and final contacts (bottom).
-\newline \noindent{\footnotesize{\textsuperscript{1} Picture from: \url{https://www.vecteezy.com/free-vector/man-walking }.}} \label{fig:methods_marker_vs_imu}}
-\end{figure}
-
-Participants performed three walking trials consisting of walking 5 meter at either (1) preferred speed ("\emph{Please walk at your normal walking speed.}"), (2) slow speed ("\emph{Please walk half of your normal walking speed.}"), or (3) fast speed ("\emph{Please walk as fast as possible, without running or falling.}").
-The 5 meter distance was marked with two cones on both ends, and participants were asked to start walking approximately two steps before the cones on one end, and stop walking approximately two steps after passing the cones on the other end.
-
-For the current analysis data from four IMUs (Noraxon USA Inc., myoMOTION, Scottsdale, AZ, USA) were considered, namely those that were attached laterally above the left and right ankle joint and those attached proximally at the left and right shank.
-IMUs were secured to participants using elastic bands with a special hold for the IMU.
-Furthermore, reflective markers were attached on top of the usual foot wear at the heel and toe of both feet (Figure~\ref{fig:methods_marker_vs_imu}).
-Marker data were recorded using a twelve-camera optoelectronic motion capture system (Qualisys AB, G\"{o}teborg, Sweden) at a sampling frequency of 200 Hz.
-IMU data were recorded at the same sampling frequency, and both systems were synchronized using a TTL signal \cite{Warmerdam2021}.
-For some recordings, the sampling frequency of the IMUs was erroneously set at 100 Hz, and therefore data from these trials were upsampled before further analysis.
-
-\subsection{Data Pre-processing \label{subsec:data_preprocessing}}
-\subsubsection{Marker Data}
-The reflective marker data were first used to determine start and end of each trial.
-The start of the trial was defined as the time for which the first toe marker (left or right) crossed the \emph{virtual} starting line.
-The end was defined as the time for which the last heel marker crossed the end line.
-For both marker and IMU systems, data were then cropped from start to the end of the trial.
-
-Any remaining gaps in the marker data were filled by interpolation making use of inter-correlations between markers \cite{Federolf2013,Gloersen2016}.
-The data were then low-pass filtered using a double pass 6th order Butterworth filter with a cut-off frequency of 20 Hz \cite{Kormylo1974,Racz2021}.
-The filtered data were differentiated to get velocity signals, and timings of ICs and FCs were determined from local maxima and minima in the heel and toe vertical velocity signals \cite{Pijnappels2001,OConnor2007}.
-Like in \cite{Carcreff2018,Romijnders2021}, all identified ICs and FCs were manually checked, and corrected if necessary, using Qualisys Track Manager 2018.1 software (Qualisys AB, Göteborg, Sweden).
-The resulting annotated ICs and FCs were considered the \emph{true} events (also \emph{labels} or \emph{targets}), and were used as reference timings to derive stride-specific gait parameters.
-
-\subsubsection{IMU Data}
-The idea behind the deep learning approach was that a \emph{model} was trained to predict the likelihood of an IC and FC, given accelerometer and gyroscope data from a single IMU.
-In other words, the model was iteratively trained to learn a mapping $h_{\mathbf{W}}(\mathbf{X}): \mathbf{X} \rightarrow \mathbf{y}$, where $h_{\mathbf{W}}$ was also referred to as the \emph{hypothesis} parameterized by the weights, collectively denoted by $\mathbf{W}$, $\mathbf{X}$ was the matrix of IMU data, and $\mathbf{y}$ was the vector of annotated events.
-
-Here, the matrix $\mathbf{X}$ consisted of the IMU data, arranged as:
-\begin{equation}
-	\mathbf{X} = \begin{bmatrix}
-		\rule[0ex]{0.5pt}{2.5ex} & \rule[0ex]{0.5pt}{2.5ex} &  & \rule[0ex]{0.5pt}{2.5ex}\\
-		\mathbf{x}_{1} & \mathbf{x}_{2} & \cdots & \mathbf{x}_{D}\\
-		\rule[0ex]{0.5pt}{2.5ex} & \rule[0ex]{0.5pt}{2.5ex} &  & \rule[0ex]{0.5pt}{2.5ex}
-	\end{bmatrix} = \begin{bmatrix}
-		x_{1}[1] & x_{2}[1] & & x_{D}[1]\\
-		x_{1}[2] & x_{2}[2] & & x_{D}[2]\\
-		\vdots & \vdots & \cdots & \vdots\\
-		x_{1}[N] & x_{2}[1] & & x_{D}[N]\end{bmatrix}, \quad \mathbf{X} \in \mathbb{R}^{N \times D}
-	\label{eqn:train_data_single_instance}
-\end{equation}
-where $\mathbf{x}_{d} = \begin{bmatrix}x_{d}[1] & x_{d}[2] & \cdots & x_{d}[n] & \cdots & x_{d}[N]\end{bmatrix}^{\mathrm{T}}$, with $d = 1, \cdots, D$ referred to the $d$-th channel, and $n = 1, \cdots, N$ referred to the $n$-th sample (or discrete time step).
-
-Accordingly, the vector $\mathbf{y}$ consisted of the annotated events, arranged as:
-\begin{equation}
-	\mathbf{y}_{\mathrm{IC}} = \begin{bmatrix}
-		y_{1}[1]\\
-		y_{1}[2]\\
-		\vdots\\
-		y_{1}[N]
-	\end{bmatrix}, \quad \mathbf{y}_{\mathrm{FC}} = \begin{bmatrix}
-		y_{2}[1]\\
-		y_{2}[2]\\
-		\vdots\\
-		y_{2}[N]
-	\end{bmatrix}, \quad y_{i}[n] \in [0, 1]
-	\label{eqn:train_labels_single_instace}
-\end{equation}
-
-The data were split in three independent data sets, namely a training set, a validation set, and a test set.
-Each set contained data from approximately one-third of the participants.
-Participants were randomly assigned to one of the sets, stratified by both group (i.e., diagnosis) and gender (Table~\ref{tab:demographics_data}).
-
-Accelerometer and gyroscope data were normalized by subtracting the channel-wise mean, and dividing by the channel-wise standard deviation.
-Then, for the training and validation data set, the data were partitioned into equal length time windows \cite{Filtjens2020} of 400~samples, with an overlap of 50\% between successive windows (corresponding to 2 s windows, and 1 s overlap, respectively).
-
-\subsection{Model}
-\subsubsection{Model Architecture}
-The basic architecture for the deep learning model was a temporal convolutional network (TCN) \cite{Bai2018,Remy2020,Filtjens2020}.
-The TCN consisted of repeating blocks of dilated convolutions (CONV) \cite{YuKoltun2016,Bai2018} that were followed by batch normalization (BN) \cite{Ioffe2015}, rectified linear unit (ReLU) activation, and dropout (DropOut) \cite{Srivastava2014}.
-For each given dilation factor, the sequence of layers CONV-BN-ReLU-DropOut was repeated twice \cite{Remy2020}.
-Dilation factors were given as a sequence of increasing powers of 2, e.g., $\left\{1, 2, 4, 8\right\}$ \cite{VanDenOord2016,YuKoltun2016,Bai2018}.
-These repeating blocks were followed by a fully-connected (dense) layer with sigmoid activation, and outputs were predicted separately for ICs and FCs.
-The mean squared error (MSE) was used as loss function, and a gradient descent-based optimization algorithm with adaptive moment (Adam) optimizer was used to iteratively learn the weights \cite{Kingma2014,Schmidt2021}.
-
-\subsubsection{Hyperparameter Optimization}
-In order to find the best model architecture, hyperparameter tuning was perfomed using KerasTuner \cite{OMalley2019}.
-Here, the number of filters, the kernel size, and the maximum dilation factor (Table \ref{tab:hyperparameter_optimization}) were optimized for using a random search strategy \cite{Bergstra2012}.
-
-\begin{table}[H] 
-	\caption{Model hyperparameters that were optimized for, and the corresponding sets of possible values.\label{tab:hyperparameter_optimization}}
-	\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabularx}{\textwidth}{CC}
-		\toprule
-		\textbf{Description}	& \textbf{Possible values}\\
-		\midrule
-		Number of filters	& 8, 16, 32, 64, 128\\
-		Kernel size			& 3, 5, 7\\
-		Dilations 			& [1, 2], [1, 2, 4], [1, 2, 4, 8]\\
-		\bottomrule
-	\end{tabularx}
-\end{table}
-
-The model architecture that resulted from the hyperparameter optimization was then trained on the combined set of training and validation data.
-The trained model was used to predict occurrence of gait events from the hold-out test set.
-
-\subsection{Analysis}
-The predictions of the model on the test set data were compared with the labels from the test set.
-The model performance was evaluated for (1) overall detection performance, (2) time agreement between the predicted events and the (marker-based) annotated events, (3) agreement between subsequently derived gait parameters.
-\subsubsection{Overall detection performance \label{subsubsec:overall_detection_performance}}
-The overall detection performance quantified how many of the annotated evens were detected by the model (true positives, TP), how many of the annotated events were not detected (false negatives, FN), and how many event that were detected, were actually not annotated (false positives, FP).
-From these metrics, the recall (or sensitivity), precision and F$_{1}$ score were calculated as:
-\begin{equation}
-	\textrm{recall} = \frac{\textrm{TP}}{\textrm{TP} + \textrm{FN}} \nonumber
-	\label{eqn:recall}
-\end{equation}
-\begin{equation}
-	\textrm{precision} = \frac{\textrm{TP}}{\textrm{TP} + \textrm{FP}} \nonumber
-	\label{eqn:precision}
-\end{equation}
-\begin{equation}
-	\textrm{F$_{1}$ score} = 2 \cdot \frac{\textrm{recall} \cdot \textrm{precision}}{\textrm{recall} + \textrm{precision}}  \nonumber
-	\label{eqn:f1_score}
-\end{equation}
-
-\subsubsection{Time Error}
-For all correctly detected gait events (TP, Section \ref{subsubsec:overall_detection_performance}), the time error between the annotated and detect gait event was defined as:
-\begin{equation}
-	\textrm{time error} = t_{\textrm{ref}} - t_{\textrm{pred}}
-	\label{eqn:time_agreement}
-\end{equation}
-with $t_{\mathrm{ref}}$ the gait event time from the marker-based annotations, and $t_{\mathrm{pred}}$ the gait event time from the model predictions.
-As a robust measure for the average time error and its spread, the median time error and the inter-quartile range (IQR) were reported \cite{OpenIntro2019}.
-
-\subsubsection{Stride Parameters}
-For those trials for which all gait events were detected, and no spurious events were detected, the stride time, stance time and swing were calculated.
-Stride was the time between two successive ICs of the same foot.
-Stance time was the time between FC and the preceding IC of the same foot.
-Swing time was the time between the IC following the last FC of the same foot.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-
-\subsection{Overall detection performance}
-The performance of detecting initial contacts and final contacts was objectively quantified by the number of annotated events that were detected (true positives, TP), the number of annotated events that were not detected (false negatives, FN), and the number of detected events that were not annotated (false positives, FP).
-From these, recall, precision and F$_{1}$ score were calculated (Table \ref{tab:overall_detection_performance}).
-\begin{table}[H]
-	\caption{Overall detection performance for initial contacts and final contacts as quantified by recall, precision and F$_{1}$ score.\label{tab:overall_detection_performance}}
-	\begin{adjustwidth}{-\extralength}{0cm}
-		\newcolumntype{C}{>{\centering\arraybackslash}X}
-		\begin{tabularx}{\fulllength}{r|CCCCCC|CCCCCC}
-			\toprule
-			 & \multicolumn{6}{c}{\textbf{Initial contacts}}	& \multicolumn{6}{c}{\textbf{Final contacts}}\\
-			\textbf{Tracked point}	& \textbf{TP}	& \textbf{FN}	& \textbf{FP}	& \textbf{recall}	& \textbf{precision}	& \textbf{F1}	& \textbf{TP}	& \textbf{FN}	& \textbf{FP}	& \textbf{recall}	& \textbf{precision} 	& \textbf{F1}\\
-			\midrule
-			left ankle		& 624	& 19	& 5		& 97\%	& 99\%	& 98\%		& 606	& 32	& 10	& 95\%	& 98\%	& 97\%\\
-			right ankle		& 599	& 42	& 8 	& 93\%	& 99\%	& 96\%		& 614	& 17	& 12	& 97\%	& 98\%	& 98\%\\
-			left shank		& 605	& 38	& 15	& 94\%	& 98\%	& 96\%		& 585	& 53	& 18	& 92\%	& 97\%	& 94\%\\
-			right shank		& 603	& 36	& 15 	& 94\%	& 98\%	& 96\%		& 595	& 30	& 9		& 95\%	& 99\%	& 97\%\\
-			\bottomrule
-		\end{tabularx}
-	\end{adjustwidth}
-	\noindent{\footnotesize{TP: true positives, FN: false negatives, FP: false positives, F1: F$_{1}$ score.}}
-\end{table}
-
-For both ICs and FCs, recall is high for each of the tracked points (i.e., $\ge 92\%$), and so is precision (i.e., $\ge 97\%$).
-Differences between the tracked points are small, i.e.
-the minimum recall is $92\%$ and the maximum recall is $97\%$, and the minimum precision is $97\%$ and the maximum precision is $99\%$.
-
-\subsection{Time Error}
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=13.5 cm]{fig/box_plots_tracked_points_with_outliers.png}
-	\caption{Time errors for initial (left) and final (right) contacts detection, for each of the different tracked points.\label{fig:time_error_box_plots}}
-\end{figure}
-
-Time errors for ICs and FCs are visually depicted using boxplots for each tracked point.
-Data were not normally distributed, thus Wilcoxon signed-rank tests were used to evaluate whether the median time error was zero.
-\begin{table}[H] 
-	\caption{Time errors for the correctly detected gait events. \label{tab:time_errors}}
-	\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabularx}{\textwidth}{r|CC|CC}
-		\toprule
-		 & \multicolumn{2}{c}{\textbf{Initial contacts}} & \multicolumn{2}{c}{\textbf{Final contacts}}\\
-		\textbf{Tracked point} & \textbf{median} & \textbf{IQR} & \textbf{median} & \textbf{IQR}\\
-		 & s & s & s & s \\
-		\midrule
-		left ankle & 0.000 & 0.020 & 0.000 & 0.010\\
-		right ankle & 0.000 & 0.020 & -0.005 & 0.015\\
-		left shank & -0.005 & 0.020 & -0.005 & 0.020\\
-		right shank & -0.003 & 0.020 & -0.005 & 0.020\\
-		\bottomrule
-	\end{tabularx}
-	\noindent{\footnotesize{IQR: inter-quartile range.}}
-\end{table}
-
-\subsection{Gait parameters}
-For those trials for which all gait events were correctly detected (and no spurious events were detected, i.e., no false positives), stride time, stance time and swing time were calculated.
-The mean difference and the limits of agreement between the NN-derived gait parameters and the marker-based annotations were calculated.
-
-For all stride-specific gait parameters, and for all tracked points, the mean difference compared to the marker-based reference values was close to zero, i.e., the maxmum mean difference was 0.003 s.
-Furthermore, for all gait parameters and for all tracked points the limits of agreement, based on a 95\% confidence interval were distributed around zero with the overall span between -0.049 s and 0.051 s.
-\begin{table}[H] 
-	\caption{Time agreement between the stride-specific parameters. \label{tab:stride_parameters}}
-	\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabularx}{\textwidth}{rrCC}
-		\toprule
-		\textbf{Tracked point} & \textbf{Parameters} & \textbf{Mean difference} & \textbf{Limits of Agreement}\\
-		 & & ms & (ms, ms)\\
-		\midrule
-		left ankle & stride time & 0.001 & (-0.035, 0.036)\\
-		 & stance time & 0.002 & (-0.039, 0.042)\\
-		 & swing time & -0.001 & (-0.045, 0.043)\\
-		\midrule
-		right ankle & stride time & 0.000 & (-0.039, 0.040)\\
-		 & stance time & -0.002 & (-0.048, 0.044)\\
-		 & swing time & 0.003 & (-0.046, 0.051)\\
-		\midrule
-		left shank & stride time & 0.001 & (-0.039, 0.041)\\
-		& stance time & 0.002 & (-0.043, 0.046)\\
-		& swing time & -0.001 & (-0.049, 0.047)\\
-		\midrule
-		right shank & stride time & -0.000 & (-0.031, 0.031)\\
-		& stance time & 0.002 & (-0.046, 0.049)\\
-		& swing time & -0.002 & (-0.049, 0.046)\\
-		\bottomrule
-	\end{tabularx}
-	\noindent{}
-\end{table}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=13.5cm]{fig/bland_altman_plots_stride_params.png}
-	\caption{The agreement of extracted gait parameters between the sensor-based and marker-based methods.\label{fig:gait_parameters_bland_altman_plots}}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
-The current study aimed to validate a deep learning approach for detecting gait events from a single IMU worn on the lower leg.
-Data from left and right ankle- and shank-worn IMUs were used for training a neural network to detect gait events from walking trials performed by healthy younger and older adults, participants diagnosed with Parkinson's Disease, multiple sclerosis, or chronic low back pain, participants who had a recent symptomatic stroke, and participants diagnosed with other neurological diseases.
-Participants walked a 5 meter distance at three different self-selected walking speeds.
-The gait event timings that were predicted by the neural network were compared to a common reference method, i.e., stereophotogrammetry, and clinically relevant stride-specific gait parameters were extracted.
-
-A first measure for the model performance was given by the recall (how many annotated events were detected) and precision (how many detected events were annotated).
-For both initial contacts and final contacts, a high recall ($\ge 95\%$) and high precision ($\ge 98\%$) were observed, meaning that most events can be detected and most detected events were actually true events.
-There was little difference in recall and precision between tracked points (Table~\ref{tab:overall_detection_performance}) confirming that the deep learning approach is relatively invariant to exact sensor localization.
-These values for recall and precision were slightly lower than our previously reported $100 \%$ \cite{Romijnders2021} that used a heuristics-based approach \cite{Salarian2004}, but in the current study more trials were included and from a more heterogeneous study population.
-
-Next, the time error, that is the difference between the annotated event and the detected event, was of interest.
-For both initial contacts and final contacts, and for all tracked points, the observed time error was small, and the middle $50\%$ of the time errors were within a range of $\left[-0.015,0.010\right]$ s (Table~\ref{tab:time_errors}, Figure~\ref{fig:time_error_box_plots}).
-These data showed that the deep learning-based is approach is precise in detecting initial and final contacts.
-Time errors were slightly smaller than our previously reported results \cite{Romijnders2021} that used a heuristics-based approach \cite{Salarian2004}.
-The heuristics-based approach determined ICs and FCs as local minima in the medio-lateral angular velocity \cite{Salarian2004} and it could be that these minima do not exactly coincide with the referent event timing as determined from the stereophotogrammetry.
-
-From the correctly detected gait events, stride-specific gait parameters were derived.
-These are probably of greatest clinical relevance, as changes in stride-specific gait parameters have been linked directly with disease onset and progression \cite{DelDin2019,Koenig2017,Bertoli2018,SchroederVon1995,Mohan2021,Griskevicius2016,Flachenecker2019}.
-Therefore, stride time, stance time, and swing time were calculated, and the differences between the deep learning-based approach and the marker-based reference method were quantified (Table~\ref{tab:stride_parameters}, Figure~\ref{fig:gait_parameters_bland_altman_plots}).
-The limits of agreement for a $95\%$ confidence interval were calculated, and for all metrics the zero mean difference was enclosed in the limit of agreement.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
-In this study we have validated a deep learning-based approach to detect gait events and subsequently extract clinically relevant stride parameters from a single inertial measurement unit.
-Performance analysis showed an excellent detection rate, and low time errors in both event detection and stride parameter calculation for different walking speeds and across both healthy and neurological cohorts.
-Our next step is to validate these methods under more challenging conditions, that involve real-life walking sequences.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{6pt}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}
-
-% Only for the journal Methods and Protocols:
-% If you wish to submit a video article, please do so with any other supplementary material.
-% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.
-A supporting video article is available at doi: link.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{Conceptualization, R.R., G.S., and W.M.; methodology, R.R., G.S.; software, R.R.; validation, R.R.,; formal analysis, R.R.; investigation, R.R., G.S., W.M.; resources, C.H, W.M..; data curation, E.W., R.R.,; writing---original draft preparation, R.R.; writing---review and editing, E.W., C.H., G.S., W.M.; visualization, R.R.; supervision, G.S., W.M.; project administration, R.R., E.W., C.H., G.S., W.M.; funding acquisition, W.M.
-All authors have read and agreed to the published version of the manuscript.}
-
-\funding{This research received funding from the DFG Open Access fund.}
-
-\institutionalreview{The study was conducted in accordance with the Declaration of Helsinki, and approved by the Ethics Committee of the medical faculty of the Christian-Albrechts-Universit\"{a}t zu Kiel (D438/18, approved on 8 May 2018).}
-
-\informedconsent{Informed consent was obtained from all subjects involved in the study.}
-
-\dataavailability{Data from the first 10 participant are available online at \url{https://github.com/neurogeriatricskiel/Validation-dataset}.
-Additionally, we are preparing the open-source release of all data from the healthy younger and older adults.
-Data from ptient groups }
-
-\acknowledgments{The authors sincerely thank all people that were involved in the data collection, from study participants to students who aided and assisted during measurements and subsequent marker labeling.
-The authors appreciate the off- and on-topic discussions with Julius Welzel, and his positive contributions to the organization of the research data.
-The authors give a thumbs up to Johannes Hoffmann for his tips and tricks regarding the \LaTeX typesetting.}
-
-\conflictsofinterest{The authors declare no conflict of interest.}
-
-%% Optional
-% \sampleavailability{Samples of the compounds ... are available from the authors.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Only for journal Encyclopedia
-%\entrylink{The Link to this entry published on the encyclopedia platform.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Optional
-\abbreviations{Abbreviations}{
-The following abbreviations are used in this manuscript:\\
-
-\noindent 
-\begin{tabular}{@{}ll}
-	cLBP & chronic low back pain\\
-	CNN & convolutional neural network\\
-	IMU & inertial measurement unit\\
-	MS & multiple sclerosis\\
-	OA & older adults\\
-	PD & Parkinson's Disease\\
-	TCN & temporal convolutional network\\
-	YA & younger adults
-\end{tabular}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% Optional
-%\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A").
-If the appendix sections contain a heading then change the argument to "yes".
-%\appendixstart
-%\appendix
-%\section[\appendixname~\thesection]{}
-%\subsection[\appendixname~\thesubsection]{}
-%The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data.
-Mathematical proofs of results not central to the paper can be added as an appendix.
-%
-%\begin{table}[H] 
-%\caption{This is a table caption.\label{tab5}}
-%\newcolumntype{C}{>{\centering\arraybackslash}X}
-%\begin{tabularx}{\textwidth}{CCC}
-%\toprule
-%\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-%\midrule
-%Entry 1		& Data			& Data\\
-%Entry 2		& Data			& Data\\
-%\bottomrule
-%\end{tabularx}
-%\end{table}
-%
-%\section[\appendixname~\thesection]{}
-%All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{adjustwidth}{-\extralength}{0cm}
-%\printendnotes[custom] % Un-comment to print a list of endnotes
-
-\reftitle{References}
-
-% Please provide either the correct journal abbreviation (e.g.
-according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
-% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
-
-%=====================================
-% References, variant A: external bibliography
-%=====================================
-%\bibliography{your_external_BibTeX_file}
-
-%=====================================
-% References, variant B: internal bibliography
-%=====================================
-\begin{thebibliography}{999}
-	\bibitem[Snijders(2007)]{Snijders2007}
-	Snijders,~A.H.; {van de Warrenburg},~B.P.; Giladi,~N.; Bloem,~B.R.
-Neurological gait disorders in elderly people: clinical approach and classification.
-{\em Lancet Neurol.} {\bf 2007}, {\em 6}(1), 63--74.
-	\bibitem[Hodgins(2008)]{Hodgins2008}
-	Hodgins,~D. The importance of measuring human gait. {\em Med. Device Technol.} {\bf 2008}, {\em 19}(5):42, 44-7.
-	\bibitem[DelDin(2019)]{DelDin2019}
-	{Del Din},~S.; Elshehabi,~M.; Galna,~B.; Hobert,~M.A.; Warmerdam,~E.; Suenkel,~U.; Brockmann,~K.; Metzger,~F.; Hansen,~C.; Berg,~D.; Rochester,~L.; Maetzler,~W.
-Gait analysis with wearables predicts conversion to Parkinson disease.
-{\em Ann.
-Neurol.} {\bf 2019}, {\em 86}(3), 357--367.
-	\bibitem[Koenig(2017]{Koenig2017}
-	K\"{o}nig,~A.; Klaming,~L.; Pijl,~M.; Demeurraux,~A.; Davis,~R.; Robert,~P.
-Objective measurement of gait parameters in healthy and cognitively impaired elderly using the dual-task paradigm.
-{\em Aging.
-Clin.
-Exp.
-Res.} {\bf 2017}, {\em 29}(6), 1181--1189.
-	\bibitem[Bertoli(2018)]{Bertoli2018}
-	Bertoli,~M.; Cereatti,~A.; Trojaniello,~D.; Avanzino,~L.; Pelosin,~E.; Del Din,~S.; Rochester,~L.; Ginis,~P.; Bekkers,~E.M.J.; Mirelman,~A.; Hausdorff,~J.M.; {Della Croce},~U.
-Estimation of spatio-temporal parameters of gait from magneto-inertial measurement units: multicenter validation among Parkinson, mildly cognitively impaired and healthy older adults.
-{\em Biomed.
-Eng.
-Online} {\bf 2018}, {\em 17}(58).
-	\bibitem[SchroederVon(1995)]{SchroederVon1995}
-	von Schroeder,~H.P.; Coutts,~R.D.; Lyden,~P.D.; Billings,~E.,~Jr; Nickel,~V. L. Gait parameters following stroke: a practical assessment. {\em J. Rehabil. Res. Dev.} {\bf 1995}, {\em 32}(1), 25--31.
-	\bibitem[Mohan(2021)]{Mohan2021}
-	Mohan,~D.M.; Khandoker,~A.H.; Wasti,~S.A.; Ismail~Ibrahim~Ismail~Alali,~S.; Jelinek,~H.F.; Khalaf,~K.
-Assessment methods of post-stroke gait: A scoping review of technology-driven approaches to gait characterization and analysis.
-{\em Front.
-Neurol.} {\bf 2021}, {\em 12}.
-	\bibitem[Griskevicius(2016)]{Griskevicius2016}
-	Gri\v{s}kevi\v{c}ius,~J.; Apanskien\.{e},~V.; \v{Z}i\v{z}ien\.{e},~J.; Daunoravi\v{c}ien\.{e},~K.; Ov\v{c}inikova,~A.; Kizlaitien\.{e},~R.; Sereik\.{e},~I.; Kaubrys,~G.; Pauk,~J.; Id\'{z}kowski,~A.
-Estimation of temporal gait parameters of multiple sclerosis patients in clinical setting using inertial sensors.
-In Proceedings of the 11th Int Conf BIOMDLORE 2016, Druskininkai, Lithuania, 20--22 Oct 2016; 80--82.
-	\bibitem[Flachenecker(2019)]{Flachenecker2019}
-	Flachenecker,~F.; Ga{\ss}ner,~H.; Hannik,~J.; Lee,~D.H.; Flachenecker,~P.; Winkler,~J.; Eskofier,~B.; Linker,~R.A.; Klucken,~J.
-Objective sensor-based gait measures reflect motor impairment in multiple sclerosis patients: Reliability and clinical validation of a wearable sensor device.
-{\em Mult.
-Scler.
-Relat.
-Dis.} {\bf 2019}, {\em 39}, 101903.
-	\bibitem[Hannink(2016)]{Hannink2016}
-	Hannink,~J.; Kautz,~T.; Pasluosta,~C.F.; Ga{\ss}mann,~K.-G.; Klucken,~J.; Eskofier,~B.M.
-Sensor-Based Gait Parameter Extraction With Deep Convolutional Neural Networks.
-{\em IEEE J.
-Biomed.
-Health} {\bf 2017}, {\em 21}(1), 85--93.
-	\bibitem[Perry(2010)]{Perry2010}
-	Perry,~J; Burnfield,~J.M. \textit{Gait analysis: normal and pathological gait}, 2nd ed.; SLACK Inc.: Thorofare, NJ, USA, 2010.
-	\bibitem[Whittle(2012)]{Whittle2012}
-	Richards,~J.; Levine,~D.; Whittle,~M. \textit{Whittle's Gait Analysis}, 5th ed.; Churchill Livingstone: London, UK, 2012.
-	\bibitem[Rueterbories(2010)]{Rueterbories2010}
-	Rueterbories,~J.; Spaich,~E.G.; Larsen,~B.; Andersen,~O.K. Methods for gait event detection and analysis in ambulatory systems. {\em Med. Eng. Phys.} {\bf 2010}, {\em 32}(6), 545--552.
-	\bibitem[Bruening(2014)]{Bruening2014}
-	Bruening,~D.A.; Ridge,~S.T. Automated event detection algorithms in pathological gait. {\em Gait Posture} {\bf 2014}, {\em 39}(1), 472--477.
-	\bibitem[Chiari(2005)]{Chiari2005}
-	Chiari,~L.; Della~Croce,~U.; Leardini,~A.; Cappozzo,~A. Human movement analysis using stereophotogrammetry: Part 2: Instrumental errors {\em Gait Posture} {\bf 2005}, {\em 21}(2), 197--211.
-	\bibitem[Topley(2020)]{Topley2020}
-	Topley,~M.; Richards,~J.G. A A comparison of currently available optoelectronic motion capture systems. {\em J. Biomech.} {\bf 2020}, {\em 106}:109820.	
-	\bibitem[Iosa(2016)]{Iosa2016}
-	Iosa,~M.; Picerno,~P.; Paolucci,~S.; Morone,~G. Wearable inertial sensors for human movement analysis. {\em Expert Rev. Med. Devic.} {\bf 2016}, {\em 13}(7), 641--659.
-	\bibitem[Jarchi(2018)]{Jarchi2018}
-	Jarchi,~D.; Pope,~J.; Lee,~T.K.M.; Tamjidi,~L.; Mirzaei,~A.; Sanei,~S.
-A Review on Accelerometry-Based Gait Analysis and Emerging Clinical Applications.
-{\em IEEE Rev.
-Biomed.
-Eng.} {\bf 2018}, {\em 11}, 177--194.
-	\bibitem[Hillel(2019)]{Hillel2019}
-	Hillel,~I; Gazit,~E.; Nieuwboer,~A.; Avanzino,~L.; Rochester,~L.; Cereatti,~A.; Della~Croce,~U.; Rikkert,~M.O.; Bloem,~B.R.; Pelosin,~E.; Del~Din,~S.; Ginis,~P.; Giladi,~N.;  Mirelman,~A.; Hausdorff,~J.M.
-Is every-day walking in older adults more analogous to dual-task walking or to usual walking?
-Elucidating the gaps between gait performance in the lab and during 24/7 monitoring.
-{\em Eur.
-Rev.
-Aging Phys.
-A.} {\bf 2019}, {\em 16}(6).
-	\bibitem[Warmerdam(2020)]{Warmerdam2020}
-	Warmerdam,~E.; Hausdorff,~J.M.; Atrsaei,~A.; Zhou,~Y.; Mirelman,~A.; Aminian,~K.; Espay,~A.J.; Hansen,~C.; Evers,~L.J.W.; Keller,~A.; Lamoth,~C.; Pilotto,~A.; Rochester,~L.; Schmidt,~G.; Bloem,~B.R.; Maetzler,~W.
-Long-term unsupervised mobility assessment in movement disorders.
-{\em Lancet Neurol.} {\bf 2020}, {\em 19}(5), 462--470.
-	\bibitem[Atrsaei(2021)]{Atrsaei2021}
-	Atrsaei,~A.; Corr\'{a},~M.F.; Dadashi,~F.; Vila-Ch\~{a},~N.; Maia,~L.; Mariani,~B.; Maetzler,~W.; Aminian,~K.
-Gait speed in clinical and daily living assessments in Parkinson’s disease patients: performance versus capacity.
-{\em npj Parkinsons Dis.} {\bf 2021}, {\em 7}(1):24.
-	\bibitem[DelDin(2016)]{DelDin2016}
-	Del~Din,~S.; Godfrey,~A.; Mazz\`{a},~C.; Lord,~S.; Rochester,~L. Free-living monitoring of Parkinson's disease: Lessons from the field. {\em Movement Disord.} {\bf 2016}, {\em 31}(9), 1293--1313.
-	\bibitem[Shah(2020)]{Shah2020}
-	Shah,~V.V.; McNames,~J.; Mancini,~M.; Carlson-Kuhta,~P.; Nutt,~J.G.; El-Gohary,~M.; Lapidus,~J.A.; Horak,~F.B.; Curtze,~C.
-Digital Biomarkers of Mobility in Parkinson's Disease During Daily Living.
-{\em J.
-Parkinson Dis.} {\bf 2020}, {\em 10}(3), 1099--1111.
-	\bibitem[Fasano(2020)]{Fasano2020}
-	Fasano,~A.; Mancini,~M. Wearable-based mobility monitoring: the long road ahead. {\em Lancet Neurol.} {\bf 2020}, {\em 19}(5), 378--379.
-	\bibitem[Corra(2021)]{Corra2021}
-	Corr\'{a},~M.F.; Atrsaei,~A.; Sardoreira,~A.; Hansen,~C.; Aminian,~K.; Correia,~M.; Vila-Ch\~{a},~N.; Maetzler,~W.; Maia,~L.
-Comparison of Laboratory and Daily-Life Gait Speed Assessment during ON and OFF States in Parkinson’s Disease.
-{\em Sensors} {\bf 2021}, {\em 21}(12):3974.
-	\bibitem[BenMansour(2015)]{BenMansour2015}
-	Ben~Mansour,~K.; Rezzoug,~N.; Gorce,~P.
-Analysis of several methods and inertial sensors locations to assess gait parameters in able-bodied subjects.
-{\em Gait Posture} {\bf 2015}, {\em 42}, 409--414.
-	\bibitem[Storm(2016)]{Storm2016}
-	Storm,~F.A.; Buckley,~C.J.; Mazz\`{a},~C. Gait event detection in laboratory and real life settings: Accuracy of ankle and waist sensor based methods. {\em Gait Posture} {\bf 2016}, {\em 50}, 42--46.
-	\bibitem[Panebianco(2018)]{Panebianco2018}
-	Panebianco,~G.P.; Bisi,~M.C.; Stagni,~R.; Fantozzi,~S.
-Analysis of the performance of 17 algorithms from a systematic review: Influence of sensor position, analysed variable and computational approach in gait timing estimation from IMU measurements.
-{\em Gait Posture} {\bf 2018}, {\em 66}, 76--82.
-	\bibitem[Niswander(2021)]{Niswander2021}
-	Niswander,~W.; Kontson,~K. Evaluating the Impact of IMU Sensor Location and Walking Task on Accuracy of Gait Event Detection Algorithms. {\em Sensors} {\bf 2021}, {\em 21}(12):3989.
-	\bibitem[Salarian(2004)]{Salarian2004}
-	Salarian,~A.; Russmann,~H.; Vingerhoets,~F.J.; Dehollain,~C.; Blanc,~Y.; Burkhard,~P.R.; Aminian,~K. Gait assessment in Parkinson's
-	disease: Toward an ambulatory system for long-term monitoring. {\em IEEE Trans. Biomed. Eng.} {\bf 2004}, {\em 51}(8), 1434--1443. 
-	\bibitem[Catalfamo(2010)]{Catalfamo2010}
-	Catalfamo,~P.; Ghoussayni,~S.; Ewins,~D. Gait Event Detection on Level Ground and Incline Walking Using a Rate Gyroscope. {\em Sensors} {\bf 2010}, {\em 10}(6), 5683--5702. 
-	\bibitem[Sabatini(2005)]{Sabatini2005}
-	Sabatini,~A.; Martelloni,~C.; Scapellato,~S.; Cavallo,~F. Assessment of Walking Features from Foot Inertial Sensing. {\em IEEE Trans. Biomed. Eng.} {\bf 2005}, {\em 52}(3), 486--494.
-	\bibitem[Maqbool(2016)]{Maqbool2016}
-	Maqbool,~H.F.; Husman,~M.A.B.; Awad,~M.; Abouhossein,~A.; Mehryar,~P.; Iqbal,~N.; Dehghani-Sanij,~A.A.
-Real-time gait event detection for lower limb amputees using a single wearable sensor.
-In Proceedings of the 2016 38th Ann.
-Int.
-Conf.
-of the IEEE Eng.
-in Med.
-Biol.
-Soc.
-(EMBC), Orlando, FL, USA, 16--20 Aug.
-2016, IEEE: Piscataway, NJ, USA, 2016.
-	\bibitem[Romijnders(2021)]{Romijnders2021}
-	Romijnders,~R.; Warmerdam,~E.; Hansen,~C.; Welzel,~J.; Schmidt,~G.; Maetzler,~W.
-Validation of IMU-based gait event detection during curved walking and turning in older adults and Parkinson's Disease patients.
-{\em J.
-Neuroeng.
-Rehabil.} {\bf 2021}, {\em 18}:28.
-	\bibitem[Jasiewicz(2006)]{Jasiewicz2006}
-	Jasiewicz,~J.M.; Allum,~J.H.; Middleton,~J.W.; Barriskill,~A.; Condie,~P.; Purcell,~B.; Li,~R.C.T.
-Gait event detection using linear accelerometers or angular velocity transducers in able-bodied and spinal-cord injured individuals.
-{\em Gait Posture} {\bf 2006}, {\em 24}(4), 502--509.
-	\bibitem[Trojaniello(2014)]{Trojaniello2014}
-	Trojaniello,~D.; Cereatti,~A.; Pelosin,~E.; Avanzino,~L.; Mirelman,~A.; Hausdorff,~J.M.; Della~Croce,~U.
-Estimation of step-by-step spatio-temporal parameters of normal and impaired gait using shank-mounted magneto-inertial sensors: Application to elderly, hemiparetic, parkinsonian and choreic gait.
-{\em J.
-Neuroeng.
-Rehabil.} {\bf 2014}, {\em 11}:152.
-	\bibitem[Ferraris(1995)]{Ferraris1995}
-	Ferraris,~F.; Grimaldi,~U.; Parvis,~M. Procedure for effortless in-field calibration of three-axis rate gyros and accelerometers. {\em Sensor. Mater.} {\bf 1995}, {\em 7}(5), 311--330.
-	\bibitem[Greene(2010)]{Greene2010}
-	Greene,~B.R.; McGrath,~D.; O'Neill,~R.; O'Donovan,~K.J.; Burns,~A.; Caulfield,~B.
-An adaptive gyroscope-based algorithm for temporal gait analysis.
-{\em Med.
-Biol.
-Eng.
-Comput.} {\bf 2010}, {\em 48}(12), 1251--1260.
-	\bibitem[LeCun(2015)]{LeCun2015}
-	LeCun,~Y.; Bengio,~Y.; Hinton,~G. Deep learning. {\em Nature} {\bf 2015}, {\em 521}, 436-444.
-	\bibitem[TerHaarRomeny(2019)]{TerHaarRomeny2019}
-	Ter Haar Romeny,~B.M.
-A Deeper Understanding of Deep Learning.
-In {\em Artificial Intelligence in Medical Imaging: Opportunities, Applications and Risks}; Ranschaert,~E.R., Morozov,~S., Algra,~P.R., Eds.; Springer Int.
-Publish.: Cham, Switzerland, 2019; pp.
-25--38.
-	\bibitem[Kidzinski(2019)]{Kidzinski2019}
-	Kidzi\'{n}ski,~{\L}.; Delp,~S.; Schwartz,~M. Automatic real-time gait event detection in children using deep neural networks. {\em PLoS ONE} {\bf 2019}, {\em 14}(1):e0211466.
-	\bibitem[Lempereur(2020)]{Lempereur2020}
-	Lempereur,~M.; Rousseau,~F.; R\'{e}my-N\'{e}ris,~O.; Pons,~C.; Houx,~L.; Quellec,~G.; Brochard,~S.
-A new deep learning-based method for the detection of gait events in children with gait disorders: Proof-of-concept and concurrent validity.
-{\em J.
-Biomech.} {\bf 2020}, {\em 98}, 109490.
-	\bibitem[Filtjens(2020)]{Filtjens2020}
-	Filtjens,~B.; Nieuwboer,~A.; D'cruz,~N.; Spildooren,~J.; Slaets,~P.; Vanrumste,~B.
-A data-driven approach for detecting gait events during turning in people with Parkinson's disease and freezing of gait.
-{\em Gait Posture} {\bf 2020}, {\em 80}, 130--136.
-	\bibitem[Gadaleta(2019)]{Gadaleta2019}
-	Gadaleta,~M.; Cisotto,~G.; Rossi,~M.; Ur~Rehman,~R.Z.; Rochester,~L.; Del~Din,~S.
-Deep Learning Techniques for Improving Digital Gait Segmentation.
-In Proceedings of the 2019 41st Ann.
-Int.
-Conf.
-of the IEEE Eng.
-in Med.
-Biol.
-Soc.
-(EMBC), Berlin, Germany, 23--27 Jul.
-2019, IEEE: Piscataway, NJ, USA, 2019.
-
-	% Materials and Methods
-	\bibitem[Warmerdam(2021)]{Warmerdam2021}
-	Warmerdam,~E.; Romijnders,~R.; Geritz,~J.; Elshehabi,~M.; Maetzler,~C.; Otto,~J.C.; Reimer,~M.; Stuerner,~K.; Baron,~R.; Paschen,~S.; Beyer,~T.; Dopcke,~D.; Eiken,~T.; Ortmann,~H.; Peters,~F.; von~der~Recke,~F.; Riesen,~M.; Rohwedder,~G.; Schaade,~A.; Schumacher,~M.; Sondermann,~A; Maetzler,~W.; Hansen,~C.
-Proposed Mobility Assessments with Simultaneous Full-Body Inertial Measurement Units and Optical Motion Capture in Healthy Adults and Neurological Patients for Future Validation Studies: Study Protocol.
-{\em Sensors} {\bf 2021}, {\em 21}(17):5833.
-	\bibitem[Gibb(1988)]{Gibb1988}
-	Gibb,~W.R.; Lees,~A.J. The relevance of the Lewy body to the pathogenesis of idiopathic Parkinson's disease. {\em J. Neurol. Neurosur. Ps.} {\bf 1988}, {\em 51}(6), 745--752.
-	\bibitem[Thompson(2018)]{Thompson2018}
-	Thompson,~A.J.; Banwell,~B.L.; Barkhof,~F.; Carroll,~W.M.; Coetzee,~T.; Comi,~G.; Correale,~J.; Fazekas,~F.; Filippi,~M.; Freedman,~M.S.; Fujihara,~K.; Galetta,~S.L.; Hartung,~H.P.; Kappos,~L.; Lublin,~F.D.; Marrie,~R.A.; Miller,~A.E.; Miller,~D.H.; Montalban,~X.; Mowry,~E.M.; Soelberg~Sorensen,~P.; Tintor\'{e},~M.; Traboulsee,~A.L.; Trojano,~M.; Uitdehaag,~B.M.J.; Vukusic,~S.; Waubant,~E.; Weinshenker,~B.G.; Reingold,~S.C.; Cohen,~J.A.
-Diagnosis of multiple sclerosis: 2017 revisions of the McDonald criteria.
-{\em Lancet Neurol.} {\bf 2018}, {\em 17}(2), 162--173.
-	\bibitem[Nasreddine(2005)]{Nasreddine2005}
-	Nasreddine,~Z.S.; Phillips,~N.A.; B\'{e}dirian,~V.; Charbonneau,~S.; Whitehead,~V.; Collin,~I.; Cummings,~J.L.; Chertkow,~H.
-The Montreal Cognitive Assessment, MoCA: A Brief Screening Tool For Mild Cognitive Impairment.
-{\em J.
-Am.
-Geriatr.
-Soc.} {\bf 2005}, {\em 53}(4), 695--699.
-	\bibitem[Federolf(2013)]{Federolf2013}
-	Federolf,~P.A.
-A Novel Approach to Solve the “Missing Marker Problem” in Marker-Based Motion Analysis That Exploits the Segment Coordination Patterns in Multi-Limb Motion Data.
-{\em PLoS ONE} {\bf 2013}, {\em 8}(10), 1--13.
-	\bibitem[Gloersen(2016)]{Gloersen2016}
-	Gl{\o}ersen,~{\O}; Federolf,~P. Predicting Missing Marker Trajectories in Human Motion Data Using Marker Intercorrelations. {\em PLoS ONE} {\bf 2016}, {\em 11}(3), 1--14.
-	\bibitem[Kormylo(1974)]{Kormylo1974}
-	Kormylo,~J.; Jain,~V. Two-pass recursive digital filter with zero phase shift. {\em IEEE T. Acoust. Speech} {\bf 1974}, {\em 22}(5), 384--387.
-	\bibitem[Racz(2021)]{Racz2021}
-	R\'{a}cz,~K.; Rita,~M.K. Marker displacement data filtering in gait analysis: A technical note. {\em Biomed. Signal Proces.} {\bf 2021}, {\em 70}:102974.
-	\bibitem[Pijnappels(2001)]{Pijnappels2001}
-	Pijnappels,~M.; Bobbert,~M.F.; Van Die\"{e}n,~J.H. Changes in walking pattern caused by the possibility of a tripping reaction. {\em Gait Posture} {\bf 2001}, {\em 14}(1), 11--18.
-	\bibitem[OConnor(2007)]{OConnor2007}
-	O'Connor,~C.M.; Thorpe,~S.K.; O'Malley,~M.J.; Vaughan,~C.L. Automatic detection of gait events using kinematic data. {\em Gait Posture} {\bf 2007}, {\em 25}(3), 469--474.
-	\bibitem[Carcreff(2018)]{Carcreff2018}
-	Carcreff,~L.; Gerber,~C.; Paraschiv-Ionescu,~A.; De~Coulon,~G,; Newman,~C.; Armand,~S.; Aminian,~K. What is the best configuration of wearable sensors
-	to measure spatiotemporal gait parameters in children with cerebral palsy? {\em Sensors} {\bf 2018}, {\em 18}(2):394.
-	\bibitem[YuKoltun(2016)]{YuKoltun2016}
-	Yu,~F.; Koltun,~V.
-Multi-Scale Context Aggregation by Dilated Convolutions.
-In Proceedings of the 4th Int.
-Conf.
-on Learning Representations (ICLR), San Juan, Puerto Rico, 2--4 May 2016, Conference Track Proceedings, 2016.
-	\bibitem[Bai(2018)]{Bai2018}
-	Bai,~S.; Kolter,~J.Z.; Koltun,~V. An Empirical Evaluation of Generic Convolutional and Recurrent Networks for Sequence Modeling. {\em arXiv:1803.01271} {\bf 2018}.
-	\bibitem[Remy(2020)]{Remy2020}
-	R\'{e}my,~P. Temporal Convolutional Networks for Keras. {\em GitHub repository} {\bf 2020}, {\em GitHub}, \url{https://github.com/philipperemy/keras-tcn}.
-	\bibitem[LeCun(1989)]{LeCun1989}
-	LeCun,~Y.; Boser,~B.; Denker,~J.S.; Henderson,~D.; Howard,~R.E.; Hubbard,~W.; Jackel,~L.D.
-Backpropagation Applied to Handwritten Zip Code Recognition.
-{\em Neural Comput.} {\bf 1989}, {\em 1}(4), 541--551.
-	\bibitem[Ioffe(2015)]{Ioffe2015}
-	Ioffe,~S.; Szegedy,~C. Batch Normalization: Accelerating Deep Network Training by
-	Reducing Internal Covariate Shift. {\em arXiv:1502.03167} {\bf 2015}.
-	\bibitem[Srivastava(2014)]{Srivastava2014}
-	Srivastava,~N.; Hinton,~G.; Krizhevsky,~A.; Sutskever,~I.; Salakhutdinov,~R. Dropout: a
-	simple way to prevent neural networks from overfitting. {\em J. Mach. Learn. Res.} {\bf 2014} {\em 15}, 1929--1958.
-	\bibitem[VanDenOord(2016)]{VanDenOord2016}
-	van~den~Oord,~A.; Dieleman,~S.; Zen,~H.; Simonyan,~K.; Vinyals,~O.; Graves,~A.; Kalchbrenner,~N.; Senior,~A.W.; Kavukcuoglu,~K.
-WaveNet: A generative	model for raw audio.
-{\em arXiv:1609.03499} {\bf 2016}.
-	\bibitem[OMalley(2019)]{OMalley2019}
-	O'Malley,~T.; Bursztein,~E.; Long,~J.; Chollet,~F.; Jin,~H.; Invernizzi,~L.; and others; KerasTuner. {\em GitHub repository} {\bf 2019}, {\em GitHub}, \url{https://github.com/keras-team/keras-tuner}.
-	\bibitem[Kingma(2014)]{Kingma2014}
-	Kingma,~D.P.; Ba,~J. Adam: A Method for Stochastic Optimization {\em arXiv:1412.6980v9} {\bf 2014}.
-	\bibitem[Schmidt(2021)]{Schmidt2021}
-	Schmidt,~R.M.; Schneider,~F.; Henning,~P.
-Descending through a crowded valley-benchmarking deep learning optimizers.
-In Proceedings of the 38th Int.
-Conf.
-on Machine Learning (ICML), {\em online}, 18--24 Jul.
-2021, pp.
-9367--9376.
-	\bibitem[Bergstra(2012)]{Bergstra2012}
-	Bergstra,~J.; Bengio,~Y. Random Search for Hyper-Parameter Optimization. {\em J. Mach. Learn. Res.} {\bf 2012}, {\em 13}(10), 281--305.
 \bibitem[Mishra(2019)]{Mishra2019}
@@
 McDonald,~J.H. \textit{Handbook of Biological Statistics}, 3rd ed.; Sparky House Publishing: Sparky House Publishing, USA, 2014; pp. 186--189.
-	\bibitem[OpenIntro(2019)]{OpenIntro2019}
-	Diez,~D.; \c{C}etinkaya-Rundel,~M.; Barr,~C.D. \textit{OpenIntro Statistics}, 4th ed.; 2019. \url{https://www.openintro.org/book/os/}
-\end{thebibliography}
-
-% If authors have biography, please use the format below
-%\section*{Short Biography of Authors}
-%\bio
-%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
-%{\textbf{Firstname Lastname} Biography of first author}
-%
-%\bio
-%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
-%{\textbf{Firstname Lastname} Biography of second author}
-
-% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
-% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
-% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p.
-328; \citeyear{ref-journal-3b}, p.475).
-This produces: Wong (1999, p.
-328; 2000, p.
-475)
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% for journal Sci
-%\reviewreports{\\
-%Reviewer 1 comments and authors’ response\\
-%Reviewer 2 comments and authors’ response\\
-%Reviewer 3 comments and authors’ response
-%}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\end{adjustwidth}
-\end{document}

### 2022-04-13 paper/MDPI_template/article.tex
Sync for home office

@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{A single paragraph of about 200 words maximum.
-For research articles, abstracts should give a pertinent overview of the work.
-We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: describe briefly the main methods or treatments applied; (3) Results: summarize the article's main findings; (4) Conclusions: indicate the main conclusions or interpretations.
-The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}
+\abstract{Many algorithms use 3D accelerometer and/or gyroscope data from IMU sensors to detect gait events (i.e., initial and final contact).
+However, these algorithms often require knowledge about sensor orientation and use empirically derived thresholds.
+As alignment cannot always be controlled for in ambulatory assessments, methods are needed that require little knowledge on sensor location and orientation, e.g., a convolutional neural network-based deep learning model.
+Therefore, 160 participants from healthy and neurologically diseased cohorts walked 5 meter distances at slow, preferred, and fast walking speed, while data were collected from IMUs on the left and right ankle and shank.
+Gait events were detected and stride parameters were extracted using a deep learning model and an optoelectronic motion capture (OMC) system for reference.
+Results showed a high detection rate for both initial and final contact detection across the IMUs (recall~$\ge 92\%$, precision~$\ge 97\%$).
+Time agreement was excellent, as witnessed median time error (0.005 s) and corresponding inter-quartile range (0.020~s).
+The extracted stride-specific parameters were in good agreement with parameters derived from the OMC system (maximum mean difference 0.003~s and corresponding maximum limits of agreement (-0.049, 0.051)~s for $95\%$ confidence level).
+Thus, the deep learning approach was considered a valid approach for detecting gait events and extracting stride-specific parameters with little knowledge on exact IMU location and orientation in conditions with and without walking pathologies due to neurological diseases.}
 
 % Keywords
-\keyword{keyword 1; keyword 2; keyword 3 (List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.)}
+\keyword{gait; inertial measurement units; deep learning}
 
@@
 Similarly, temporal gait parameters are different for stroke patients \cite{SchroederVon1995,Mohan2021} and patients with multiple sclerosis \cite{Griskevicius2016,Flachenecker2019} when compared to healthy controls.
-To objectively quantify gait deficits, stride-specific parameters such as stride time or stride length are often used \cite{Hannink2016}, where the beginning and end of a stride are determined from two successive initial contacts (ICs) of the same foot \cite{Perry2010,Whittle2012}.
-The IC is when the foot contacts the ground and together with the instant at which the foot leaves the ground (final contact, FC), each stride can be divided in a stance and swing phase \cite{Rueterbories2010,Bruening2014}.
-The events of IC and FC, also referred to as \emph{gait events}, are commonly determined using force or pressure measuring devices \cite{Bruening2014}, or passive, retro-reflective marker-based optoelectronic motion capture systems (henceforth referred to as the \emph{marker-based} system or method) \cite{Chiari2005,Topley2020}.
+To objectively quantify gait deficits, stride-specific parameters such as stride time or stride length are often used \cite{Hannink2016}.
+The beginning and end of a stride are determined from two successive initial contacts (ICs) of the same foot \cite{Perry2010,Whittle2012}.
+The IC is when the foot contacts the ground, and together with the instant at which the foot leaves the ground (final contact, FC), each stride can be divided in a stance and swing phase \cite{Rueterbories2010,Bruening2014}.
+The events of IC and FC, also referred to as \emph{gait events}, are commonly determined using force or pressure measuring devices \cite{Bruening2014}, or marker-based optoelectronic motion capture systems (henceforth referred to as the \emph{marker-based} system or method) \cite{Chiari2005,Topley2020}.
 These systems are relatively expensive, and restricted to usage in expertise laboratories \cite{Iosa2016,Jarchi2018}.
-As there is increasing evidence that gait measured in the lab does not reflect daily-life gait \cite{Hillel2019,Warmerdam2020,Atrsaei2021}, there is more and more interest in measurement systems that allow for continuous gait analysis in ambulatory settings.
+As there is increasing evidence that gait measured in the lab does not reflect daily-life gait \cite{Hillel2019,Warmerdam2020,Atrsaei2021}, there is increasingly more interest in measurement systems that allow for continuous gait analysis in ambulatory settings.
 Therefore, the use of inertial measurement units (IMUs) is especially attractive, as these can be used to measure gait in ecologically valid environments, such as the home environment, thereby painting a more complete picture of health status \cite{DelDin2016,Shah2020} and providing clinical information that is complementary to standardized lab-based assessments \cite{Warmerdam2020,Fasano2020,Atrsaei2021,Corra2021}.
@@
 
-In this study, we further these works by validating this deep learning approach for detecting gait events in a heterogeneous cohort of healthy and neurologically diseased adults considering a single IMU setup, worn on the lower leg.
+The aim of this study is to extend these works by validating this deep learning approach for detecting gait events in a heterogeneous cohort of healthy and neurologically diseased adults considering a single IMU setup, worn on the lower leg.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The study \cite{Warmerdam2021} was approved by the ethical committee of the medical faculty at the UKSH (no: D438/18).
-In total, data from 160 participants were included for the current analysis, including data from young adults (YA; age: 18 - 60 years), older adults (OA; age: $>$60 years), people with Parkinson's Disease (PD; according to the UK Brain Bank criteria \cite{Gibb1988}), people with a recent ($<$4 weeks) symptomatic stroke (stroke), people with multiple sclerosis (MS; according to the McDonalds criteria \cite{Thompson2018}), people with chronic low back pain (cLBP), and people with other diagnoses that were assumed not to affect mobility (Table \ref{tab:demographics_data}).
+In total, data from 160 participants were included for the current analysis, including data from young adults (YA; age: 18 - 60 years), older adults (OA; age: $>$60 years), people with Parkinson's Disease (PD; according to the UK Brain Bank criteria \cite{Gibb1988}), people with a recent ($<$4 weeks) symptomatic stroke (stroke), people with multiple sclerosis (MS; according to the McDonalds criteria \cite{Thompson2018}), people with chronic low back pain (cLBP), and people with other diagnoses that affected mobility (Table \ref{tab:demographics_data}).
 Inclusion criteria were an age of 18 years or older, and the ability to walk independently without a walking aid.
@@
 		\textbf{Group}	& \textbf{Gender}	& \textbf{Number of}	& \textbf{Age}	& \textbf{Height}	& \textbf{Weight}\\
-		 & & \textbf{subjects} & years	& cm	& kg\\
+		 & & \textbf{participants} & years	& cm	& kg\\
 		\midrule
@@
 
-Participants performed three walking trials consisting of walking 5 meter at either (1) preferred speed ("\emph{Please walk at your normal walking speed.}"), (2) slow speed ("\emph{Please walk half of your normal walking speed.}"), or (3) fast speed ("\emph{Please walk as fast as possible, without running or falling.}").
+Participants performed three walking trials consisting of walking 5 meter at either (1) preferred speed ("\emph{Please walk at your normal walking speed.}"), (2) slow speed ("\emph{Please walk at half of your normal walking speed.}"), or (3) fast speed ("\emph{Please walk as fast as possible, without running or falling.}").
 The 5 meter distance was marked with two cones on both ends, and participants were asked to start walking approximately two steps before the cones on one end, and stop walking approximately two steps after passing the cones on the other end.
@@
 \subsubsection{Marker Data \label{subsubsec:Marker_Data}}
-The reflective marker data were first used to determine start and end of each trial.
-The start of the trial was defined as the time for which the first toe marker (left or right) crossed the \emph{virtual} starting line.
-The end was defined as the time for which the last heel marker crossed the end line.
-For both marker and IMU systems, data were then cropped from start to the end of the trial.
-
-Any remaining gaps in the marker data were filled by interpolation making use of inter-correlations between markers \cite{Federolf2013,Gloersen2016}.
+First, data from both marker and IMU systems were cropped so that only data from within the 5 meter distance was considered.
+Any gaps in the marker data were then filled by interpolation making use of inter-correlations between markers \cite{Federolf2013,Gloersen2016}.
 The data were then low-pass filtered using a double pass 6th order Butterworth filter with a cut-off frequency of 20 Hz \cite{Kormylo1974,Racz2021}.
 The filtered data were differentiated to get velocity signals, and timings of ICs and FCs were determined from local maxima and minima in the heel and toe vertical velocity signals \cite{Pijnappels2001,OConnor2007}.
-Like in \cite{Carcreff2018,Romijnders2021}, all identified ICs and FCs were manually checked, and corrected if necessary, using Qualisys Track Manager 2018.1 software (Qualisys AB, Göteborg, Sweden).
+Like in \cite{Carcreff2018,Romijnders2021}, all identified ICs and FCs were manually checked using Qualisys Track Manager 2018.1 software (Qualisys AB, Göteborg, Sweden), and corrected if necessary.
 The resulting annotated ICs and FCs were considered the \emph{true} events (also \emph{labels} or \emph{targets}), and were used as reference timings to derive stride-specific gait parameters.
@@
 Participants were randomly assigned to one of the sets, stratified by both group (i.e., diagnosis) and gender (Table~\ref{tab:demographics_data}).
+The training and validation set were used to train an optimal deep learning model, whereas the test set was used to evaluate the model performance on \emph{unseen} data (that is, the test set data were not used to train or find the model architecture).
+Any results on the model performance therefore, were only based on the test set (Section~\ref{sec:Results}).
 
@@
 \subsubsection{Overall detection performance \label{subsubsec:overall_detection_performance}}
-The overall detection performance quantified how many of the annotated evens were detected by the model (true positives, TP), how many of the annotated events were not detected (false negatives, FN), and how many event that were detected, were actually not annotated (false positives, FP).
+The overall detection performance quantified how many of the annotated events were detected by the model (true positives, TP), how many of the annotated events were not detected (false negatives, FN), and how many event that were detected, were actually not annotated (false positives, FP).
 An annotated event was considered to be detected if any detected event was within 0.075 s.
-A detected event were defined as peaks in the predicted likelihoods with a minimum height of 0.4, i.e.
+A detected event was defined as peaks in the predicted likelihoods with a minimum height of 0.4, i.e.
 $40\%$ likely that it corresponded to an event.
@@
 \begin{equation}
-	\textrm{recall} = \frac{\textrm{TP}}{\textrm{TP} + \textrm{FN}} \nonumber
+	\textrm{recall} = \frac{\textrm{TP}}{\textrm{TP} + \textrm{FN}} 
 	\label{eqn:recall}
@@
 \begin{equation}
-	\textrm{precision} = \frac{\textrm{TP}}{\textrm{TP} + \textrm{FP}} \nonumber
+	\textrm{precision} = \frac{\textrm{TP}}{\textrm{TP} + \textrm{FP}} 
 	\label{eqn:precision}
@@
 \begin{equation}
-	\textrm{F$_{1}$ score} = 2 \cdot \frac{\textrm{recall} \cdot \textrm{precision}}{\textrm{recall} + \textrm{precision}}  \nonumber
+	\textrm{F$_{1}$ score} = 2 \cdot \frac{\textrm{recall} \times \textrm{precision}}{\textrm{recall} + \textrm{precision}}  
 	\label{eqn:f1_score}
@@
 \section{Results}
+\label{sec:Results}
 
@@
 Time agreement between the annotated and detected events was quantified for the TPs for each of the tracked points (Figure~\ref{fig:time_error_box_plots}).
-The median time error for each of the tracked points, and for both ICs and FCs was close to zero (Table~\ref{tab:time_errors}), and the largest deviation was -0.005 s, corresponding to one sample period.
+The median time error for each of the tracked points, and for both ICs and FCs was close to zero (Table~\ref{tab:time_errors}), and the largest deviation was -0.005 s, corresponding to one sample period (at the sampling frequency of 200 Hz).
 The IQR was at most 0.020 s, corresponding to 4 sample periods.
@@
 		\textbf{Tracked point} & \textbf{Parameters} & \textbf{Mean difference} & \textbf{Limits of Agreement}\\
-		 & & ms & (ms, ms)\\
+		 & & s & s\\
 		\midrule
@@
 \begin{figure}[H]
+	\begin{adjustwidth}{-\extralength}{0cm}
 		\centering
-	\includegraphics[width=13.5cm]{fig/bland_altman_plots_stride_params.png}
+		\includegraphics[width=16.5cm]{fig/bland_altman_plots_stride_params.png}
+	\end{adjustwidth}
 	\caption{The agreement of extracted gait parameters between the sensor-based and marker-based methods.\label{fig:gait_parameters_bland_altman_plots}}
@@
 The current study aimed to validate a deep learning approach for detecting gait events from a single IMU worn on the lower leg.
-Data from a left and right ankle- and shank-worn IMU were used for training a deep learning model to detect gait events from walking trials performed by healthy younger and older adults, participants diagnosed with Parkinson's Disease, multiple sclerosis, or chronic low back pain, participants who had a recent symptomatic stroke, and participants diagnosed with other neurological diseases.
+Data from a left and right ankle- and shank-worn IMU were used for training a deep learning model to detect gait events from walking trials performed by healthy YA, OA, participants diagnosed with PD, MS, or cLBP, participants who had a recent symptomatic stroke, and participants diagnosed with other neurological diseases.
 Participants walked a 5 meter distance at three different self-selected walking speeds.
-The gait event timings that were predicted by the deep learning model were compared to a common reference method, i.e., optoelectronc motion capture, and clinically relevant stride-specific gait parameters were extracted.
+The gait event timings that were predicted by the deep learning model were compared to a common reference method, i.e., optoelectronic motion capture, and clinically relevant stride-specific gait parameters were extracted.
 
@@
 The main limitations of the current study were that only walking trials involving straight-line walking were considered, and the walking distance was relatively short.
-The observed gait patterns from these walking trials may therefore not fully representative of gait patterns observed in daily-life \cite{Hillel2019,Warmerdam2020,Atrsaei2021}.
+The observed gait patterns from these walking trials may therefore not be fully representative of gait patterns observed in daily-life \cite{Hillel2019,Warmerdam2020,Atrsaei2021}.
 However, as the deep learning-based approach does not rely on fixed thresholds or assumptions regarding to which sensor axis is used, it is theoretically transferable and scalable to other conditions if input data and corresponding labels can be provided.
@@
 \section{Conclusions}
-In this study we have validated a deep learning-based approach to detect gait events and subsequently extract clinically relevant stride parameters from a single inertial measurement unit worn either laterally above the ankle joint or proximally below the knee joint.
+In this study we have validated a deep learning-based approach to detect gait events and subsequently extract clinically relevant stride parameters from a single inertial measurement unit worn either laterally above the ankle joint or proximal below the knee joint.
 Performance analysis showed an excellent detection rate, and low time errors in both event detection and stride parameter calculation for different walking speeds and across both healthy and neurological cohorts.
@@
 Additionally, we are preparing the open-source release of all data from the healthy younger and older adults.
-Data from ptient groups }
+Data from patient groups can be shared upon reasonable request.
+The full algorithm pipeline is going to be made publicly available online at \url{https://github.com/rmndrs89/my-gait-events-tcn}.}
 
 \acknowledgments{The authors sincerely thank all people that were involved in the data collection, from study participants to students who aided and assisted during measurements and subsequent marker labeling.
-The authors appreciate the off- and on-topic discussions with Julius Welzel, and his positive contributions to the organization of the research data.
-The authors give a thumbs up to Johannes Hoffmann for his tips and tricks regarding the \LaTeX typesetting.}
+The authors thank Julius Welzel for his contributions to the organization of the research data.
+The authors thank Johannes Hoffmann for his tips regarding \LaTeX\ typesetting.}
 

### 2022-04-21 paper/MDPI_template/article.tex
Cleaned working directory. Setup __obsolete__ directory.

@@
 % Authors, for the paper (add full first names)
-\Author{Robbin Romijnders$^{1}$*\orcidA{}, Elke Warmerdam$^{2}$, Clint Hansen$^{1}$*, Gerhard Schmidt$^{3}$ and Walter Maetzler$^{1}$}
+\Author{Robbin Romijnders$^{1}$*\orcidA{}, Elke Warmerdam$^{2}$, Clint Hansen$^{1}$, Gerhard Schmidt$^{3}$ and Walter Maetzler$^{1}$}
 
@@
 $^{1}$ \quad Department of Neurology, Kiel University, 24105 Kiel, Germany; r.romijnders@neurologie.uni-kiel.de (R.R.), c.hansen@neurologie.uni-kiel.de (C.H.), w.maetzler@neurologie.uni-kiel.de (W.M.)\\
-$^{2}$ \quad xxxxx, xxxxx, xxxxx Homburg, Germany; elke.warmerdam@uni-saarland.de (E.W.)\\
+$^{2}$ \quad Innovative Implant Development (Fracture Healing), Division of Surgery, Saarland University, 66421 Homburg, Germany; elke.warmerdam@uni-saarland.de (E.W.)\\
 $^{3}$ \quad Institute of Electrical Engineering and Information Technology, Faculty of Engineering, Kiel University, 24143 Kiel, Germany; gus@tf.uni-kiel.de (G.S.)}
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{Many algorithms use 3D accelerometer and/or gyroscope data from IMU sensors to detect gait events (i.e., initial and final contact).
+\abstract{Many algorithms use 3D accelerometer and/or gyroscope data from inertial measurement unit (IMU) sensors to detect gait events (i.e., initial and final foot contact).
 However, these algorithms often require knowledge about sensor orientation and use empirically derived thresholds.
-As alignment cannot always be controlled for in ambulatory assessments, methods are needed that require little knowledge on sensor location and orientation, e.g., a convolutional neural network-based deep learning model.
+As sensor-to-segment alignment cannot always be controlled for in ambulatory assessments, methods are needed that require little knowledge on sensor location and orientation, e.g., a convolutional neural network-based deep learning model.
 Therefore, 160 participants from healthy and neurologically diseased cohorts walked 5 meter distances at slow, preferred, and fast walking speed, while data were collected from IMUs on the left and right ankle and shank.
 Gait events were detected and stride parameters were extracted using a deep learning model and an optoelectronic motion capture (OMC) system for reference.
-Results showed a high detection rate for both initial and final contact detection across the IMUs (recall~$\ge 92\%$, precision~$\ge 97\%$).
-Time agreement was excellent, as witnessed median time error (0.005 s) and corresponding inter-quartile range (0.020~s).
-The extracted stride-specific parameters were in good agreement with parameters derived from the OMC system (maximum mean difference 0.003~s and corresponding maximum limits of agreement (-0.049, 0.051)~s for $95\%$ confidence level).
-Thus, the deep learning approach was considered a valid approach for detecting gait events and extracting stride-specific parameters with little knowledge on exact IMU location and orientation in conditions with and without walking pathologies due to neurological diseases.}
+Results showed a high detection rate for both initial and final contacts across sensor locations (recall $\ge 92\%$, precision $\ge 97\%$).
+Time agreement was excellent as witnessed from the median time error (0.005 s) and corresponding inter-quartile range (0.020 s).
+The extracted stride-specific parameters were in good agreement with parameters derived from the OMC system (maximum mean difference 0.003 s, and corresponding maximum limits of agreement (-0.049 s, 0.051 s) for a $95\%$ confidence level.) Thus, the deep learning approach was considered a valid approach for detecting gait events and extracting stride-specific parameters with little knowledge on exact IMU location and orientation in conditions with and without walking pathologies due to neurological diseases.}
 
 % Keywords
-\keyword{gait; inertial measurement units; deep learning}
+\keyword{gait; gait events; interial measurement unit; deep learning}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction \label{sec:Introduction}}
+\section{Introduction}
 Gait deficits are common in older adults and possibly reflect the presence of an underlying neurodegenerative disease \cite{Snijders2007,Hodgins2008}.
-For example, conversion to Parkinson's Disease \cite{DelDin2019} or from mild cognitive impairment to Alzheimer's Disease \cite{Koenig2017,Bertoli2018} are linked with changes in spatiotemporal gait parameters.
+For example, conversion to Parkinson's Disease \cite{DelDin2019} or conversion from mild cognitive impairment to Alzheimer's Disease \cite{Koenig2017,Bertoli2018} are linked with changes in spatiotemporal gait parameters.
 Similarly, temporal gait parameters are different for stroke patients \cite{SchroederVon1995,Mohan2021} and patients with multiple sclerosis \cite{Griskevicius2016,Flachenecker2019} when compared to healthy controls.
@@
 The beginning and end of a stride are determined from two successive initial contacts (ICs) of the same foot \cite{Perry2010,Whittle2012}.
-The IC is when the foot contacts the ground, and together with the instant at which the foot leaves the ground (final contact, FC), each stride can be divided in a stance and swing phase \cite{Rueterbories2010,Bruening2014}.
+The IC is when the foot contacts the ground and together with the instant at which the foot leaves the ground (final contact, FC), each stride can be divided in a stance and swing phase \cite{Rueterbories2010,Bruening2014}.
 The events of IC and FC, also referred to as \emph{gait events}, are commonly determined using force or pressure measuring devices \cite{Bruening2014}, or marker-based optoelectronic motion capture systems (henceforth referred to as the \emph{marker-based} system or method) \cite{Chiari2005,Topley2020}.
@@
 A recent study has evaluated a cross-section of these algorithms for different sensor locations on the lower leg and foot \cite{Niswander2021}.
-The algorithms were categorized according to which signals were analyzed, for example the angular velocity about the medio-lateral axis, or the accelerations along vertical and antero-posterior axis.
+The algorithms were categorized according to which signals were analyzed, for example the angular velocity about the medio-lateral axis, or the accelerations along vertical and antero-posterior axes.
 This means the sensor readings need to be linked with the anatomical axes, that is, one needs to know which sensor axis aligns with for example the medio-lateral axis.
 In most approaches, it is simply assumed that due to sensor attachment the sensor axis aligns roughly with the anatomical axis of interest (\cite{Salarian2004,Sabatini2005,Jasiewicz2006,Catalfamo2010,Trojaniello2014,Maqbool2016,Romijnders2021}) or an additional calibration procedure (e.g., \cite{Ferraris1995}) is required (\cite{Greene2010,Niswander2021}).
-In ambulatory assessments however, study participants often attach the sensor themselves, and therefore the sensor location and alignment cannot be controlled for.
-Furthermore, it is unlikely that each time the sensor is (re-)attached study participants, especially those with gait deficits, perform a calibration procedure that usually consists of holding a pre-defined pose and performing some known movement sequences (TODO: reference?!
-Kong?
-Seel?).
+In ambulatory assessments however, study participants often attach the sensor themselves, for example after showering, and therefore the sensor location and alignment cannot be controlled for.
+Furthermore, it is unlikely that each time the sensor is (re-)attached study participants, especially those with gait deficits, perform a calibration procedure that usually consists of holding a pre-defined pose and performing some known movement sequences \cite{Leineweber2019,Pacher2020}.
 
 Taken together, this drives the need for an approach that is invariant to sensor orientation, and is applicable across a variety of pathological gait patterns.
-As pointed out by \cite{Hannink2016}, in the field of image analysis similar requirements have been successfully addressed by algorithms that share a common underlying methodology referred to as deep learning \cite{LeCun2015,TerHaarRomeny2019}.
+In the field of image analysis similar requirements have been successfully addressed by algorithms that share a common underlying methodology referred to as deep learning \cite{LeCun2015,Hannink2016,TerHaarRomeny2019}.
 Recent applications of deep learning algorithms have already shown improved performance in detecting gait events from marker-based motion capture when compared to conventional, often heuristics-based, algorithms \cite{Kidzinski2019,Lempereur2020,Filtjens2020}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Materials and Methods \label{sec:Materials_and_Methods}}
-\subsection{Data Collection \label{subsec:Data_Collection}}
+\section{Materials and Methods}
+\subsection{Data Collection}
 Gait analyses were performed in the Universit\"{a}tsklinikum Schleswig-Holstein (UKSH) campus Kiel, Germany.
 The study \cite{Warmerdam2021} was approved by the ethical committee of the medical faculty at the UKSH (no: D438/18).
-In total, data from 160 participants were included for the current analysis, including data from young adults (YA; age: 18 - 60 years), older adults (OA; age: $>$60 years), people with Parkinson's Disease (PD; according to the UK Brain Bank criteria \cite{Gibb1988}), people with a recent ($<$4 weeks) symptomatic stroke (stroke), people with multiple sclerosis (MS; according to the McDonalds criteria \cite{Thompson2018}), people with chronic low back pain (cLBP), and people with other diagnoses that affected mobility (Table \ref{tab:demographics_data}).
+In total, data from 160 participants were included for the current analysis, including data from young adults (YA; age: 18 - 60 years), older adults (OA; age: $>$60 years), people with Parkinson's Disease (PD; according to the UK Brain Bank criteria \cite{Gibb1988}), people with a recent ($<$4 weeks) symptomatic stroke (stroke), people with multiple sclerosis (MS; according to the McDonalds criteria \cite{Thompson2018}), people with chronic low back pain (cLBP), and people with diagnoses not fitting in any before-mentioned groups or disorders with no explicit diagnosis (other) (Table \ref{tab:demographics_data}).
 Inclusion criteria were an age of 18 years or older, and the ability to walk independently without a walking aid.
@@
 	\caption{Schematic depiction$^{1}$ of the current study.
-Study participants wore IMUs on the ankle and shanks, and reflective markers were adhered on the heel and toe of usual footwear (shown on the left).
+Study participants wore IMUs on the ankle and shanks, and reflective markers were adhered on the heel and toe of usual footwear (illustrated on the left).
 Marker data were used to obtain reference values for the timings of initial and final contacts (top), where accelerometer and gyroscope data from each tracked point were inputted to a neural network that predicted timings of the same initial and final contacts (bottom).
@@
 IMU data were recorded at the same sampling frequency, and both systems were synchronized using a TTL signal \cite{Warmerdam2021}.
-For some recordings, the sampling frequency of the IMUs was mistakenly set at 100 Hz, and therefore data from these trials were upsampled before further analysis.
 
-\subsection{Data Pre-processing \label{subsec:Data_Pre-processing}}
-\subsubsection{Marker Data \label{subsubsec:Marker_Data}}
-First, data from both marker and IMU systems were cropped so that only data from within the 5 meter distance was considered.
-Any gaps in the marker data were then filled by interpolation making use of inter-correlations between markers \cite{Federolf2013,Gloersen2016}.
-The data were then low-pass filtered using a double pass 6th order Butterworth filter with a cut-off frequency of 20 Hz \cite{Kormylo1974,Racz2021}.
+\subsection{Data Pre-processing \label{subsec:data_preprocessing}}
+\subsubsection{Marker Data}
+First, data from both marker and IMU systems were cropped so that only data from within the 5 meter distance were considered.
+Any gaps in the marker data were filled by interpolation making use of inter-correlations between markers \cite{Federolf2013,Gloersen2016}.
+The data were then low-pass filtered using a 6th order Butterworth filter with a cut-off frequency of 20 Hz \cite{Racz2021}.
+The filter was applied twice to the input data \cite{Kormylo1974}.
+After filtering in forward direction, the filtered sequence was reversed and run back through the filter \cite{Salarian2004}.
 The filtered data were differentiated to get velocity signals, and timings of ICs and FCs were determined from local maxima and minima in the heel and toe vertical velocity signals \cite{Pijnappels2001,OConnor2007}.
-Like in \cite{Carcreff2018,Romijnders2021}, all identified ICs and FCs were manually checked using Qualisys Track Manager 2018.1 software (Qualisys AB, Göteborg, Sweden), and corrected if necessary.
+All identified ICs and FCs were manually checked using Qualisys Track Manager 2018.1 software (Qualisys AB, Göteborg, Sweden), and corrected if necessary \cite{Carcreff2018,Romijnders2021}.
 The resulting annotated ICs and FCs were considered the \emph{true} events (also \emph{labels} or \emph{targets}), and were used as reference timings to derive stride-specific gait parameters.
 
-\subsubsection{IMU Data \label{subsubsec:IMU_Data}}
+\subsubsection{IMU Data}
 The idea behind the deep learning approach was that a \emph{model} was trained to predict the likelihood of an IC and FC, given accelerometer and gyroscope data from a single IMU.
-The data from a single sensor channel, e.g., the acceleration in forward direction, or the angular velocity about the vertical direction, was denoted by $\mathbf{x}_{d} = \begin{bmatrix}
+The data from a single sensor channel, e.g., the acceleration in forward direction, was denoted by $\mathbf{x}_{d} = \begin{bmatrix}
 	x_{d}[1] & x_{d}[2] & \cdots & x_{d}[N]
 \end{bmatrix}^{\mathrm{T}}$, with $d$ referring to the $d$th sensor channel (i.e., $d = 1, \cdots, D$) and $n$ referring to the $n$th sample or time step (i.e., $n = 1, \cdots, N$).
-Data from all $D$ sensor channels together was then denoted by:
+Similarly, the data from all $D$ sensor channels at a given time instant $n$, was denoted by $\mathbf{x}[n] = \begin{bmatrix}
+x_{1}[n] & x_{2}[n] & \cdots & x_{D}[n]
+\end{bmatrix}^{\mathrm{T}}$. Data from all $D$ channels, and for all $N$ time steps, was then denoted by:
 \begin{equation}
@@
 		\vdots & \vdots & \cdots & \vdots\\
-		x_{1}[N] & x_{2}[1] & & x_{D}[N]\end{bmatrix}, \quad \mathbf{X} \in \mathbb{R}^{N \times D}
+		x_{1}[N] & x_{2}[N] & & x_{D}[N]\end{bmatrix}, \quad \mathbf{X} \in \mathbb{R}^{N \times D}
 	\label{eqn:train_data_single_instance}
@@
 	\end{bmatrix}, \quad y_{\mathrm{IC}/\mathrm{FC}}[n] \in [0, 1]
-	\label{eqn:train_labels_single_instance}
+	\label{eqn:train_labels_single_instace}
 \end{equation}
 
-The model was then iteratively trained to learn a mapping $h_{\mathbf{\Theta}}(\mathbf{X}): \mathbf{X} \rightarrow \mathbf{y}$, where $h_{\mathbf{\Theta}}$ was also referred to as the \emph{hypothesis} which was parameterized by the weights and biases, collectively denoted by $\mathbf{\Theta}$.
+The model was iteratively trained to learn a mapping $h_{\mathbf{\Theta}}(\mathbf{X}): \mathbf{X} \rightarrow \mathbf{y}$, where $h_{\mathbf{\Theta}}$ was also referred to as the \emph{hypothesis} parameterized by the weights, collectively denoted by $\mathbf{\Theta}$.
 
-All participant data were split in three independent data sets, namely a training set, a validation set, and a test set.
+All participant data data were split in three independent data sets, namely a training set, a validation set, and a test set.
 Each set contained data from approximately one-third of the participants.
 Participants were randomly assigned to one of the sets, stratified by both group (i.e., diagnosis) and gender (Table~\ref{tab:demographics_data}).
-The training and validation set were used to train an optimal deep learning model, whereas the test set was used to evaluate the model performance on \emph{unseen} data (that is, the test set data were not used to train or find the model architecture).
-Any results on the model performance therefore, were only based on the test set (Section~\ref{sec:Results}).
+The training and validation set were used to train an optimal deep learning model.
+Test set data were not used for model training or hyperparameter tuning.
+The results on the model's performance were only based on the test set, and therefore reflect how good the model generalizes to new, \emph{unseen} data.
 
@@
 
-\subsection{Model \label{subsec:Model}}
-\subsubsection{Model Architecture \label{subsubsec:Model_Architecture}}
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=13.5cm]{fig/methods_tcn_arch.pdf}
-	\caption{The generic model architecture of the deep learning model to predict initial contacts (ICs) and final contacts (FCs).
-The inputs are the accelerometer and gyroscope data from a single inertial measurement unit, and are fed to a temporal convolutional network (TCN) (left).
-The TCN consisted of repeating residual blocks (ResBlock) with exponentially increasing dilation factor (middle).
-Each ResBlock was built from two sequences of a convolutional layer (Conv), batch normalization layer (BatchNorm), a rectified linear unit activation layer (ReLU), and a dropout layer (DropOut) (right).
-\label{fig:methods_tcn_arch}}
-\end{figure} 
+\subsection{Model}
+\subsubsection{Model Architecture}
 The generic architecture for the deep learning model was based on a temporal convolutional network (TCN) \cite{Bai2018,Remy2020,Filtjens2020}.
 The TCN consisted of a sequence of residual blocks with exponentially increasing dilation factor \cite{YuKoltun2016,Bai2018}.
-Each residual block was built from two sequences of a dilated convolutional layer \cite{YuKoltun2016}, a batch normalization layer \cite{Ioffe2015}, a rectified linear unit (ReLU) activation layer, and dropout layer \cite{Srivastava2014} (Figure~\ref{fig:methods_tcn_arch}).
-The model was built in Python \cite{VanRossum2009} using the high-level TensorFlow API Keras \cite{Chollet2015,Remy2020}.
+Each residual block was built from two sequences of a dilated convolutional layer \cite{YuKoltun2016}, a batch normalization layer \cite{Ioffe2015}, a rectified linear unit (ReLU) activation layer, and a dropout layer \cite{Srivastava2014} (Figure).
+The model was built in Python \cite{VanRossum2009} using the high-level TensorFlow API Keras \cite{Remy2020,Chollet2015}.
 
@@
 \begin{equation}
-	\hat{y}_{i}[n] = f(\cdots,\mathbf{X}[n-1],\mathbf{X}[n],\mathbf{X}[n+1],\cdots), \quad i \in \left\{ \mathrm{IC}, \mathrm{FC}\right\}
-	\label{eqn:predictions}
+	\hat{y}_{i}[n] = f\left(\cdots, \mathbf{x}[n-1], \mathbf{x}[n], \mathbf{x}[n+1], \cdots \right), \quad i \in \left\{ \mathrm{IC}, \mathrm{FC}\right\}
 \end{equation}
 The number of samples that the predictions at time $n$ "sees", was referred to as the \emph{receptive field} \cite{Lea2017} and was a function of the kernel size and the dilation factors \cite{Remy2020}.
-Dilation factors were always given as a sequence of increasing powers of 2 \cite{VanDenOord2016,YuKoltun2016,Bai2018}.
+Dilation factors were always given as a sequence of increasing power of 2 \cite{YuKoltun2016,Bai2018,VanDenOord2016}.
 
 The outputs of the TCN block were fed to two separate fully-connected (FCN, or dense) layers, that both were followed by a sigmoid activation layer.
-Outputs were then predicted separately for ICs and FCs.
-The mean squared error (MSE) was used as loss function, and a gradient descent-based optimization algorithm with adaptive moment (Adam) optimizer was used to iteratively learn the weights \cite{Kingma2014,Schmidt2021}.
+Outputs were then predicted separately for ICs and FCs \cite{Gadaleta2019,Filtjens2020}.
+The mean squared error (MSE) was used as a loss function, and a gradient descent-based optimization algorithm with adaptive moment (Adam) optimizer was used to iteratively learn the weights \cite{Kingma2014,Schmidt2021}.
 
@@
 In order to find the best model architecture, hyperparameter tuning was perfomed using KerasTuner \cite{OMalley2019}.
-Here, the number of filters, the kernel size, and the maximum dilation factor (Table \ref{tab:hyperparameter_optimization}) were optimized using a random search strategy \cite{Bergstra2012}.
+Here, the number of filters, the kernel size, and the maximum dilation factor (Table \ref{tab:hyperparameter_optimization}) were optimized for using a random search strategy \cite{Bergstra2012}.
 
@@
 		\midrule
-		Number of filters	& 8, 16, 32, 64, 128\\
-		Kernel size			& 3, 5, 7\\
-		Dilations 			& [1, 2], [1, 2, 4], [1, 2, 4, 8]\\
+		Number of filters	& 8, {\bf 16}, 32, 64, 128\\
+		Kernel size			& 3, {\bf 5}, 7\\
+		Dilations 			& [1, 2], {\bf [1, 2, 4]}, [1, 2, 4, 8]\\
 		\bottomrule
 	\end{tabularx}
+	\noindent{\footnotesize{In bold typesetting the hyperparameter values that were selected for the trained model to make predictions on the test set.}}
 \end{table}
@@
 The model architecture that resulted from the hyperparameter optimization was then trained on the combined set of training and validation data.
-The trained model was used to predict the likelihoods of ICs and FCs events on the hold-out test set.
+The trained model was used to predict the likelihoods of ICs and FCs on the test set data.
 
@@
 The predictions of the model on the test set data were compared with the labels from the test set.
-The model performance was evaluated for (1) overall detection performance, (2) time agreement between the predicted events and the (marker-based) annotated events, (3) agreement between subsequently derived gait parameters.
+The model performance was evaluated for (1) overall detection performance, (2) time agreement between the predicted events and the (marker-based) annotated events, (3) agreement between subsequently derived stride-specific gait parameters.
 \subsubsection{Overall detection performance \label{subsubsec:overall_detection_performance}}
-The overall detection performance quantified how many of the annotated events were detected by the model (true positives, TP), how many of the annotated events were not detected (false negatives, FN), and how many event that were detected, were actually not annotated (false positives, FP).
-An annotated event was considered to be detected if any detected event was within 0.075 s.
-A detected event was defined as peaks in the predicted likelihoods with a minimum height of 0.4, i.e.
-$40\%$ likely that it corresponded to an event.
-
+The overall detection performance quantified how many of the annotated evens were detected by the model (true positives, TP), how many of the annotated events were not detected (false negatives, FN), and how many events that were detected, were actually not annotated (false positives, FP).
 From these metrics, the recall (or sensitivity), precision and F$_{1}$ score were calculated as:
@@
 \begin{equation}
-	\textrm{F$_{1}$ score} = 2 \cdot \frac{\textrm{recall} \times \textrm{precision}}{\textrm{recall} + \textrm{precision}}  
+	\textrm{F$_{1}$ score} = 2 \cdot \frac{\textrm{recall} \cdot \textrm{precision}}{\textrm{recall} + \textrm{precision}} 
 	\label{eqn:f1_score}
@@
 
-\subsubsection{Time Agreement \label{subsubsec:Methods_Time_Agreement}}
-For all correctly detected gait events (TP, Section \ref{subsubsec:overall_detection_performance}), the time agreement between the annotated and detect gait event was given by the time error:
+\subsubsection{Time Error}
+For all correctly detected gait events (TP, Section \ref{subsubsec:overall_detection_performance}), the time error between the annotated and detect gait event was defined as:
 \begin{equation}
@@
 For those trials for which all gait events were detected, and no false positives were detected, the stride time, stance time and swing were calculated.
-Stride time was the time between two successive ICs of the same foot.
+Stride was the time between two successive ICs of the same foot.
 Stance time was the time between a FC and the preceding IC of the same foot.
@@
 \section{Results}
-\label{sec:Results}
 
-\subsection{Overall Detection Performance}
+\subsection{Overall detection performance}
 The performance of detecting ICs and FCs was objectively quantified by the number of TPs, the number of FNs, and the number of FPs.
-From these, recall, precision and F$_{1}$ score were calculated (Table \ref{tab:overall_detection_performance}).
+From these numbers, recall, precision and F$_{1}$ score were calculated (Table \ref{tab:overall_detection_performance}).
 \begin{table}[H]
@@
 
-For both ICs and FCs, recall is high for each of the tracked points (i.e., $\ge 92\%$), and so is precision (i.e., $\ge 97\%$).
-Differences between the tracked points are small, i.e.
+For both ICs and FCs, recall is high for each of the sensor locations (i.e., $\ge 92\%$), and so is precision (i.e., $\ge 97\%$).
+Differences between the sensor locations are small, i.e.
 the minimum recall is $92\%$ and the maximum recall is $97\%$, and the minimum precision is $97\%$ and the maximum precision is $99\%$.
@@
 	\centering
-	\includegraphics[width=13.5 cm]{fig/box_plots_tracked_points_with_outliers.png}
+	\includegraphics[width=13.5 cm]{fig/box_plots_tracked_points_with_outliers}
 	\caption{Time errors for initial (left) and final (right) contacts detection, for each of the different tracked points.\label{fig:time_error_box_plots}}
@@
 
-Time agreement between the annotated and detected events was quantified for the TPs for each of the tracked points (Figure~\ref{fig:time_error_box_plots}).
-The median time error for each of the tracked points, and for both ICs and FCs was close to zero (Table~\ref{tab:time_errors}), and the largest deviation was -0.005 s, corresponding to one sample period (at the sampling frequency of 200 Hz).
+Time agreement between the annotated and detected events was quantified for the TPs for each of the sensor locations (Figure~\ref{fig:time_error_box_plots}).
+The median time error for each of the sensor locations, and for both ICs and FCs was close to zero (Table~\ref{tab:time_errors}), and the largest median time error was -0.005 s, corresponding to one sample period (at a sampling frequency of 200 Hz).
 The IQR was at most 0.020 s, corresponding to 4 sample periods.
 \begin{table}[H] 
-	\caption{Time errors for the correctly detected gait events. \label{tab:time_errors}}
+	\caption{Time errors for the correctly detected gait events. Note that 0.005 s corresponds to 1 sample period, given the sampling frequency of 200 Hz. \label{tab:time_errors}}
 	\newcolumntype{C}{>{\centering\arraybackslash}X}
@@
 
-\subsection{Stride Parameters}
+\subsection{Stride-specific Gait Parameters}
 For those trials for which all gait events were correctly detected (and no false positives were detected), stride time, stance time and swing time were calculated.
@@
 
-For all stride-specific gait parameters, and for all tracked points, the mean difference was close to zero, i.e., the maximum mean difference was 0.003 s, namely for the calculated swing time of the right ankle (Table~\ref{tab:stride_parameters}).
-Furthermore, for all gait parameters and for all tracked points the limits of agreement, based on a 95\% confidence interval were distributed around a zero mean difference with the overall limits of agreement at -0.049 s and 0.051 s (Figure~\ref{fig:gait_parameters_bland_altman_plots}).
+For all stride-specific gait parameters, and for all sensor locations, the mean difference was close to zero, i.e., the maximum mean difference was 0.003 s, namely for the calcualted swing time of the right ankle (Table~\ref{tab:stride_parameters}).
+Furthermore, for all gait parameters and for all sensor locations the limits of agreement, based on a 95\% confidence interval were distributed around a zero-mean difference with the overall limits of agreement at -0.049 s and 0.051 s (Figure~\ref{fig:gait_parameters_bland_altman_plots}).
 \begin{table}[H] 
@@
 		\textbf{Tracked point} & \textbf{Parameters} & \textbf{Mean difference} & \textbf{Limits of Agreement}\\
-		 & & s & s\\
+		 & & s & (s, s)\\
 		\midrule
@@
 		\centering
-		\includegraphics[width=16.5cm]{fig/bland_altman_plots_stride_params.png}
+		\includegraphics[width=18.5cm]{fig/bland_altman_plots_stride_params}
 	\end{adjustwidth}
@@
 The current study aimed to validate a deep learning approach for detecting gait events from a single IMU worn on the lower leg.
-Data from a left and right ankle- and shank-worn IMU were used for training a deep learning model to detect gait events from walking trials performed by healthy YA, OA, participants diagnosed with PD, MS, or cLBP, participants who had a recent symptomatic stroke, and participants diagnosed with other neurological diseases.
+Data from left and right ankle- and shank-worn IMUs were used for training a neural network to detect gait events from walking trials performed by healthy YA, healthy OA, participants diagnosed with PD, MS, or cLBP, participants who had a recent symptomatic stroke, and participants diagnosed with other neurological diseases.
 Participants walked a 5 meter distance at three different self-selected walking speeds.
-The gait event timings that were predicted by the deep learning model were compared to a common reference method, i.e., optoelectronic motion capture, and clinically relevant stride-specific gait parameters were extracted.
+The gait event timings that were predicted by the neural network were compared to a common reference method, i.e., OMC system, and clinically relevant stride-specific gait parameters were extracted.
 
-A first measure for the model performance was given by the recall, precision and F$_{1}$ score.
+A first measure for the model performance was given by the recall (how many annotated events were detected) and precision (how many detected events were annotated).
 For both ICs and FCs, a high recall ($\ge 95\%$) and high precision ($\ge 98\%$) were observed, meaning that most events can be detected and most detected events were actually true events.
-There was little difference in recall and precision between tracked points (Table~\ref{tab:overall_detection_performance}) confirming that the deep learning approach is relatively invariant to exact sensor location.
-These values for recall and precision were slightly lower than our previously reported values \cite{Romijnders2021} that used a heuristics-based approach \cite{Salarian2004}, but in the current study more trials were included and from a more heterogeneous study population.
-The F$_{1}$ score was comparable to the F$_{1}$ score obtained by \cite{Filtjens2020} who compared marker-based gait event detection to manual annotations, and was also comparable to the F$_{1}$ score reported by \cite{Ji2019} for gait event detection from a continuous wavelet-based approach.
+There was little difference in recall and precision between sensor locations (Table~\ref{tab:overall_detection_performance}) confirming that the deep learning approach is relatively invariant to exact sensor localization.
 
-Next, the time agreement, expressed by the time error the annotated event and the detected event, was of interest.
-For both ICs and FCs, and for all tracked points, the observed time error was small, and the middle $50\%$ of the time errors were within a range of $\left[-0.015,0.010\right]$ s (Table~\ref{tab:time_errors}, Figure~\ref{fig:time_error_box_plots}).
-These data showed that the deep learning-based is approach is precise in detecting ICs and FCs.
+Next, the time error, that is the difference between the annotated event and the detected event, was of interest.
+For both ICs and FCs, and for all sensor locations, the observed time error was small, and the middle $50\%$ of the time errors were within a range of $\left[-0.015,0.010\right]$ s (Table~\ref{tab:time_errors}, Figure~\ref{fig:time_error_box_plots}).
+These data showed that the deep learning-based approach is precise in detecting initial and final contacts.
 Time errors were slightly smaller than our previously reported results \cite{Romijnders2021} that used a heuristics-based approach \cite{Salarian2004}.
-The heuristics-based approach determined ICs and FCs as local minima in the medio-lateral angular velocity \cite{Salarian2004} and it could be that these minima do not exactly coincide with the referent event timing as determined from the optoelectronic motion capture systems.
-The median and IQR of the time errors were in the same range as previously found by \cite{Gadaleta2019} that used a similar model architecture.
-The time errors were lower than previously reported time errors from a continuous wavelet-based approach \cite{Ji2019}.
+The heuristics-based approach determined ICs and FCs as local minima in the medio-lateral angular velocity \cite{Salarian2004} and it could be that these minima do not exactly coincide with the referent event timing as determined from the OMC systems.
+The median and IQR of the time errors were in the same range as previously found by \cite{Gadaleta2019}.
+The time errors were lower than previously reported time errors from a continious wavelet-based approach \cite{Ji2019}.
 
@@
 Therefore, stride time, stance time, and swing time were calculated, and the differences between the deep learning-based approach and the marker-based reference method were quantified (Table~\ref{tab:stride_parameters}, Figure~\ref{fig:gait_parameters_bland_altman_plots}).
-The limits of agreement for a $95\%$ confidence interval were calculated, and for all metrics the zero mean difference was enclosed in the limit of agreement.
+The limits of agreement for a $95\%$ confidence interval were calculated, and for all metrics the zero-mean difference was enclosed in the limit of agreement.
 These data provided evidence that the deep learning-based model was able to derive stride-specific gait parameters.
-The differences between the deep learning model-based stride parameters and the marker-based stride parameters were in a similar range as a recent study that compared IMU-derived stride parameters against stride parameters obtained with a pressure sensing walkway \cite{Gadaleta2019,Niswander2021}, and were also in the same range as a study that compared IMU-derived stride parameters with stride parameters obtained with an optoelectronic motion capture systems \cite{Carcreff2018}.
+The differences between the deep learning model-based stride parameters and the marker-based stride parameters were in a similar range as a recent study that compared IMU-derived stride parameters against stride parameters obtained with a pressure sensing walkway \cite{Niswander2021,Gadaleta2019}, and were also in the same range as a study that compared IMU-derived stride parameters with stride parameters obtained with an OMC systems \cite{Carcreff2018}.
 
 The main limitations of the current study were that only walking trials involving straight-line walking were considered, and the walking distance was relatively short.
-The observed gait patterns from these walking trials may therefore not be fully representative of gait patterns observed in daily-life \cite{Hillel2019,Warmerdam2020,Atrsaei2021}.
-However, as the deep learning-based approach does not rely on fixed thresholds or assumptions regarding to which sensor axis is used, it is theoretically transferable and scalable to other conditions if input data and corresponding labels can be provided.
-For example, in \cite{Gadaleta2019} a similar deep learning model was tested for a setup with three IMUs and for a setup with a single IMU, and observed differences in time errors compared to a pressure sensing walkway were negligible.
+Therefore, it may be that the observed gait patterns from these walking trials are not fully representative of gait patterns observed in daily-life \cite{Hillel2019,Warmerdam2020,Atrsaei2021}.
+However, as the deep learning-based approach does not rely on fixed thresholds or assumptions to which sensor axis is used, it is theoretically transferable and scalable to other conditions if input data and corresponding labels can be provided.
 
@@
 \section{Conclusions}
-In this study we have validated a deep learning-based approach to detect gait events and subsequently extract clinically relevant stride parameters from a single inertial measurement unit worn either laterally above the ankle joint or proximal below the knee joint.
+In this study we have validated a deep learning-based approach to detect gait events and subsequently extract clinically relevant stride-specific gait parameters from a single IMU worn either laterally above the ankle joint or proximal below the knee joint.
 Performance analysis showed an excellent detection rate, and low time errors in both event detection and stride parameter calculation for different walking speeds and across both healthy and neurological cohorts.
@@
 Additionally, we are preparing the open-source release of all data from the healthy younger and older adults.
-Data from patient groups can be shared upon reasonable request.
-The full algorithm pipeline is going to be made publicly available online at \url{https://github.com/rmndrs89/my-gait-events-tcn}.}
+Data from patient groups can be shared upon reasonable request.}
 
 \acknowledgments{The authors sincerely thank all people that were involved in the data collection, from study participants to students who aided and assisted during measurements and subsequent marker labeling.
-The authors thank Julius Welzel for his contributions to the organization of the research data.
-The authors thank Johannes Hoffmann for his tips regarding \LaTeX\ typesetting.}
+The authors thank Julius Welzel for his input regarding the organization of the data in a BIDS-like format.
+The authors thank Johannes Hoffmann for his tips regarding the \LaTeX typesetting.}
 
@@
 Comput.} {\bf 2010}, {\em 48}(12), 1251--1260.
+	\bibitem[Leineweber(2019)]{Leineweber2019}
+	Leineweber,~M.J.; Gomez~Orozco,~M.~D.; Andrysek,~J.
+Evaluating the feasibility of two post-hoc correction techniques for mitigating posture-induced measurement errors associated with wearable motion capture.
+{\em Med.
+Eng.
+Phys.} {\bf 2019}.
+{\em 71}:38–44.
+	\bibitem[Pacher(2020)]{Pacher2020}
+	Pacher,~L.; Chatellier,~C.; Vauzelle,~R.; Fradet,~L.
+Sensor-to-Segment Calibration Methodologies for Lower-Body Kinematic Analysis with Inertial Sensors: A Systematic Review.
+{\em Sensors} {\bf 2020}, {\em 20}(11):3322.
 	\bibitem[LeCun(2015)]{LeCun2015}
@@
 	\bibitem[VanRossum(2009)]{VanRossum2009}
-	Van~Rossum,~G.; Drake,~F.L. \textit{Python 3 Reference Manual}; CreateSpace, Scotts Valley, CA, USA, 2009.
+	van~Rossum,~G.; Drake,~F.L. {\em Python 3 Reference Manual}; CreateSpace, Scotts Valley, CA, USA, 2009.
 	\bibitem[Chollet(2015)]{Chollet2015}
@@
 In Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition, Honolulu, HI, USA, 22--25 Jul.
-2017; pp.
+2017; p.
 156--165.
@@
 {\em arXiv:1609.03499} {\bf 2016}.
+	\bibitem[OMalley(2019)]{OMalley2019}
+	O'Malley,~T.; Bursztein,~E.; Long,~J.; Chollet,~F.; Jin,~H.; Invernizzi,~L.; and others; KerasTuner. {\em GitHub repository} {\bf 2019}, {\em GitHub}, \url{https://github.com/keras-team/keras-tuner}.
 	\bibitem[Kingma(2014)]{Kingma2014}
@@
 9367--9376.
-	\bibitem[OMalley(2019)]{OMalley2019}
-	O'Malley,~T.; Bursztein,~E.; Long,~J.; Chollet,~F.; Jin,~H.; Invernizzi,~L.; and others; KerasTuner. {\em GitHub repository} {\bf 2019}, {\em GitHub}, \url{https://github.com/keras-team/keras-tuner}.
 	\bibitem[Bergstra(2012)]{Bergstra2012}
@@
 {\em Sensors} {\bf 2019}, {\em 19}(16):3462.
-	\bibitem[Carcreff(2018)]{Carcreff2018}
-	Carcreff,~L.; Gerber,~C.N.; Paraschiv-Ionescu,~A.; De~Coulon,~G.; Newman,~C.J.; Armand,~S.; Aminian,~K.
-What is the Best Configuration of Wearable Sensors to Measure Spatiotemporal Gait Parameters in Children with Cerebral Palsy?
-{\em Sensors} {\bf 2018}, {\em 18}(2):394.
+
+	\bibitem[Mishra(2019)]{Mishra2019}
+	Mishra,~P.; Pandey,~C.M.; Singh,~U.; Gupta,~A.; Sahu,~C.; Keshri,~A. Descriptive Statistics and Normality Tests for Statistical Data. {\em Ann. Card. Anaesth.} {\bf 2019}, {\em 22}(1), 67--72. 	
+	\bibitem[Wilcoxon(1945)]{Wilcoxon1945}
+	Wilcoxon,~F. Individual Comparisons by Ranking Methods. {\em Biometrics Bull.} {\bf 1945}, {\em 1}, 80--83.
+	\bibitem[McDonald(2014)]{McDonald2014}
+	McDonald,~J.H. \textit{Handbook of Biological Statistics}, 3rd ed.; Sparky House Publishing: Sparky House Publishing, USA, 2014; pp. 186--189.
 \end{thebibliography}

### 2022-04-21 extract_gait_metrics.py

@@ -1,98 +1,0 @@
-import numpy as np
-import seaborn as sns
-import pandas as pd
-import matplotlib.pyplot as plt
-import os
-
-# Settings
-ROOT_DIR = "."
-FILENAME = "results_v3.tsv"
-
-# Load data
-df = pd.read_csv(os.path.join(ROOT_DIR, FILENAME), header=0, sep="\t")
-
-# 
-df_gait_metrics = {"sub_id": [],
-                    "task": [],
-                    "tracked_point": [],
-                    "ix_ref": [],
-                    "ix_pred": [],
-                    "stride_time_ref": [],
-                    "stride_time_pred": [],
-                    "stance_time_ref": [],
-                    "stance_time_pred": [],
-                    "swing_time_ref": [],
-                    "swing_time_pred": []}
-
-for sub_id in df["sub_id"].unique():
-    # print(f"{sub_id}")
-    df_sel = df.loc[df["sub_id"]==sub_id]
-    for task in df_sel["task"].unique():
-        # print(f"    {task:s}")
-        df_sel = df.loc[(df["sub_id"]==sub_id) & (df["task"]==task)]
-        for run in df_sel["run"].unique():
-            if not isinstance(run, str):
-                for tracked_point in df_sel["tracked_point"].unique():
-                    # print(f"        {tracked_point}")
-                    df_sel = df.loc[(df["sub_id"]==sub_id) & (df["task"]==task) & (df["tracked_point"]==tracked_point)]
-                    if not(df_sel[["ix_ref", "ix_pred"]].isna().any().any()):
-                        ix_IC_ref = np.sort(df_sel.loc[df_sel["event_type"]=="IC"]["ix_ref"].values[:])
-                        ix_IC_pred = np.sort(df_sel.loc[df_sel["event_type"]=="IC"]["ix_pred"].values[:])
-                        ix_FC_ref = np.sort(df_sel.loc[df_sel["event_type"]=="FC"]["ix_ref"].values[:])
-                        ix_FC_pred = np.sort(df_sel.loc[df_sel["event_type"]=="FC"]["ix_pred"].values[:])
-                        if len(ix_IC_ref)==0 or len(ix_IC_pred)==0 or len(ix_FC_ref)==0 or len(ix_FC_pred)==0:
-                            continue
-                        for i in range(len(ix_IC_ref)-1):
[…]

### 2022-04-21 test.py

@@ -1,76 +1,0 @@
-from fileinput import filename
-from locale import normalize
-import os, sys
-import pandas as pd
-import numpy as np
-import matplotlib as mpl
-import matplotlib.pyplot as plt
-from utils.data_utils import load_dataset, load_file, split_ids, split_left_right
-from utils.plot_utils import plot_targets
-from utils.preprocessing import create_batch_sequences, create_sequences
-from scipy.signal import find_peaks
-import timeit
-
-def main():
-    # Get list of all subject for which we have any kind of data
-    sub_ids = [sub_id for sub_id in os.listdir(ROOT_DIR) if sub_id.startswith("sub-pp")]
-    
-    # Split the subject ids into separate lists
-    train_ids, val_ids, test_ids = split_ids(ROOT_DIR)
-    
-    # Get a training dataset
-    ds_train = []
-    start_time = timeit.default_timer()
-    for sub_id in train_ids:
-        filenames = [fname for fname in os.listdir(os.path.join(ROOT_DIR, sub_id, "motion")) if (fname.endswith("_events.tsv")) and ("_task-walk" in fname)]
-        for ix_filename, filename in enumerate(filenames):
-            examples = load_file(
-                os.path.join(ROOT_DIR, sub_id, "motion", filename),
-                tracked_points=TRACKED_POINTS,
-                incl_magn=INCL_MAGN,
-                normalize=NORMALIZE
-            )
-            ds_train += examples
-    elapsed_time = timeit.default_timer() - start_time
-    print(f"Training dataset completed, run {elapsed_time}")
-    
-    # Get a validation dataset
-    ds_val = []
-    for sub_id in val_ids:
-        filenames = [fname for fname in os.listdir(os.path.join(ROOT_DIR, sub_id, "motion")) if (fname.endswith("_events.tsv")) and ("_task-walk" in fname)]
-        for ix_filename, filename in enumerate(filenames):
-            examples = load_file(
-                os.path.join(ROOT_DIR, sub_id, "motion", filename),
-                tracked_points=TRACKED_POINTS,
-                incl_magn=INCL_MAGN,
-                normalize=NORMALIZE
-            )
-            ds_val += examples
-    elapsed_time = timeit.default_timer() - start_time
-    print(f"Validation dataset completed, run {elapsed_time}")
-    
-    # Get a test dataset
-    ds_test = []
[…]

### 2022-04-21 paper/MDPI_template/article.tex
Updated draft with generic tcn architecture

@@
 However, these algorithms often require knowledge about sensor orientation and use empirically derived thresholds.
-As sensor-to-segment alignment cannot always be controlled for in ambulatory assessments, methods are needed that require little knowledge on sensor location and orientation, e.g., a convolutional neural network-based deep learning model.
+As alignment cannot always be controlled for in ambulatory assessments, methods are needed that require little knowledge on sensor location and orientation, e.g., a convolutional neural network-based deep learning model.
 Therefore, 160 participants from healthy and neurologically diseased cohorts walked 5 meter distances at slow, preferred, and fast walking speed, while data were collected from IMUs on the left and right ankle and shank.
@@
 Time agreement was excellent as witnessed from the median time error (0.005 s) and corresponding inter-quartile range (0.020 s).
-The extracted stride-specific parameters were in good agreement with parameters derived from the OMC system (maximum mean difference 0.003 s, and corresponding maximum limits of agreement (-0.049 s, 0.051 s) for a $95\%$ confidence level.) Thus, the deep learning approach was considered a valid approach for detecting gait events and extracting stride-specific parameters with little knowledge on exact IMU location and orientation in conditions with and without walking pathologies due to neurological diseases.}
+The extracted stride-specific parameters were in good agreement with parameters derived from the OMC system (maximum mean difference 0.003 s, and corresponding maximum limits of agreement (-0.049~s, 0.051~s) for a $95\%$ confidence level.) Thus, the deep learning approach was considered a valid approach for detecting gait events and extracting stride-specific parameters with little knowledge on exact IMU location and orientation in conditions with and without walking pathologies due to neurological diseases.}
 
@@
 The IC is when the foot contacts the ground and together with the instant at which the foot leaves the ground (final contact, FC), each stride can be divided in a stance and swing phase \cite{Rueterbories2010,Bruening2014}.
-The events of IC and FC, also referred to as \emph{gait events}, are commonly determined using force or pressure measuring devices \cite{Bruening2014}, or marker-based optoelectronic motion capture systems (henceforth referred to as the \emph{marker-based} system or method) \cite{Chiari2005,Topley2020}.
+The events of IC and FC, also referred to as \emph{gait events}, are commonly determined using force or pressure measuring devices \cite{Bruening2014}, or marker-based optoelectronic motion capture systems (OMC; henceforth referred to as the \emph{marker-based} system or method) \cite{Chiari2005,Topley2020}.
 These systems are relatively expensive, and restricted to usage in expertise laboratories \cite{Iosa2016,Jarchi2018}.
@@
 Previous research suggests that gait event detection is more accurate using an IMU worn on a lower limb (e.g., shank or foot) compared to an IMU worn on the low back \cite{BenMansour2015,Storm2016,Panebianco2018}.
-Now, in order to get from abstract IMU sensor readings to clinically relevant gait parameters (e.g., from accelerations and angular velocities to stride times) \cite{Hannink2016}, different algorithmic approaches have been developed in the last twenty years of clinical gait research.
+Now, in order to get from abstract IMU sensor readings to clinically relevant gait parameters (i.e., from accelerations and angular velocities to stride times) \cite{Hannink2016}, different algorithmic approaches have been developed in the last twenty years of clinical gait research.
 A recent study has evaluated a cross-section of these algorithms for different sensor locations on the lower leg and foot \cite{Niswander2021}.
@@
 This means the sensor readings need to be linked with the anatomical axes, that is, one needs to know which sensor axis aligns with for example the medio-lateral axis.
-In most approaches, it is simply assumed that due to sensor attachment the sensor axis aligns roughly with the anatomical axis of interest (\cite{Salarian2004,Sabatini2005,Jasiewicz2006,Catalfamo2010,Trojaniello2014,Maqbool2016,Romijnders2021}) or an additional calibration procedure (e.g., \cite{Ferraris1995}) is required (\cite{Greene2010,Niswander2021}).
+In most approaches, it is simply assumed that due to sensor attachment the sensor axis aligns roughly with the anatomical axis of interest \cite{Salarian2004,Sabatini2005,Jasiewicz2006,Catalfamo2010,Trojaniello2014,Maqbool2016,Romijnders2021} or an additional calibration procedure (e.g., \cite{Ferraris1995}) is required \cite{Greene2010,Niswander2021}.
 In ambulatory assessments however, study participants often attach the sensor themselves, for example after showering, and therefore the sensor location and alignment cannot be controlled for.
@@
 Furthermore, reflective markers were attached on top of the usual foot wear at the heel and toe of both feet (Figure~\ref{fig:methods_marker_vs_imu}).
-Marker data were recorded using a twelve-camera optoelectronic motion capture system (Qualisys AB, G\"{o}teborg, Sweden) at a sampling frequency of 200 Hz.
+Marker data were recorded using a twelve-camera OMC system (Qualisys AB, G\"{o}teborg, Sweden) at a sampling frequency of 200 Hz.
 IMU data were recorded at the same sampling frequency, and both systems were synchronized using a TTL signal \cite{Warmerdam2021}.
@@
 The training and validation set were used to train an optimal deep learning model.
-Test set data were not used for model training or hyperparameter tuning.
-The results on the model's performance were only based on the test set, and therefore reflect how good the model generalizes to new, \emph{unseen} data.
+Test set data were not used for training the model or hyperparameter tuning.
+The results on the model's performance were only based on the test set, and therefore reflected how good the model generalizes to new, \emph{unseen} data.
 
@@
 \subsubsection{Model Architecture}
+\begin{figure}[H]
+	\begin{adjustwidth}{-\extralength}{0cm}
+		\centering
+		\includegraphics[width=13.5cm]{fig/tcn_model_arch}
+	\end{adjustwidth}
+	\caption{The generic model architecture of the deep learning model to predict initial contacts (ICs) and final contacts (FCs).
+The inputs are the accelerometer and gyroscope data from a single inertial measurement unit, and are fed to a temporal convolutional network (TCN) (left).
+The TCN consisted of repeating residual blocks (ResBlocks) with exponentially increasing dilation factor (middle).
+Each ResBlock was built from two sequences of a convolutional layer (Conv), batch normalization layer (BatchNorm), a rectified linear unit activation layer (ReLU), and a dropout layer (DropOut) (right).
+\label{fig:tcn_model_arch}}
+\end{figure}
 The generic architecture for the deep learning model was based on a temporal convolutional network (TCN) \cite{Bai2018,Remy2020,Filtjens2020}.
@@
 The model performance was evaluated for (1) overall detection performance, (2) time agreement between the predicted events and the (marker-based) annotated events, (3) agreement between subsequently derived stride-specific gait parameters.
-\subsubsection{Overall detection performance \label{subsubsec:overall_detection_performance}}
+\subsubsection{Overall Detection Performance \label{subsubsec:overall_detection_performance}}
 The overall detection performance quantified how many of the annotated evens were detected by the model (true positives, TP), how many of the annotated events were not detected (false negatives, FN), and how many events that were detected, were actually not annotated (false positives, FP).
@@
 
-\subsubsection{Time Error}
-For all correctly detected gait events (TP, Section \ref{subsubsec:overall_detection_performance}), the time error between the annotated and detect gait event was defined as:
+\subsubsection{Time Agreement}
+For all correctly detected gait events (TP, Section \ref{subsubsec:overall_detection_performance}), time agreement was assessed by the time error between the annotated and detect gait event, which was defined as:
 \begin{equation}
@@
 
-\subsubsection{Stride Parameters}
+\subsubsection{Stride-specific Gait Parameters}
 For those trials for which all gait events were detected, and no false positives were detected, the stride time, stance time and swing were calculated.
@@
 
-\subsection{Overall detection performance}
+\subsection{Overall Detection Performance}
 The performance of detecting ICs and FCs was objectively quantified by the number of TPs, the number of FNs, and the number of FPs.
@@
 	\end{adjustwidth}
-	\caption{The agreement of extracted gait parameters between the sensor-based and marker-based methods.\label{fig:gait_parameters_bland_altman_plots}}
+	\caption{The agreement of extracted gait parameters between the sensor-based and marker-based methods.
+The differences between the stride-specific temporal gait parameters extracted from the marker-based and proposed approach are plotted against the means.
+\label{fig:gait_parameters_bland_altman_plots}}
 \end{figure}
@@
 The median and IQR of the time errors were in the same range as previously found by \cite{Gadaleta2019}.
-The time errors were lower than previously reported time errors from a continious wavelet-based approach \cite{Ji2019}.
+The time errors were lower than previously reported time errors from a continuous wavelet-based approach \cite{Ji2019}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{Conceptualization, R.R., G.S., and W.M.; methodology, R.R., G.S.; software, R.R.; validation, R.R.,; formal analysis, R.R.; investigation, R.R., G.S., W.M.; resources, C.H, W.M..; data curation, E.W., R.R.,; writing---original draft preparation, R.R.; writing---review and editing, E.W., C.H., G.S., W.M.; visualization, R.R.; supervision, G.S., W.M.; project administration, R.R., E.W., C.H., G.S., W.M.; funding acquisition, W.M.
+\authorcontributions{Conceptualization, R.R., G.S., and W.M.; methodology, R.R., G.S.; software, R.R.; validation, R.R.; formal analysis, R.R.; investigation, R.R., G.S., W.M.; resources, C.H, W.M.; data curation, E.W., R.R.,; writing---original draft preparation, R.R.; writing---review and editing, E.W., C.H., G.S., W.M.; visualization, R.R.; supervision, G.S., W.M.; project administration, R.R., E.W., C.H., G.S., W.M.; funding acquisition, W.M.
 All authors have read and agreed to the published version of the manuscript.}
 
-\funding{This research received funding from the DFG Open Access fund.}
+\funding{}
 
@@
 Additionally, we are preparing the open-source release of all data from the healthy younger and older adults.
-Data from patient groups can be shared upon reasonable request.}
+Data from patient groups can be shared upon reasonable request.
+The scripts are publicly available at the author's personal GitHub, which can be found at \url{https://github.com/rmndrs89/my-gait-events-tcn}.}
 
@@
 
-	\bibitem[Mishra(2019)]{Mishra2019}
-	Mishra,~P.; Pandey,~C.M.; Singh,~U.; Gupta,~A.; Sahu,~C.; Keshri,~A. Descriptive Statistics and Normality Tests for Statistical Data. {\em Ann. Card. Anaesth.} {\bf 2019}, {\em 22}(1), 67--72. 	
-	\bibitem[Wilcoxon(1945)]{Wilcoxon1945}
-	Wilcoxon,~F. Individual Comparisons by Ranking Methods. {\em Biometrics Bull.} {\bf 1945}, {\em 1}, 80--83.
-	\bibitem[McDonald(2014)]{McDonald2014}
-	McDonald,~J.H. \textit{Handbook of Biological Statistics}, 3rd ed.; Sparky House Publishing: Sparky House Publishing, USA, 2014; pp. 186--189.
+%	\bibitem[Mishra(2019)]{Mishra2019}
+%	Mishra,~P.; Pandey,~C.M.; Singh,~U.; Gupta,~A.; Sahu,~C.; Keshri,~A. Descriptive Statistics and Normality Tests for Statistical Data. {\em Ann. Card. Anaesth.} {\bf 2019}, {\em 22}(1), 67--72. 	
+%	\bibitem[Wilcoxon(1945)]{Wilcoxon1945}
+%	Wilcoxon,~F. Individual Comparisons by Ranking Methods. {\em Biometrics Bull.} {\bf 1945}, {\em 1}, 80--83.
+%	\bibitem[McDonald(2014)]{McDonald2014}
+%	McDonald,~J.H. \textit{Handbook of Biological Statistics}, 3rd ed.; Sparky House Publishing: Sparky House Publishing, USA, 2014; pp. 186--189.
 \end{thebibliography}

### 2022-04-22 paper/MDPI_template/article.tex
Edited authors, and submission completed

@@
 % Authors, for the paper (add full first names)
-\Author{Robbin Romijnders$^{1}$*\orcidA{}, Elke Warmerdam$^{2}$, Clint Hansen$^{1}$, Gerhard Schmidt$^{3}$ and Walter Maetzler$^{1}$}
+\Author{Robbin Romijnders$^{1}$\orcidA{}, Elke Warmerdam$^{2}$, Clint Hansen$^{1}$, Gerhard Schmidt$^{3}$ and Walter Maetzler$^{1}$*}
 
@@
 % Contact information of the corresponding author
-\corres{Correspondence: r.romijnders@neurologie.uni-kiel.de (R.R.)}
+\corres{Correspondence: w.maetzler@neurologie.uni-kiel.de (W.M.)}
 
@@
 
-\funding{}
+\funding{We acknowledge financial support by Land Schleswig-Holstein within the funding programme Open Access Publikationsfonds.}
 

### 2022-04-22 paper/MDPI_template/article.tex
Changed Vecteezy image attribution

@@
 Marker data were used to obtain reference values for the timings of initial and final contacts (top), where accelerometer and gyroscope data from each tracked point were inputted to a neural network that predicted timings of the same initial and final contacts (bottom).
-\newline \noindent{\footnotesize{\textsuperscript{1} Picture from: \url{https://www.vecteezy.com/free-vector/man-walking }.}} \label{fig:methods_marker_vs_imu}}
+\newline \noindent{\footnotesize{\textsuperscript{1} Picture from: \href{https://www.vecteezy.com/free-vector/man-walking}{Man Walking Vectors by Vecteezy}.}} \label{fig:methods_marker_vs_imu}}
 \end{figure}
@@
 The authors thank Julius Welzel for his input regarding the organization of the data in a BIDS-like format.
-The authors thank Johannes Hoffmann for his tips regarding the \LaTeX typesetting.}
+The authors thank Johannes Hoffmann for his tips regarding the \LaTeX typesetting.
+The "walking man" picture from Figure~\ref{fig:methods_marker_vs_imu} is from \href{https://www.vecteezy.com/free-vector/man-walking}{Man Walking Vectors by Vecteezy}.}
 
